### 2018-01-28 paper/main.tex
Add the ICML template

%%%%%%%% ICML 2018 EXAMPLE LATEX SUBMISSION FILE %%%%%%%%%%%%%%%%%

\documentclass{article}

% Recommended, but optional, packages for figures and better typesetting:
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs} % for professional tables

% hyperref makes hyperlinks in the resulting PDF.
% If your build breaks (sometimes temporarily if a hyperlink spans a page)
% please comment out the following usepackage line and replace
% \usepackage{icml2018} with \usepackage[nohyperref]{icml2018} above.
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{icml2018}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{icml2018}

% The \icmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\icmltitlerunning{Submission and Formatting Instructions for ICML 2018}

\begin{document}

\twocolumn[
\icmltitle{Submission and Formatting Instructions for \\
           International Conference on Machine Learning (ICML 2018)}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the icml2018
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\icmlsetsymbol{equal}{*}

\begin{icmlauthorlist}
\icmlauthor{Aeiau Zzzz}{equal,to}
\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\icmlauthor{Cieua Vvvvv}{goo}
\icmlauthor{Iaesut Saoeu}{ed}
\icmlauthor{Fiuea Rrrr}{to}
\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\icmlauthor{Aaoeu Iasoh}{goo}
\icmlauthor{Buiui Eueu}{ed}
\icmlauthor{Aeuia Zzzz}{ed}
\icmlauthor{Bieea C.~Yyyy}{to,goo}
\icmlauthor{Teoau Xxxx}{ed}
\icmlauthor{Eee Pppp}{ed}
\end{icmlauthorlist}

\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\icmlkeywords{Machine Learning, ICML}

\vskip 0.3in
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \icmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}

\section{Electronic Submission}
\label{submission}

Submission to ICML 2018 will be entirely electronic, via a web site
(not email). Information about the submission process and \LaTeX\ templates
are available on the conference web site at:
\begin{center}
\textbf{\texttt{http://icml.cc/2018/}}
\end{center}

The guidelines below will be enforced for initial submissions and
camera-ready copies. Here is a brief summary:
\begin{itemize}
\item Submissions must be in PDF\@.
\item The maximum paper length is \textbf{8 pages excluding references and
    acknowledgements, and 10 pages including references and acknowledgements}
    (pages 9 and 10 must contain only references and acknowledgements).
\item \textbf{Do not include author information or acknowledgements} in your
    initial submission.
\item Your paper should be in \textbf{10 point Times font}.
\item Make sure your PDF file only uses Type-1 fonts.
\item Place figure captions \emph{under} the figure (and omit titles from inside
    the graphic file itself). Place table captions \emph{over} the table.
\item References must include page numbers whenever possible and be as complete
    as possible. Place multiple citations in chronological order.
\item Do not alter the style template; in particular, do not compress the paper
    format by reducing the vertical spaces.
\item Keep your abstract brief and self-contained, one paragraph and roughly
    4--6 sentences. Gross violations will require correction at the
    camera-ready phase. The title should have content words capitalized.
\end{itemize}

\subsection{Submitting Papers}

\textbf{Paper Deadline:} The deadline for paper submission that is
advertised on the conference website is strict. If your full,
anonymized, submission does not reach us on time, it will not be
considered for publication. There is no separate abstract submission.

\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
author information may appear on the title page or in the paper
itself. Section~\ref{author info} gives further details.

\textbf{Simultaneous Submission:} ICML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. ICML submissions must not be
submitted to other conferences during ICML's review period. Authors
may submit to ICML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

Authors must provide their manuscripts in \textbf{PDF} format.
Furthermore, please make sure that files contain only embedded Type-1 fonts
(e.g.,~using the program \texttt{pdffonts} in linux or using
File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
might come from graphics files imported into the document.

Authors using \textbf{Word} must convert their document to PDF\@. Most
of the latest versions of Word have the facility to do this
automatically. Submissions will not be accepted in Word format or any
format other than PDF\@. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
Those using \texttt{latex} and \texttt{dvips} may need the following
two commands:

{\footnotesize
\begin{verbatim}
dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
ps2pdf paper.ps
\end{verbatim}}
It is a zero following the ``-G'', which tells dvips to use
the config.pdf file. Newer \TeX\ distributions don't always need this
option.

Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
results. This program avoids the Type-3 font problem, and supports more
advanced features in the \texttt{microtype} package.

\textbf{Graphics files} should be a reasonable size, and included from
an appropriate format. Use vector formats (.eps/.pdf) for plots,
lossless bitmap formats (.png) for raster graphics with sharp lines, and
jpeg for photo-like images.

The style file uses the \texttt{hyperref} package to make clickable
links in documents. If this causes problems for you, add
\texttt{nohyperref} as one of the options to the \texttt{icml2018}
usepackage statement.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
Section~\ref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the International
Conference on Machine Learning (ICML). Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{35}^{th}$ International Conference on Machine Learning},
Stockholm, Sweden, PMLR 80, 2018.
Copyright 2018 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{icml2018\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{icml2018\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the ICML
2018 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\icmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Length and Dimensions}

Papers must not exceed eight (8) pages, including all figures, tables,
and appendices, but excluding references and acknowledgements. When references and acknowledgements are included,
the paper must not exceed ten (10) pages.
Acknowledgements should be limited to grants and people who contributed to the paper.
Any submission that exceeds
this page limit, or that diverges significantly from the specified format,
will be rejected without review.

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

ICML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{icml2018.sty} file, use
\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via CMT\@. However, keep in mind that an ICML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the ICML2018 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\begin{figure}[ht]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{img/icml_numpapers}}
\caption{Historical locations and number of accepted papers for International
Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
produced, the number of accepted papers for ICML 2008 was unknown and instead
estimated.}
\label{icml-historical}
\end{center}
\vskip -0.2in
\end{figure}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it, as in
Figure~\ref{icml-historical}. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
Table~\ref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{icml2018.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\subsection{Software and Data}

We strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, do not
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system. Note that reviewers are not required to look a this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas,
and to funding agencies and corporate sponsors that provided financial
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{ref}
\bibliographystyle{icml2018}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\textbf{\emph{Do not put content after the references.}}
%
Put anything that you might normally include after the references in a separate
supplementary file.

We recommend that you build supplementary material in a separate document.
If you must create one PDF and cut it up, please be careful to use a tool that
doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
pdftk usually works fine.

\textbf{Please do not use Apple's preview to cut off supplementary material.} In
previous years it has altered margins, and created headaches at the camera-ready
stage. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018. It was modified from a version from Dan Roy in
% 2017, which was based on a version from Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2018-01-28 paper/abstract.tex
Abstract

\begin{abstract} 
    Recently, Bayesian optimization has been proposed for automated analog
    circuit design and has shown very good performance. However, the sequential
    property of Bayesian optimization limits its further application. In this
    paper, a batched bayesian optimization method is proposed, the
    parallelization is realized via multi-objective ensemble of acquisition
    functions. In each iteration, multiple acquisition functions are selected,
    multi-objective optimization is then performed to search for the Pareto
    front of the acquisition functions, candidate points are then sampled from
    the Pareto fronts. The proposed method is compared with several
    state-of-the-art algorithms using analytical benchmark functions and
    real-world analog circuits, the experimental results show that the proposed
    method is competitive.
\end{abstract}

### 2018-01-28 paper/background.tex
Abstract

\section{Background}

\subsection{Formulation}

We formulate the sizing problem as an optimization problem

\subsection{Gaussian Process}

Basic introduction to GP

\subsection{Acquisition Function}

Introduce LCB, EI and PI

### 2018-01-28 paper/experiments.tex
Abstract

\section{Experimental Results}

\subsection{Benchmark Problems}

\begin{enumerate}
        \item Hart6
        \item Alpine1
        \item Branin
        \item Rosenbrock-2
        \item Rosenbrock-10
        \item Ackley-2
        \item Ackley-10
\end{enumerate}

\subsection{Operational Amplifier}

\textcolor{red}{TODO: qKG and qEI}

\begin{figure}[]
\vskip 0.2in
\begin{center}
\centerline{\includegraphics[width=\columnwidth]{./img/mean_DAC2014.eps}}
\caption{Optimization results of the operational amplifier}
\label{resDAC2014}
\end{center}
\vskip -0.2in
\end{figure}

### 2018-01-28 paper/intro.tex
Abstract

\section{Introduction}

Automated analog IC design is very important

Traditional methods using offline model and simulated based methods are not good

Bayesian optimization has been applied, and outperformed many other algorithm

Bayesian optimization is a sequential algorithm, there is a need to parallelize it

Review current methods

Beiefly introduce my algorithm

### 2018-01-28 paper/mace.tex
Abstract

\section{Proposed Batched Bayesian Optimization Algorithm}

\subsection{Multi-objective optimization}

\subsection{MACE}

\textcolor{red}{Plot a figure to illustrate the PF/PS of acquisition functions}

### 2018-01-28 paper/main.tex
Abstract

@@
 \twocolumn[
-\icmltitle{Submission and Formatting Instructions for \\
-           International Conference on Machine Learning (ICML 2018)}
+\icmltitle{Batched Bayesian Optimization via Multi-objective Acquisition Function Ensemble for Automated Analog Circuit Design}
 
@@
 
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
+% % You can specify symbols, otherwise they are numbered in order.
+% % Ideally, you should not use this facility. Affiliations will be numbered
+% % in order of appearance and this is the preferred way.
+% \icmlsetsymbol{equal}{*}
 
-\begin{icmlauthorlist}
-\icmlauthor{Aeiau Zzzz}{equal,to}
-\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-\icmlauthor{Cieua Vvvvv}{goo}
-\icmlauthor{Iaesut Saoeu}{ed}
-\icmlauthor{Fiuea Rrrr}{to}
-\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
-\icmlauthor{Aaoeu Iasoh}{goo}
-\icmlauthor{Buiui Eueu}{ed}
-\icmlauthor{Aeuia Zzzz}{ed}
-\icmlauthor{Bieea C.~Yyyy}{to,goo}
-\icmlauthor{Teoau Xxxx}{ed}
-\icmlauthor{Eee Pppp}{ed}
-\end{icmlauthorlist}
+% \begin{icmlauthorlist}
+% \icmlauthor{Aeiau Zzzz}{equal,to}
+% \icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
+% \icmlauthor{Cieua Vvvvv}{goo}
+% \icmlauthor{Iaesut Saoeu}{ed}
+% \icmlauthor{Fiuea Rrrr}{to}
+% \icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
+% \icmlauthor{Aaoeu Iasoh}{goo}
+% \icmlauthor{Buiui Eueu}{ed}
+% \icmlauthor{Aeuia Zzzz}{ed}
+% \icmlauthor{Bieea C.~Yyyy}{to,goo}
+% \icmlauthor{Teoau Xxxx}{ed}
+% \icmlauthor{Eee Pppp}{ed}
+% \end{icmlauthorlist}
 
-\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
+% \icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
+% \icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
+% \icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
 
-\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+% \icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
+% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
 
-% You may provide any keywords that you
-% find helpful for describing your paper; these are used to populate
-% the "keywords" metadata in the PDF but will not be shown in the document
-\icmlkeywords{Machine Learning, ICML}
+% % You may provide any keywords that you
+% % find helpful for describing your paper; these are used to populate
+% % the "keywords" metadata in the PDF but will not be shown in the document
+% \icmlkeywords{Bayesian Optimization, Automated analog circuit design}
 
@@
 
-\begin{abstract}
-This document provides a basic paper template and submission guidelines.
-Abstracts must be a single paragraph, ideally between 4--6 sentences long.
-Gross violations will trigger corrections at the camera-ready phase.
-\end{abstract}
+\input{abstract}
+\input{intro}
+\input{background}
+\input{mace}
+\input{experiments}
 
-\section{Electronic Submission}
-\label{submission}
-
-Submission to ICML 2018 will be entirely electronic, via a web site
-(not email). Information about the submission process and \LaTeX\ templates
-are available on the conference web site at:
-\begin{center}
-\textbf{\texttt{http://icml.cc/2018/}}
-\end{center}
-
-The guidelines below will be enforced for initial submissions and
-camera-ready copies. Here is a brief summary:
-\begin{itemize}
-\item Submissions must be in PDF\@.
-\item The maximum paper length is \textbf{8 pages excluding references and
-    acknowledgements, and 10 pages including references and acknowledgements}
-    (pages 9 and 10 must contain only references and acknowledgements).
-\item \textbf{Do not include author information or acknowledgements} in your
-    initial submission.
-\item Your paper should be in \textbf{10 point Times font}.
-\item Make sure your PDF file only uses Type-1 fonts.
-\item Place figure captions \emph{under} the figure (and omit titles from inside
-    the graphic file itself). Place table captions \emph{over} the table.
-\item References must include page numbers whenever possible and be as complete
-    as possible. Place multiple citations in chronological order.
-\item Do not alter the style template; in particular, do not compress the paper
-    format by reducing the vertical spaces.
-\item Keep your abstract brief and self-contained, one paragraph and roughly
-    4--6 sentences. Gross violations will require correction at the
-    camera-ready phase. The title should have content words capitalized.
-\end{itemize}
-
-\subsection{Submitting Papers}
-
-\textbf{Paper Deadline:} The deadline for paper submission that is
-advertised on the conference website is strict. If your full,
-anonymized, submission does not reach us on time, it will not be
-considered for publication. There is no separate abstract submission.
-
-\textbf{Anonymous Submission:} ICML uses double-blind review: no identifying
-author information may appear on the title page or in the paper
-itself. Section~\ref{author info} gives further details.
-
-\textbf{Simultaneous Submission:} ICML will not accept any paper which,
-at the time of submission, is under review for another conference or
-has already been published. This policy also applies to papers that
-overlap substantially in technical content with conference papers
-under review or previously published. ICML submissions must not be
-submitted to other conferences during ICML's review period. Authors
-may submit to ICML substantially different versions of journal papers
-that are currently under review by the journal, but not yet accepted
-at the time of submission. Informal publications, such as technical
-reports or papers in workshop proceedings which do not appear in
-print, do not fall under these restrictions.
-
-\medskip
-
-Authors must provide their manuscripts in \textbf{PDF} format.
-Furthermore, please make sure that files contain only embedded Type-1 fonts
-(e.g.,~using the program \texttt{pdffonts} in linux or using
-File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
-might come from graphics files imported into the document.
-
-Authors using \textbf{Word} must convert their document to PDF\@. Most
-of the latest versions of Word have the facility to do this
-automatically. Submissions will not be accepted in Word format or any
-format other than PDF\@. Really. We're not joking. Don't send Word.
-
-Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
-Those using \texttt{latex} and \texttt{dvips} may need the following
-two commands:
-
-{\footnotesize
-\begin{verbatim}
-dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
-ps2pdf paper.ps
-\end{verbatim}}
-It is a zero following the ``-G'', which tells dvips to use
-the config.pdf file. Newer \TeX\ distributions don't always need this
-option.
-
-Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
-results. This program avoids the Type-3 font problem, and supports more
-advanced features in the \texttt{microtype} package.
-
-\textbf{Graphics files} should be a reasonable size, and included from
-an appropriate format. Use vector formats (.eps/.pdf) for plots,
-lossless bitmap formats (.png) for raster graphics with sharp lines, and
-jpeg for photo-like images.
-
-The style file uses the \texttt{hyperref} package to make clickable
-links in documents. If this causes problems for you, add
-\texttt{nohyperref} as one of the options to the \texttt{icml2018}
-usepackage statement.
-
-\subsection{Submitting Final Camera-Ready Copy}
-
-The final versions of papers accepted for publication should follow the
-same format and naming convention as initial submissions, except that
-author information (names and affiliations) should be given. See
-Section~\ref{final author} for formatting instructions.
-
-The footnote, ``Preliminary work. Under review by the International
-Conference on Machine Learning (ICML). Do not distribute.'' must be
-modified to ``\textit{Proceedings of the
-$\mathit{35}^{th}$ International Conference on Machine Learning},
-Stockholm, Sweden, PMLR 80, 2018.
-Copyright 2018 by the author(s).''
-
-For those using the \textbf{\LaTeX} style file, this change (and others) is
-handled automatically by simply changing
-$\mathtt{\backslash usepackage\{icml2018\}}$ to
-$$\mathtt{\backslash usepackage[accepted]\{icml2018\}}$$
-Authors using \textbf{Word} must edit the
-footnote on the first page of the document themselves.
-
-Camera-ready copies should have the title of the paper as running head
-on each page except the first one. The running title consists of a
-single line centered above a horizontal rule which is $1$~point thick.
-The running head should be centered, bold and in $9$~point type. The
-rule should be $10$~points above the main text. For those using the
-\textbf{\LaTeX} style file, the original title is automatically set as running
-head using the \texttt{fancyhdr} package which is included in the ICML
-2018 style file package. In case that the original title exceeds the
-size restrictions, a shorter form can be supplied by using
-
-\verb|\icmltitlerunning{...}|
-
-just before $\mathtt{\backslash begin\{document\}}$.
-Authors using \textbf{Word} must edit the header of the document themselves.
-
-\section{Format of the Paper}
-
-All submissions must follow the specified format.
-
-\subsection{Length and Dimensions}
-
-Papers must not exceed eight (8) pages, including all figures, tables,
-and appendices, but excluding references and acknowledgements. When references and acknowledgements are included,
-the paper must not exceed ten (10) pages.
-Acknowledgements should be limited to grants and people who contributed to the paper.
-Any submission that exceeds
-this page limit, or that diverges significantly from the specified format,
-will be rejected without review.
-
-The text of the paper should be formatted in two columns, with an
-overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
-between the columns. The left margin should be 0.75~inches and the top
-margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
-whether you print on US letter or A4 paper, but all final versions
-must be produced for US letter size.
-
-The paper body should be set in 10~point type with a vertical spacing
-of 11~points. Please use Times typeface throughout the text.
-
-\subsection{Title}
-
-The paper title should be set in 14~point bold type and centered
-between two horizontal rules that are 1~point thick, with 1.0~inch
-between the top rule and the top edge of the page. Capitalize the
-first letter of content words and put the rest of the title in lower
-case.
-
-\subsection{Author Information for Submission}
-\label{author info}
-
-ICML uses double-blind review, so author information must not appear. If
-you are using \LaTeX\/ and the \texttt{icml2018.sty} file, use
-\verb+\icmlauthor{...}+ to specify authors and \verb+\icmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
-will not be printed unless \texttt{accepted} is passed as an argument to the
-style file.
-Submissions that include the author information will not
-be reviewed.
-
-\subsubsection{Self-Citations}
-
-If you are citing published papers for which you are an author, refer
-to yourself in the third person. In particular, do not use phrases
-that reveal your identity (e.g., ``in previous work \cite{langley00}, we
-have shown \ldots'').
-
-Do not anonymize citations in the reference section. The only exception are manuscripts that are
-not yet published (e.g., under submission). If you choose to refer to
-such unpublished manuscripts \cite{anonymous}, anonymized copies have
-to be submitted
-as Supplementary Material via CMT\@. However, keep in mind that an ICML
-paper should be self contained and should contain sufficient detail
-for the reviewers to evaluate the work. In particular, reviewers are
-not required to look at the Supplementary Material when writing their
-review.
-
-\subsubsection{Camera-Ready Author Information}
-\label{final author}
-
-If a paper is accepted, a final camera-ready copy must be prepared.
-%
-For camera-ready papers, author information should start 0.3~inches below the
-bottom rule surrounding the title. The authors' names should appear in 10~point
-bold type, in a row, separated by white space, and centered. Author names should
-not be broken across lines. Unbolded superscripted numbers, starting 1, should
-be used to refer to affiliations.
-
-Affiliations should be numbered in the order of appearance. A single footnote
-block of text should be used to list all the affiliations. (Academic
-affiliations should list Department, University, City, State/Region, Country.
-Similarly for industrial affiliations.)
-
-Each distinct affiliations should be listed once. If an author has multiple
-affiliations, multiple superscripts should be placed after the name, separated
-by thin spaces. If the authors would like to highlight equal contribution by
-multiple first authors, those authors should have an asterisk placed after their
-name in superscript, and the term ``\textsuperscript{*}Equal contribution"
-should be placed in the footnote block ahead of the list of affiliations. A
-list of corresponding authors and their emails (in the format Full Name
-\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
-Ideally only one or two names should be listed.
-
-A sample file with author names is included in the ICML2018 style file
-package. Turn on the \texttt{[accepted]} option to the stylefile to
-see the names rendered. All of the guidelines above are implemented
-by the \LaTeX\ style file.
-
-\subsection{Abstract}
-
-The paper abstract should begin in the left column, 0.4~inches below the final
-address. The heading `Abstract' should be centered, bold, and in 11~point type.
-The abstract body should use 10~point type, with a vertical spacing of
-11~points, and should be indented 0.25~inches more than normal on left-hand and
-right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
-abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
-sentences. Gross violations will require correction at the camera-ready phase.
-
-\subsection{Partitioning the Text}
-
-You should organize your paper into sections and paragraphs to help
-readers place a structure on the material and understand its
-contributions.
-
-\subsubsection{Sections and Subsections}
-
-Section headings should be numbered, flush left, and set in 11~pt bold
-type with the content words capitalized. Leave 0.25~inches of space
-before the heading and 0.15~inches after the heading.
-
-Similarly, subsection headings should be numbered, flush left, and set
-in 10~pt bold type with the content words capitalized. Leave
-0.2~inches of space before the heading and 0.13~inches afterward.
-
-Finally, subsubsection headings should be numbered, flush left, and
-set in 10~pt small caps with the content words capitalized. Leave
-0.18~inches of space before the heading and 0.1~inches after the
-heading.
-
-Please use no more than three levels of headings.
-
-\subsubsection{Paragraphs and Footnotes}
-
-Within each section or subsection, you should further partition the
-paper into paragraphs. Do not indent the first line of a given
-paragraph, but insert a blank line between succeeding ones.
-
-You can use footnotes\footnote{Footnotes
-should be complete sentences.} to provide readers with additional
-information about a topic without interrupting the flow of the paper.
-Indicate footnotes with a number in the text where the point is most
-relevant. Place the footnote in 9~point type at the bottom of the
-column in which it appears. Precede the first footnote in a column
-with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
-appear in each column, in the same order as they appear in the text,
-but spread them across columns and pages if possible.}
-
-\begin{figure}[ht]
-\vskip 0.2in
-\begin{center}
-\centerline{\includegraphics[width=\columnwidth]{img/icml_numpapers}}
-\caption{Historical locations and number of accepted papers for International
-Machine Learning Conferences (ICML 1993 -- ICML 2008) and International
-Workshops on Machine Learning (ML 1988 -- ML 1992). At the time this figure was
-produced, the number of accepted papers for ICML 2008 was unknown and instead
-estimated.}
-\label{icml-historical}
-\end{center}
-\vskip -0.2in
-\end{figure}
-
-\subsection{Figures}
-
-You may want to include figures in the paper to illustrate
-your approach and results. Such artwork should be centered,
-legible, and separated from the text. Lines should be dark and at
-least 0.5~points thick for purposes of reproduction, and text should
-not appear on a gray background.
-
-Label all distinct components of each figure. If the figure takes the
-form of a graph, then give a name for each axis and include a legend
-that briefly describes each curve. Do not include a title inside the
-figure; instead, the caption should serve this function.
-
-Number figures sequentially, placing the figure number and caption
-\emph{after} the graphics, with at least 0.1~inches of space before
-the caption and 0.1~inches after it, as in
-Figure~\ref{icml-historical}. The figure caption should be set in
-9~point type and centered unless it runs two or more lines, in which
-case it should be flush left. You may float figures to the top or
-bottom of a column, and you may set wide figures across both columns
-(use the environment \texttt{figure*} in \LaTeX). Always place
-two-column figures at the top or bottom of the page.
-
-\subsection{Algorithms}
-
-If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
-environments to format pseudocode. These require
-the corresponding stylefiles, algorithm.sty and
-algorithmic.sty, which are supplied with this package.
-Algorithm~\ref{alg:example} shows an example.
-
-\begin{algorithm}[tb]
-   \caption{Bubble Sort}
-   \label{alg:example}
-\begin{algorithmic}
-   \STATE {\bfseries Input:} data $x_i$, size $m$
-   \REPEAT
-   \STATE Initialize $noChange = true$.
-   \FOR{$i=1$ {\bfseries to} $m-1$}
-   \IF{$x_i > x_{i+1}$}
-   \STATE Swap $x_i$ and $x_{i+1}$
-   \STATE $noChange = false$
-   \ENDIF
-   \ENDFOR
-   \UNTIL{$noChange$ is $true$}
-\end{algorithmic}
-\end{algorithm}
-
-\subsection{Tables}
-
-You may also want to include tables that summarize material. Like
-figures, these should be centered, legible, and numbered consecutively.
-However, place the title \emph{above} the table with at least
-0.1~inches of space before the title and the same after it, as in
-Table~\ref{sample-table}. The table title should be set in 9~point
-type and centered unless it runs two or more lines, in which case it
-should be flush left.
-
-% Note use of \abovespace and \belowspace to get reasonable spacing
-% above and below tabular lines.
-
-\begin{table}[t]
-\caption{Classification accuracies for naive Bayes and flexible
-Bayes on various data sets.}
-\label{sample-table}
-\vskip 0.15in
-\begin{center}
-\begin{small}
-\begin{sc}
-\begin{tabular}{lcccr}
-\toprule
-Data set & Naive & Flexible & Better? \\
-\midrule
-Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-\bottomrule
-\end{tabular}
-\end{sc}
-\end{small}
-\end{center}
-\vskip -0.1in
-\end{table}
-
-Tables contain textual material, whereas figures contain graphical material.
-Specify the contents of each row and column in the table's topmost
-row. Again, you may float tables to a column's top or bottom, and set
-wide tables across both columns. Place two-column tables at the
-top or bottom of the page.
-
-\subsection{Citations and References}
-
-Please use APA reference format regardless of your formatter
-or word processor. If you rely on the \LaTeX\/ bibliographic
-facility, use \texttt{natbib.sty} and \texttt{icml2018.bst}
-included in the style-file package to obtain this format.
-
-Citations within the text should include the authors' last names and
-year. If the authors' names are included in the sentence, place only
-the year in parentheses, for example when referencing Arthur Samuel's
-pioneering work \yrcite{Samuel59}. Otherwise place the entire
-reference in parentheses with the authors and year separated by a
-comma \cite{Samuel59}. List multiple references separated by
-semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
-construct only for citations with three or more authors or after
-listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
-
-Authors should cite their own work in the third person
-in the initial version of their paper submitted for blind review.
-Please refer to Section~\ref{author info} for detailed instructions on how to
-cite your own papers.
-
-Use an unnumbered first-level section heading for the references, and use a
-hanging indent style, with the first line of the reference flush against the
-left margin and subsequent lines indented by 10 points. The references at the
-end of this document give examples for journal articles \cite{Samuel59},
-conference publications \cite{langley00}, book chapters \cite{Newell81}, books
-\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
-\cite{mitchell80}, and dissertations \cite{kearns89}.
-
-Alphabetize references by the surnames of the first authors, with
-single author entries preceding multiple author entries. Order
-references for the same authors by year of publication, with the
-earliest first. Make sure that each reference includes all relevant
-information (e.g., page numbers).
-
-Please put some effort into making references complete, presentable, and
-consistent. If using bibtex, please protect capital letters of names and
-abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
-in your .bib file.
-
-\subsection{Software and Data}
-
-We strongly encourage the publication of software and data with the
-camera-ready version of the paper whenever appropriate. This can be
-done by including a URL in the camera-ready copy. However, do not
-include URLs that reveal your institution or identity in your
-submission for review. Instead, provide an anonymous URL or upload
-the material as ``Supplementary Material'' into the CMT reviewing
-system. Note that reviewers are not required to look a this material
-when writing their review.
-
-% Acknowledgements should only appear in the accepted version.
-\section*{Acknowledgements}
-
-\textbf{Do not} include acknowledgements in the initial version of
-the paper submitted for blind review.
-
-If a paper is accepted, the final camera-ready version can (and
-probably should) include acknowledgements. In this case, please
-place such acknowledgements in an unnumbered section at the
-end of the paper. Typically, this will include thanks to reviewers
-who gave useful comments, to colleagues who contributed to the ideas,
-and to funding agencies and corporate sponsors that provided financial
-support.
-
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-\nocite{langley00}
-
-\bibliography{ref}
-\bibliographystyle{icml2018}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Do \emph{not} have an appendix here}
-
-\textbf{\emph{Do not put content after the references.}}
-%
-Put anything that you might normally include after the references in a separate
-supplementary file.
-
-We recommend that you build supplementary material in a separate document.
-If you must create one PDF and cut it up, please be careful to use a tool that
-doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
-pdftk usually works fine.
-
-\textbf{Please do not use Apple's preview to cut off supplementary material.} In
-previous years it has altered margins, and created headaches at the camera-ready
-stage. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-01-29 paper/abstract.tex
Update

@@
 \begin{abstract} 
-    Recently, Bayesian optimization has been proposed for automated analog
-    circuit design and has shown very good performance. However, the sequential
-    property of Bayesian optimization limits its further application. In this
-    paper, a batched bayesian optimization method is proposed, the
-    parallelization is realized via multi-objective ensemble of acquisition
-    functions. In each iteration, multiple acquisition functions are selected,
-    multi-objective optimization is then performed to search for the Pareto
-    front of the acquisition functions, candidate points are then sampled from
-    the Pareto fronts. The proposed method is compared with several
-    state-of-the-art algorithms using analytical benchmark functions and
-    real-world analog circuits, the experimental results show that the proposed
-    method is competitive.
+    The Bayesian optimization has recently shown promising performance for
+    automated analog circuit design, however, the sequential property of
+    Bayesian optimization limits its further application. In this paper, a
+    batched bayesian optimization method is proposed, the parallelization is
+    realized via a multi-objective ensemble of acquisition functions. In each
+    iteration, multiple acquisition functions are selected, the multi-objective
+    optimization is then performed to search for the Pareto front of the
+    acquisition functions, candidate points are then sampled from the Pareto
+    fronts. The proposed method is compared with several state-of-the-art
+    batched Bayesian optimization algorithms using analytical benchmark
+    functions and real-world analog circuits; the experimental results show
+    that the proposed method is competitive with state-of-the-art methods.
 \end{abstract}

### 2018-01-29 paper/intro.tex
Update

@@
 
-Automated analog IC design is very important
+% % TODO: more introduction to the importance of anlog IC sizing, as the reviewers may not have much knowledge of circuit design
+Automated analog circuit design has been a challenging problem for the
+community of electronic design automation (EDA). Unlike digital circuits, where
+the design flow is highly automated, analog circuit design still
+heavily relies on designer's experience. The design parameters of analog circuits like
+transistor widths and lengths need to be manually calculated based on the
+specifications and the designers' understanding of the circuit. However, due to
+the ever-scaling IC manufacture technology and the increasing demands for
+high-performance, low-power circuits, it is getting much more difficult to meet
+the performance and time-to-market requirement with manual circuit design.
+Automated analog circuit design has thus attracted more research interests in
+the past decade~\cite{rutenbar2007hierarchical}.
 
-Traditional methods using offline model and simulated based methods are not good
+% TODO: Traditional methods using offline model and simulated based methods are
+% not good
+The analog circuit design automation problems can be formulated as optimization
+problems, the aim is to find the optimal vector of design parameters that give
+best figure of merit (FOM). Prior works about analog circuit optimization
+include offline model-based approaches
+~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
+simulation based approaches. The offline model-based methods try to build
+accurate global model and then apply global optimization algorithms to the
+cheap-to-evaluate models, the model either comes from designers' manual
+derivation or from regression models like SVM and ANN. The problem of this
+approach is that the accurate models are usually hard to get, for example,
+in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
+a sparse polynomial model for a circuit with ten design parameters.
+Simulation-based methods, instead, treat the circuits as black-box functions
+that get the objective value from circuit simulations, global optimization
+algorithms are directly applied to the black-box functions. For
+simulation-based circuit optimization methods, meta-heuristic algorithms like
+particle swarm intelligence (PSO)~\cite{phelps2000anaconda} and differential
+evolution algorithm (DE)~\cite{liu2009analog} are widely used, although these
+algorithm are able to explore the whole design space, they have relatively low
+convergence rate and consume many circuit simulations. When the circuit
+simulation takes a long time, both model-based and simulation-based approaches
+can be prohibitive.
 
-Bayesian optimization has been applied, and outperformed many other algorithm
+% TODO: Bayesian optimization is a sequential algorithm, there is a need to
+% parallelize it
+%
+% TODO: cite the two 3D-IC papers of TVLSI
+To reduce the circuit simulations needed by the optimization, the Gaussian
+process (GP)~\cite{GPML} model has been introduced as online surrogate model to
+assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
+differential evolution algorithm, in~\cite{lyu2017efficient}. Recently, the
+Bayesian optimization (BO) algorithm has been applied for analog circuit
+optimization, the Bayesian optimization algorithm is firstly introduced for the
+automated design of general analog circuits, and has shown very good
+performance compared to other simulation-based approaches,
+in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined
+with adaptive Monte-Carlo sampling to optimize the yield of analog circuits and
+static random-access memory (SRAM).
 
-Bayesian optimization is a sequential algorithm, there is a need to parallelize it
+The Bayesian optimization algorithm is a well-studied algorithm, and has
+demonstrated to be a promising algorithm for automated analog circuit design,
+however, the standard Bayesian optimization algorithm is sequential, it chooses
+the next evaluation point by optimizing the specified acquisition fucntion,
+which makes the parallelization of Bayesian optimization non-trivial. The
+sequential property of BO limits its further application, as multi-core
+processors are usually availble for modern computers.
 
-Review current methods
+% TODO: Review current methods
+There are some research about batched Bayesian optimization in the machine
+learning community,
 
-Beiefly introduce my algorithm
+% BUCB, UCB-PE: regret bound
+% PPES: entropy search
+% qKG, qEI: optimal decision if multiple points are selected
+% LP: very good heuristic
+
+% TODO: Beiefly introduce my algorithm
+All the above mentioned algorithms choose to use one specified acquisition function, however it has been shown in \cite{}
+
+%For simulation-based methods, the optimization is driven directly by the
+%circuit simulations. The objective functions and constraints are viewed as
+%black-box functions. They are obtained directly from circuit simulations. Since
+%the circuit simulations are invoked on-the-fly, the number of required
+%simulations would even be much lower than those of model-based approaches. A
+%variety of global optimization algorithms, including simulated
+%annealing (SA)~\cite{phelps2000anaconda}, particle swarm intelligence (PSO)
+%algorithm~\cite{vural2012analog} and evolutionary
+%algorithm~\cite{liu2009analog}, have been proposed to better explore the
+%solution space. Stochastic characteristics of these algorithms help them to
+%avoid getting stuck in the local optimum. However, they also suffer from
+%relatively low convergence rate. Recently, gradient based local search with
+%multiple starting points (MSP)~\cite{6420988, 1510411, pengboDate}
+%have been reported to be very efficient for analog circuit sizing.
+
+%However, the computation-intensive circuit simulation makes the analog circuit
+%sizing challenging for large-scale/complicated analog/RF circuits. For
+%example, one transient simulation could take several hours for complicated
+%circuits like a PLL. The passive components such as inductors and transformers
+%are widely used in RF and microwave circuits.  However, these components are
+%usually characterized by Electro-Magnetic (EM) simulations, which could take
+%even several hours for one configuration.  Furthermore, if the process variations
+%are taken into account, PVT corner enumerations or Monte-Carlo yield
+%estimations are required.  The computational cost would thus be greatly
+%increased. To address this problem, a hybrid methodology which combines both
+%the model-based approach and simulation-based approach has been proposed
+%recently~\cite{liu2011synthesis, 5763181, 6218230, tugui2013design,
+%liu2014gaspad}. Instead of using pre-built offline models, online evolving
+%models are built. The circuit simulations are invoked during the optimization
+%procedure to update the online models incrementally. The initial model is
+%constructed firstly using the data gathered from random sampling or Design of
+%Experiments (DoE). The model is used to guide the selection of the next point
+%towards higher performance. Once a new data point is obtained through
+%simulation, the model is updated with the new data point. For example, GASPAD
+%was proposed in~\cite{liu2014gaspad} for microwave circuit synthesis.
+
+%Multi-objective optimization has also been introduced for automated
+%analog circuit design~\cite{MO_overview}, as analog circuits usually have
+%several conflicting performances. It would be helpful to provide the designers
+%a set of designs with the best trade-off between performances. Unlike the
+%aforementioned single-objective optimization algorithms, a multi-objective
+%optimization algorithm tries to find a set of \emph{non-dominated} designs that
+%approximate the Pareto front of design objectives. For multi-objective analog
+%circuits optimization, meta-heuristic based algorithms are commonly used. The
+%Non-dominated Sorting Genetic Algorithm (NSGA-II)~\cite{nsgaii}, the
+%multi-objective evolutionary algorithm based on decomposition
+%(MOEA/D)~\cite{moead}, and the particle swarm intelligence (PSO)
+%algorithm~\cite{vural2012analog} with weighted sum aggregation serve as the
+%optimization kernel of~\cite{GENOM-POF, AIDA-C, 7927171,LiuBo_MOEAD,
+%fakhfakh2010analog}.
+
+%In this paper, we propose a Weighted Expected Improvement based Bayesian
+%Optimization (WEIBO) approach for the automated analog circuit sizing. Based on the
+%prior belief of the objective functions, the probabilistic surrogate models of
+%the objective functions are refined incrementally via Bayesian posterior
+%updating when new data are observed. The probabilistic models of the objective
+%functions are used to guide the optimization procedure. Gaussian processes (GP)
+%are used as the online surrogate models for circuit performances in our
+%proposed approach. It is important to balance the \emph{exploration} and
+%\emph{exploitation} during the optimization. The \emph{exploration} means that
+%the next point tends to explore the unknown regions where the uncertainty in
+%the surrogate model is large. The \emph{exploitation} means that the next point
+%tends to be the optimum which is predicted by the surrogate model with high
+%probability. Acquisition functions are introduced in Bayesian optimization to
+%balance the exploration and exploitation. Expected Improvement (EI)
+%is selected as the acquisition function in our proposed approach.
+%The expected improvement is weighted by the probability of satisfying the
+%constraints. The weighted EI (wEI) can well balance the exploration and
+%exploitation, and thus the wEI based Bayesian optimization framework can
+%significantly reduce the number of simulations while achieving better
+%optimization results.
+
+%The Bayesian optimization algorithm is further extended to handle
+%multi-objective optimization problems in this paper. We propose to transform
+%the multi-objective problems into single-objective problems that can be solved
+%by our proposed WEIBO algorithm by Tchebysheff
+%scalarization~\cite{MO_overview} with smooth relaxation.
+
+%% \textcolor{blue}{The Bayesian optimization has been applied to the optimization
+%% of temperature gradient and skew of 3D IC~\cite{TVLSI-3DIC}.
+%% In~\cite{TVLSI-3DIC}, the lower confidence bound (LCB) is selected as the
+%% acquisition function, however, the constraints are not considered. For
+%% automated analog circuit sizing, GASPAD method~\cite{liu2014gaspad} also employ
+%% the Gaussian process based surrogate models to approximate the objective
+%% functions.  With the surrogate model, the Differential Evolutionary (DE) like
+%% algorithm was used to explore the state space. However, the uncertainty
+%% information of design constraints are not well exploited in GASPAD to fully
+%% balance the exploitation and exploration. Our experimental results show that
+%% our proposed approach can achieve better performances with much less number of
+%% simulations compared with GASPAD. This is mainly because we maximize the
+%% acquisition function, i.e., weighted expected improvements, to optimally
+%% balance the exploration and exploitation.}
+
+%The proposed WEIBO method was tested with several test cases including two
+%passive components working at 60GHz, a low power operational amplifier, a power
+%amplifier, a voltage controlled oscillator (VCO), and a charge pump. Compared
+%with the state-of-the-art approaches listed in the paper, the proposed WEIBO method can achieve
+%better optimization results with significantly less number of simulations.
+
+%%\added{A summary of the contributions of this paper is as follows: firstly, we
+%%applied Bayesian optimization method to handle problems of analog IC synthesis,
+%%although Bayesian optimization has already been used in areas like tuning of
+%%neural network hyper-parameters, to the best of our knowledge, it has not been
+%%used for analog IC optimization, secondly, we propose an extension to the
+%%origin wEI-based Bayesian optimization so that it can handle constrained
+%%multi-objective circuit optimization.  }

### 2018-01-29 paper/main.tex
Update

@@
 
-% % You can specify symbols, otherwise they are numbered in order.
-% % Ideally, you should not use this facility. Affiliations will be numbered
-% % in order of appearance and this is the preferred way.
-% \icmlsetsymbol{equal}{*}
+% You can specify symbols, otherwise they are numbered in order.
+% Ideally, you should not use this facility. Affiliations will be numbered
+% in order of appearance and this is the preferred way.
+\icmlsetsymbol{equal}{*}
 
-% \begin{icmlauthorlist}
-% \icmlauthor{Aeiau Zzzz}{equal,to}
-% \icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-% \icmlauthor{Cieua Vvvvv}{goo}
-% \icmlauthor{Iaesut Saoeu}{ed}
-% \icmlauthor{Fiuea Rrrr}{to}
-% \icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
-% \icmlauthor{Aaoeu Iasoh}{goo}
-% \icmlauthor{Buiui Eueu}{ed}
-% \icmlauthor{Aeuia Zzzz}{ed}
-% \icmlauthor{Bieea C.~Yyyy}{to,goo}
-% \icmlauthor{Teoau Xxxx}{ed}
-% \icmlauthor{Eee Pppp}{ed}
-% \end{icmlauthorlist}
+\begin{icmlauthorlist}
+\icmlauthor{Aeiau Zzzz}{equal,to}
+\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
+\icmlauthor{Cieua Vvvvv}{goo}
+\icmlauthor{Iaesut Saoeu}{ed}
+\icmlauthor{Fiuea Rrrr}{to}
+\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
+\icmlauthor{Aaoeu Iasoh}{goo}
+\icmlauthor{Buiui Eueu}{ed}
+\icmlauthor{Aeuia Zzzz}{ed}
+\icmlauthor{Bieea C.~Yyyy}{to,goo}
+\icmlauthor{Teoau Xxxx}{ed}
+\icmlauthor{Eee Pppp}{ed}
+\end{icmlauthorlist}
 
-% \icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-% \icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-% \icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
+\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
+\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
+\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
 
-% \icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
+\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
 
-% % You may provide any keywords that you
-% % find helpful for describing your paper; these are used to populate
-% % the "keywords" metadata in the PDF but will not be shown in the document
-% \icmlkeywords{Bayesian Optimization, Automated analog circuit design}
+% You may provide any keywords that you
+% find helpful for describing your paper; these are used to populate
+% the "keywords" metadata in the PDF but will not be shown in the document
+\icmlkeywords{Bayesian Optimization, Automated analog circuit design}
 
@@
 
+\bibliography{ref}
+\bibliographystyle{icml2018}
+
 \end{document}

### 2018-01-29 paper/background.tex
Update
Paper update

@@
 \section{Background}
+
+\textcolor{red}{TODO: See how other people describe GP and BO}
 
@@
 
-\subsection{Gaussian Process}
+\textcolor{red}{TODO: The circuit performance comes from \bf{circuit} simulation}
+\textcolor{red}{TODO: format, citation of HSPICE/spectre}
 
-Basic introduction to GP
+We handle the scenarios that topology of the analog circuit is fixed, this is
+practical, as for each task, thare are usually a lot of classical topologies
+that can be used. Once the topology is fixed, the designer has to choose the
+optimal design parameters according to the specifications and the circuit
+device model. What we want to do is to automatically search for the optimal
+design parameters, this task can be formulated as a bound-constrained black-box optimization problem:
 
-\subsection{Acquisition Function}
+\begin{equation}
+    \label{eq:MOFormulation}
+    \text{minimize}~\mathrm{FOM}(\mathbf{x})
+\end{equation}
+where $\mathbf{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
+and $f_i(\mathbf{x})$ represents the $i$-th cared circuit performance like gain
+or phase margin of an amplifier. and the $\mathrm{FOM}(\mathbf{x})$ is the
+design objective. Given the design parameters $\bf{x}$, the FOM value can be
+obtained via circuit simulation using softwares like HSPICE or spectre.
 
-Introduce LCB, EI and PI
+\subsection{Gaussian Process Regression}
+
+\textcolor{red}{ALERT: COPIED FROM MY PAPER SUMBITTED TO DAC}
+
+The advantage of GP is that it not only provides a prediction like other
+regression models but also gives a well-calibrated uncertainty estimation. The
+uncertainties would be small in the regions with densely sampled data and large
+in the regions with few samples.
+
+GP is fully characterized by a mean function $m(\mathbf{x})$ and a covariance
+function $k(\mathbf{x}, \mathbf{y})$. In this work, we use the constant mean function
+$m(\mathbf{x}) = \mu_0$ and the squared exponential covariance function as follows to characterize the Gaussian process.
+\begin{equation}
+    \label{eq:GaussianCovarianceFunction}
+    k(\mathbf{x}_i, \mathbf{x}_j) = \sigma_f^2 \exp\Big(-\frac{1}{2}(\mathbf{x}_i - \mathbf{x}_j)^T\Lambda^{-1}(\mathbf{x}_i - \mathbf{x}_j)\Big),
+\end{equation}
+where $\Lambda = \mathrm{diag}(l_1, \dots, l_d)$ is a diagonal matrix and $l_i$ denotes the length scale of the $i$-th dimension. $\mu_0$, $\sigma_f$ and $\Lambda$ are the hyper-parameters.
+
+GP can be used to model a black-box function $f(x)$. Denote the hyper-parameters as a vector $\mathbf{\theta}$, given the training set
+$\{X, \mathbf{y}\}$, where $X = \{\mathbf{x_1}, \dots, \mathbf{x}_N\}$, $\mathbf{y} =
+(f(\mathbf{x}_1), \dots, f(\mathbf{x}_N))^T$. The log likelihood of the training
+set~\cite{GPML} can be expressed as
+\begin{equation}
+    \log \mathrm{p}(\mathbf{y} | X, \mathbf{\theta}) \propto -\frac{1}{2}(\mathbf{y} - \mu_0)^T K_{\mathbf{\theta}}^{-1}(\mathbf{y} - \mu_0) - \frac{1}{2} \log |K_{\mathbf{\theta}}|
+    \label{eq:LikeliHood}
+\end{equation}
+where $K_\theta({i, j}) = k(\mathbf{x}_i, \mathbf{x}_j)$. By maximizing the likelihood
+function \ref{eq:LikeliHood}, we can get the maximum likelihood estimation
+(MLE) of the hyper-parameters.
+
+Given a new data point $\mathbf{x}$, the prediction of $f(\mathbf{x})$ is
+not a scalar value, but a Gaussian distribution 
+\begin{equation}
+f(\mathbf{x}) \sim N(\mu(\mathbf{x}),
+\sigma^2(\mathbf{x}))
+\label{eq:GPRPred}
+\end{equation}
+where $\mu(\mathbf{x})$ and $\sigma^2(\mathbf{x})$ can be expressed as
+\begin{equation}
+    \left\{
+        \begin{array}{lll}
+            \mu(\mathbf{x}) &=& \mu_0 + k(\mathbf{x},X)K_{\mathbf{\theta}}^{-1}(\mathbf{y} - \mu_0) \\
+            \sigma^2(\mathbf{x}) &=& \sigma_f^2 - k(\mathbf{x}, X)K_{\mathbf{\theta}}^{-1}k(X, \mathbf{x})
+        \end{array}
+    \right..
+    \label{eq:GPRPredEqNoisy}
+\end{equation}
+where $k(\mathbf{x}, X) = (k(\mathbf{x}, \mathbf{x}_1), \dots, k(\mathbf{x}, \mathbf{x}_N))^T$ and
+$k(X, \mathbf{x}) = k(\mathbf{x}, X)^T$.  The $\mu(\mathbf{x})$ can be viewed as the
+prediction of the function value, while the $\sigma^2(\mathbf{x})$ is a measure of
+uncertainty. We refer readers
+to~\cite{GPML} for more details of GP.
+
+\subsection{Bayesian Optimization}
+
+Bayesian optimization~\cite{shahriari2016taking} was proposed for the optimization
+of expensive black-box functions. It consists of two essential ingredients,
+i.e., the probabilistic surrogate models and an acquisition function. The
+probabilistic surrogate models provide the prediction with uncertainties. They are
+refined incrementally with newly observed data. Acquisition function is used to
+explore the state space based on the surrogate model optimally.
+
+In this subsection, we introduce the single-objective Bayesian optimization,
+our extension to multi-objective optimization would be described in the next
+subsection.
+
+Without loss of generality, we only consider the minimization problem. For a
+black-box function $f(\mathbf{x})$, we aim to find the global minimum.
+\begin{equation}
+    \label{eq:BO_Formulation}
+    \mathbf{x}_* = \arg\min_{x} f(\mathbf{x})
+\end{equation}
+
+The GP model is the \emph{de facto} surrogate model for Bayesian optimization.
+In Bayesian optimization, the black-box function $f(x)$ is modeled by the GP
+model (\ref{eq:GPRPred}). Through an acquisition function, the prediction and
+its uncertainty estimation can be combined to guide the optimization
+procedure efficiently.
+
+In Bayesian optimization, the acquisition function is constructed to balance
+the exploration and exploitation. By optimizing the acquisition function, the
+next data point which can efficiently explore the state space.  We consider an
+acquisition function lower confidence bound (LCB)~\cite{liu2014gaspad} defined
+as follows.
+\begin{equation}
+    \label{eq:LCB}
+    \mathrm{LCB}(\mathbf{x}) = \mu(\mathbf{x}) - \kappa \sigma(\mathbf{x})
+\end{equation}
+where $\mu(\mathbf{x})$ and $\sigma(\mathbf{x})$ are derived from the GP prediction, and
+$\kappa$ is a user-defined parameter, We set $\kappa = 3$ in this work. As can
+be seen, the prediction and uncertainty estimation are combined in the LCB function.
+
+The LCB function would have a low value if $\mu(\mathbf{x})$ is low, or the
+uncertainty $\sigma(\mathbf{x})$ is high. It means that we tend to visit the data
+point where $f(x)$ is minimized based on the prediction and also the region
+where the prediction uncertainty is large.
+
+Starting from a set of initial data points, in each iteration of Bayesian
+optimization, a GP model is trained using the existing data points. The
+acquisition function, e.g., the LCB function is then constructed, and existing
+optimization algorithms can be applied to optimize the acquisition function.
+The optimum of the acquisition function is then selected as the next data point
+to be evaluated. Note that, during the optimization of the acquisition
+function, only the evaluations of the GP models are involved, which are
+computationally efficient.
+
+Besides LCB, there also exist other acquisition functions like expected
+improvement~\cite{bull2011convergence}, Thompson
+sampling~\cite{chapelle2011empirical}, and predictive entropy
+search~\cite{hernandez2014predictive}. A portfolio of several different
+acquisition functions is also possible~\cite{hoffman2011portfolio}.

### 2018-01-29 paper/intro.tex
Paper update

--- 2018-01-28 paper/intro.tex
@@
 
-Automated analog IC design is very important
+% % TODO: more introduction to the importance of anlog IC sizing, as the reviewers may not have much knowledge of circuit design
+Automated analog circuit design has been a challenging problem for the
+community of electronic design automation (EDA). Unlike digital circuits, where
+the design flow is highly automated, analog circuit design still
+heavily relies on designer's experience. The design parameters of analog circuits like
+transistor widths and lengths need to be manually calculated based on the
+specifications and the designers' understanding of the circuit. However, due to
+the ever-scaling IC manufacture technology and the increasing demands for
+high-performance, low-power circuits, it is getting much more difficult to meet
+the performance and time-to-market requirement with manual circuit design.
+Automated analog circuit design has thus attracted more research interests in
+the past decade~\cite{rutenbar2007hierarchical}.
 
-Traditional methods using offline model and simulated based methods are not good
+% TODO: Traditional methods using offline model and simulated based methods are
+% not good
+The analog circuit design automation problems can be formulated as optimization
+problems, the aim is to find the optimal vector of design parameters that give
+best figure of merit (FOM). Prior works about analog circuit optimization
+include offline model-based approaches
+~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
+simulation based approaches. The offline model-based methods try to build
+accurate global model and then apply global optimization algorithms to the
+cheap-to-evaluate models, the model either comes from designers' manual
+derivation or from regression models like SVM and ANN. The problem of this
+approach is that the accurate models are usually hard to get, for example,
+in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
+a sparse polynomial model for a circuit with ten design parameters.
+Simulation-based methods, instead, treat the circuits as black-box functions
+that get the objective value from circuit simulations, global optimization
+algorithms are directly applied to the black-box functions. For
+simulation-based circuit optimization methods, meta-heuristic algorithms like
+particle swarm intelligence (PSO)~\cite{phelps2000anaconda} and differential
+evolution algorithm (DE)~\cite{liu2009analog} are widely used, although these
+algorithm are able to explore the whole design space, they have relatively low
+convergence rate and consume many circuit simulations. When the circuit
+simulation takes a long time, both model-based and simulation-based approaches
+can be prohibitive.
 
-Bayesian optimization has been applied, and outperformed many other algorithm
+% TODO: Bayesian optimization is a sequential algorithm, there is a need to
+% parallelize it
+%
+% TODO: cite the two 3D-IC papers of TVLSI
+To reduce the circuit simulations needed by the optimization, the Gaussian
+process (GP)~\cite{GPML} model has been introduced as online surrogate model to
+assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
+differential evolution algorithm, in~\cite{lyu2017efficient}. Recently, the
+Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for analog circuit
+optimization, the Bayesian optimization algorithm is firstly introduced for the
+automated design of general analog circuits, and has shown very good
+performance compared to other simulation-based approaches,
+in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined
+with adaptive Monte-Carlo sampling to optimize the yield of analog circuits and
+static random-access memory (SRAM).
 
-Bayesian optimization is a sequential algorithm, there is a need to parallelize it
+The Bayesian optimization algorithm is a well-studied algorithm, and has
+demonstrated to be a promising algorithm for automated analog circuit design,
+however, the standard Bayesian optimization algorithm is sequential, it chooses
+the next evaluation point by optimizing the specified acquisition fucntion,
+which makes the parallelization of Bayesian optimization non-trivial. The
+sequential property of BO limits its further application, as multi-core
+processors are usually availble for modern computers.
 
-Review current methods
+% TODO: Review current methods
+% TODO: See how other papers review existing batched BO methods
+Batched Bayesian optimization has been a \textcolor{red}{hot} topic in the BO
+literature. Related works include the \emph{simulation matching}
+method~\cite{azimi2010batch}, the \emph{BUCB} (BLCB for minimization)
+method~\cite{desautels2014parallelizing}, the \emph{GP-UCB-PE}
+method~\cite{contal2013parallel}, the \emph{local penalization}
+method~\cite{gonzalez2016batch}, the \emph{parallel predictive entropy
+search}~\cite{shah2015parallel} and the \emph{qKG}
+method~\cite{wu2016parallel}.
 
-Beiefly introduce my algorithm
+% BUCB, UCB-PE: regret bound
+% PPES: entropy search
+% qKG, qEI: optimal decision if multiple points are selected
+% LP: very good heuristic
+
+% TODO: Beiefly introduce my algorithm
+All the above mentioned algorithms choose to use one acquisition function, and
+except for the smulation mathcing method and local penalization method which
+can select arbitrary acquisition function, other parallelization methods rely on
+specific acquisition function, the UCB acquisition fucntion must be used for
+BUCB and GP-UCB-PE, and the knowledge gradient method must be used for qKG
+algorithm. As has been stated in~\cite{hoffman2011portfolio}, no one
+acquisition fucntion can always outperform other acquisition functions, so
+relying on one acquisition fucntion may resulting in poor performance. Also, a
+portfolio strategy that ensembles multiple acquisition functions would be
+helpful.
+
+In this paper, we propose to parallize the Bayesian optimization algorithm via
+a multi-objective ensemble of acquisition functions. Firstly, in each
+iteration, after the GP model is updated, multiple acquisition functions are
+selected, we then perform multi-objective optimization to find the \emph{Pareto
+front} (PF) of the acquisition functions. The PF represents the best trade-off
+between these acquisition functions, when used in sequential mode, the propose
+multi-objective acquisition ensemble (MACE) strategy can be seen as a portfolio
+strategy, when batched evaluation is possible, we can sample multiple points on
+the PF as there are usually much more points on the PF than the batch size.
+
+We tested the MACE algorithm using several analytical benchmark functions and
+two real-world analog circuits, including an operational amplifier with
+\textcolor{red}{14} design parameters and a class-E power amplifier with
+\textcolor{red}{ten} design parameters. The BLCB method, local penalization
+method with expected improvement acquisition fucntion (EI-LP), the qEI methods
+and qEI methods are compared with MACE. The proposed MACE method achieved
+competitive performance when compared with the listed state-of-the-art
+algorithms.

### 2018-01-29 paper/mace.tex
Paper update

@@
 
-\subsection{Multi-objective optimization}
+\subsection{Multi-objective Optimization}\label{sec:MOForumlation}
+
+\textcolor{red}{See how other MOBO paper formulate multi-objective optimization}
+
+\textcolor{red}{ALERT: COPIED FROM MY TCAS-I paper}
+
+When we have more than one objective to optimize, the problem is formulated as:
+\begin{equation}
+    \label{eq:MOFormulation}
+    \begin{aligned}
+        & \text{minimize} & & f_1(\mathbf{x}),~\dots~,f_m(\mathbf{x})
+    \end{aligned}
+\end{equation}
+
+Unlike the single-objective problem, there is usually no \emph{best} design for
+a multi-objective problem, as objectives can be conflicting, and it is unlikely
+to optimize all of them simultaneously. The goal of a multi-objective
+optimization algorithm is to find a set of solutions to approximate the
+$\emph{Pareto front}$. A solution $\bf{x}_1$ is said to \emph{dominate} a
+solution $\bf{x}_2$ if $\forall i \in \{1 \dots m\},~f_i(\bf{x}_1) \le
+f_i(\bf{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bf{x}_1) < f_j(\bf{x}_2)$.
+A point $\bf{x}_*$ is $\emph{weakly Pareto-optimal}$ if $\forall \bf{x} \in
+\bf{\textrm{X}}$, $\bf{x}_*$ is not dominated by $\bf{x}$.  A point $\bf{x}_*$
+is $\emph{Pareto-optimal}$ if $\forall x \in \bf{\textrm{X}}$, $\bf{x}_*$ is
+not dominated by $\bf{x}$ and $\exists i \in \{1 \dots m\},~f_i(\bf{x}_*) <
+f_i(\bf{x})$. The set of Pareto optimal outcomes is called the \emph{Pareto
+front}.
 
@@
 
+% TODO: discuss the difference of acquisition functions: LCB: do not avoid repeated sampling, EI: always positive
+
 \textcolor{red}{Plot a figure to illustrate the PF/PS of acquisition functions}

### 2018-01-30 paper/background.tex
Paper update

--- 2018-01-28 paper/background.tex
@@
 \section{Background}
+
+% TODO: See how other people describe GP and BO}
 
@@
 
-We formulate the sizing problem as an optimization problem
+% TODO: The circuit performance comes from \bf{circuit} simulation}
+% TODO: format, citation of HSPICE/spectre}
+% TODO: See how other analog circuit optimization paper formulate the problem}
 
-\subsection{Gaussian Process}
+We handle the scenarios where topology of the analog circuit is fixed, this is
+practical as thare are usually a lot of classical topologies for given design
+task. Once the circuit topology is fixed, the designer has to choose the
+appropriate design parameters according to the specifications and the circuit
+device model. What we want to do is to automatically search for the optimal
+design parameters, the problem can then be formulated as a bound-constrained
+black-box optimization problem:
 
-Basic introduction to GP
+\begin{equation}
+    \label{eq:Formulation}
+    \text{minimize}~\mathrm{FOM}(\bm{x})
+\end{equation}
 
-\subsection{Acquisition Function}
+where $\bm{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
+and $f_i(\bm{x})$ represents the $i$-th cared circuit performance like gain
+or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
+design objective. Given the design parameters $\bf{x}$, the FOM value can be
+obtained via circuit simulation using softwares like HSPICE or spectre.
 
-Introduce LCB, EI and PI
+% TODO: Explain the noise
+
+\subsection{Gaussian Process Regression}
+
+\textcolor{red}{ALERT: COPIED FROM MY PAPER SUMBITTED TO DAC}
+
+We model the $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} with Gaussian
+process (GP) model~\cite{GPML}. The GP model is the most commonly used model
+for Bayesian optimization, the advantage of GP is that it can give a
+well-calibrated uncertainty of prediction. GP is characterized by a mean
+function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
+paper, we use squared-exponential ARD kernel, and a constant mean fucntion
+$m(\bm{x}) = \mu_0$ for all our experiments.
+
+Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
+not a scalar value, but a predictive distribution 
+\begin{equation}
+f(\bm{x}) \sim N(\mu(\bm{x}),
+\sigma^2(\bm{x}))
+\label{eq:GPRPred}
+\end{equation}
+where $\mu(\bm{x})$ and $\sigma^2(\bm{x})$ can be expressed as
+\begin{equation}
+        \begin{array}{lll}
+            \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
+            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x})
+        \end{array}
+    \label{eq:GPRPredEqNoisy}
+\end{equation}
+where $k(\bm{x}, X) = (k(\bm{x}, \bm{x}_1), \dots, k(\bm{x},
+\bm{x}_N))^T$ and $k(X, \bm{x}) = k(\bm{x}, X)^T$. The
+$\mu(\bm{x})$ can be viewed as the prediction of the function value, while
+the $\sigma^2(\bm{x})$ is a measure of uncertainty.
+
+\subsection{Bayesian Optimization}
+
+Bayesian optimization~\cite{shahriari2016taking} was proposed for the
+optimization of expensive black-box functions. It consists of two essential
+ingredients, i.e., the probabilistic surrogate models and an acquisition
+function. The probabilistic surrogate models provide the prediction with
+uncertainties. They are refined incrementally with newly observed data.
+Acquisition function is used to explore the state space based on the surrogate
+model optimally. The procedure of Bayesian optimization is described in
+Algorithm~\ref{alg:BayesianOptAlgo}.
+
+\begin{algorithm}
+\caption{Bayesian Optimization}
+\label{alg:BayesianOptAlgo}
+\begin{algorithmic}[1]
+\STATE Initial Sampling
+\STATE Construct initial GP model
+\FOR{t = 1, 2, \dots}
+\STATE Construct the acquisition function
+\STATE Find $\bm{x}_t$ that optimizes the acquisition function
+\STATE Sample $y_t = f(\bm{x}_t)$
+\STATE Update probabilistic surrogate model
+\ENDFOR
+\STATE Return best $f(\bm{x})$ recorded during iterations
+\end{algorithmic}
+\end{algorithm}
+
+In Bayesian optimization described in Algorithm~\ref{alg:BayesianOptAlgo}, the acquisition function is used to balance the exploration and exploitation during the optimization.
+The acquisition fucntion considers both the predictive value and the uncertainty.
+There are a lot of existing acquisition functions, examples include the lower confidence bound (LCB), expected improvement (EI) and probability of improvement (PI).
+
+The LCB fucntion is defined as follows:
+\begin{equation}
+    \label{eq:LCB}
+\end{equation}
+Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP. $\kappa$ is a parameter that balances the exploitation and exploration.
+
+Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
+\begin{equation}
+    \label{eq:LCB}
+    \begin{array}{lll}
+        \kappa &=& \sqrt{\nu \tau_t} \\
+        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta)
+    \end{array}
+\end{equation}
+Where $t$ is the number of current iteration.
+$\nu$ and $\delta$ are two user defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.

### 2018-01-30 paper/intro.tex
Paper update

@@
 % TODO: cite the two 3D-IC papers of TVLSI
-To reduce the circuit simulations needed by the optimization, the Gaussian
-process (GP)~\cite{GPML} model has been introduced as online surrogate model to
-assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
-differential evolution algorithm, in~\cite{lyu2017efficient}. Recently, the
-Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for analog circuit
-optimization, the Bayesian optimization algorithm is firstly introduced for the
-automated design of general analog circuits, and has shown very good
-performance compared to other simulation-based approaches,
+To reduce the number of circuit simulations, the Gaussian process
+(GP)~\cite{GPML} model has been introduced as online surrogate model to assist
+the optimization. In~\cite{liu2014gaspad}, GP is combined with differential
+evolution algorithm, in~\cite{lyu2017efficient}. Recently, the Bayesian
+optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for
+analog circuit optimization, the Bayesian optimization algorithm is firstly
+introduced for the automated design of general analog circuits, and has shown
+very good performance compared to other simulation-based approaches,
 in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined

### 2018-01-30 paper/abstract.tex
Paper update

@@
     The Bayesian optimization has recently shown promising performance for
-    automated analog circuit design, however, the sequential property of
+    automated analog circuit design. However, the sequential property of
     Bayesian optimization limits its further application. In this paper, a
@@
     functions and real-world analog circuits; the experimental results show
-    that the proposed method is competitive with state-of-the-art methods.
+    that the proposed method is competitive compared to the state-of-the-art
+    methods.
 \end{abstract}

### 2018-01-30 paper/background.tex
Paper update

@@
 function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
-paper, we use squared-exponential ARD kernel, and a constant mean fucntion
+paper, we use squared-exponential ARD kernel, and a constant mean function
 $m(\bm{x}) = \mu_0$ for all our experiments.
@@
 In Bayesian optimization described in Algorithm~\ref{alg:BayesianOptAlgo}, the acquisition function is used to balance the exploration and exploitation during the optimization.
-The acquisition fucntion considers both the predictive value and the uncertainty.
-There are a lot of existing acquisition functions, examples include the lower confidence bound (LCB), expected improvement (EI) and probability of improvement (PI).
+The acquisition function considers both the predictive value and the uncertainty.
+There are a lot of existing acquisition functions, examples include the lower confidence bound (LCB), the probability of improvement (PI), and the expected improvement (EI).
 
-The LCB fucntion is defined as follows:
+The LCB function is defined as follows:
 \begin{equation}
     \label{eq:LCB}
+    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x})
 \end{equation}
@@
 $\nu$ and $\delta$ are two user defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.
+
+The PI and EI function are defined as
+\begin{equation}
+    \label{eq:PI_EI}
+    \begin{array}{lll}
+        \mathrm{PI}(\bm{x}) &=& \Phi(\lambda) \\
+        \mathrm{EI}(\bm{x}) &=& \sigma(\bm{x}) (\lambda \Phi(\lambda) + \phi(\lambda))     \\
+        \mathrm{\lambda}    &=& \displaystyle \frac{\tau - \xi - \mu(\bm{x})}{\sigma(\bm{x})}, 
+    \end{array}
+\end{equation}
+where $\tau$ is the current best value objective value, and $\xi$ is a small positive jitter to improvement the ability of exploration.
+The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution.
+
+% TODO: discuss the different behaviours of LCB, EI, PI
+
+There are also other acquisition function, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}.
+A portforlio of several acquisition function is also possible~\cite{hoffman2011portfolio}.

### 2018-01-30 paper/intro.tex
Paper update

@@
 problems, the aim is to find the optimal vector of design parameters that give
-best figure of merit (FOM). Prior works about analog circuit optimization
+the best figure of merit (FOM). Prior works about analog circuit optimization
 include offline model-based approaches
 ~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
-simulation based approaches. The offline model-based methods try to build
-accurate global model and then apply global optimization algorithms to the
-cheap-to-evaluate models, the model either comes from designers' manual
-derivation or from regression models like SVM and ANN. The problem of this
-approach is that the accurate models are usually hard to get, for example,
+simulation-based approaches. The offline model-based methods try to build
+accurate global models and then apply global optimization algorithms to the
+cheap-to-evaluate models. The model either comes from designers' manual
+derivation or regression models like SVM and ANN. The problem of this approach
+is that the accurate models are usually hard to get, for example,
 in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
@@
 Simulation-based methods, instead, treat the circuits as black-box functions
-that get the objective value from circuit simulations, global optimization
-algorithms are directly applied to the black-box functions. For
-simulation-based circuit optimization methods, meta-heuristic algorithms like
-particle swarm intelligence (PSO)~\cite{phelps2000anaconda} and differential
-evolution algorithm (DE)~\cite{liu2009analog} are widely used, although these
-algorithm are able to explore the whole design space, they have relatively low
+that get the FOM value from circuit simulations, global optimization algorithms
+are then directly applied to the black-box functions. For simulation-based
+circuit optimization methods, meta-heuristic
+algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used, although
+these algorithms can explore the whole design space, they have relatively low
 convergence rate and consume many circuit simulations. When the circuit
 simulation takes a long time, both model-based and simulation-based approaches
-can be prohibitive.
+can be very time-consuming.
 
@@
 To reduce the number of circuit simulations, the Gaussian process
-(GP)~\cite{GPML} model has been introduced as online surrogate model to assist
-the optimization. In~\cite{liu2014gaspad}, GP is combined with differential
-evolution algorithm, in~\cite{lyu2017efficient}. Recently, the Bayesian
-optimization (BO)~\cite{shahriari2016taking} algorithm has been applied for
-analog circuit optimization, the Bayesian optimization algorithm is firstly
-introduced for the automated design of general analog circuits, and has shown
-very good performance compared to other simulation-based approaches,
-in~\cite{wang2017efficient}, the Bayesian optimization algorithm is combined
-with adaptive Monte-Carlo sampling to optimize the yield of analog circuits and
-static random-access memory (SRAM).
+(GP)~\cite{GPML} model has been introduced as an online surrogate model to
+assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
+differential evolution algorithm, Recently, the
+Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
+applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
+firstly introduced for the automated design of general analog circuits and has
+shown to be more sample-efficient compared to other simulation-based
+approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
+is combined with adaptive Monte-Carlo sampling to optimize the yield of analog
+circuits and static random-access memory (SRAM).
 
-The Bayesian optimization algorithm is a well-studied algorithm, and has
-demonstrated to be a promising algorithm for automated analog circuit design,
-however, the standard Bayesian optimization algorithm is sequential, it chooses
-the next evaluation point by optimizing the specified acquisition fucntion,
+The Bayesian optimization algorithm is a well-studied algorithm and has
+demonstrated to be a promising algorithm for automated analog circuit design.
+However, the standard Bayesian optimization algorithm is sequential; it chooses
+the next evaluation point by optimizing the specified acquisition function,
 which makes the parallelization of Bayesian optimization non-trivial. The
-sequential property of BO limits its further application, as multi-core
-processors are usually availble for modern computers.
+sequential property of BO limits its further application in multi-core computer
+systems.
 
@@
 % TODO: Beiefly introduce my algorithm
-All the above mentioned algorithms choose to use one acquisition function, and
-except for the smulation mathcing method and local penalization method which
-can select arbitrary acquisition function, other parallelization methods rely on
-specific acquisition function, the UCB acquisition fucntion must be used for
-BUCB and GP-UCB-PE, and the knowledge gradient method must be used for qKG
+All the algorithms mentioned above choose to use one acquisition function, and
+except for the simulation matching method and local penalization method which
+can select arbitrary acquisition function, other parallelization methods rely
+on specific acquisition function, the UCB acquisition function must be used for
+BUCB and GP-UCB-PE, and the knowledge gradient method must be used for the qKG
 algorithm. As has been stated in~\cite{hoffman2011portfolio}, no one
-acquisition fucntion can always outperform other acquisition functions, so
-relying on one acquisition fucntion may resulting in poor performance. Also, a
-portfolio strategy that ensembles multiple acquisition functions would be
-helpful.
+acquisition function can always outperform other acquisition functions, so
+relying on one acquisition function may resulting in poor performance.
 
-In this paper, we propose to parallize the Bayesian optimization algorithm via
-a multi-objective ensemble of acquisition functions. Firstly, in each
-iteration, after the GP model is updated, multiple acquisition functions are
-selected, we then perform multi-objective optimization to find the \emph{Pareto
-front} (PF) of the acquisition functions. The PF represents the best trade-off
-between these acquisition functions, when used in sequential mode, the propose
+In contrast to existing batched bayesian optimization methods, we propose a
+different perspective to the parallelization of Bayesian optimization. In this
+paper, we propose to parallelize the Bayesian optimization algorithm via a
+multi-objective ensemble of acquisition functions. Firstly, in each iteration,
+after the GP model is updated, multiple acquisition functions are selected, we
+then perform multi-objective optimization to find the \emph{Pareto front} (PF)
+of the acquisition functions. The PF represents the best trade-off between
+these acquisition functions. When used in sequential mode, the proposed
 multi-objective acquisition ensemble (MACE) strategy can be seen as a portfolio
@@
 
-We tested the MACE algorithm using several analytical benchmark functions and
+The MACE algorithm is tested using several analytical benchmark functions and
 two real-world analog circuits, including an operational amplifier with
@@
 \textcolor{red}{ten} design parameters. The BLCB method, local penalization
-method with expected improvement acquisition fucntion (EI-LP), the qEI methods
+method with expected improvement acquisition function (EI-LP), the qEI methods
 and qEI methods are compared with MACE. The proposed MACE method achieved

### 2018-01-30 paper/mace.tex
Paper update

--- 2018-01-28 paper/mace.tex
@@
 
-\subsection{Multi-objective optimization}
+\subsection{Multi-objective Optimization of Acquisition Functions}\label{sec:MOForumlation}
+
+\textcolor{red}{See how other MOBO paper formulate multi-objective optimization}
+
+\textcolor{red}{ALERT: COPIED FROM MY TCAS-I paper}
+
+Multi-objective optimization~\cite{MO_overview} can be formulated as:
+\begin{equation}
+    \label{eq:MOFormulation}
+    \begin{aligned}
+        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x})
+    \end{aligned}
+\end{equation}
+
+For multi-objective optimization, there are more than one objecive to optimize, and usually there does not exist a single solution that simultaneously optimize all these objectives.
+A design $\bm{x}_1$ is said to be \emph{dominate} by $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
+A design is \emph{Pareto-optimal} if it is not dominated by any other point and dominate at least one point.
+The whole set of the non-dominated points in the design space is called the \emph{Pareto set}, and the set of non-dominated points in the objective space is called the \emph{Pareto front}.
+It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
+
+There exist many mature multi-objective optimization algorithms, like the non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the multi-objective evolutionary algorithm based on decomposition (MOEA/D)~\cite{moead}.
+In this paper, the multi-objective optimization based on differential evolution (DEMO)~\cite{demo} is used to solve multi-objective optimization problems.
+
+% When we have more than one objective to optimize, the problem is formulated as:
 
@@
 
-\textcolor{red}{Plot a figure to illustrate the PF/PS of acquisition functions}
+We propose a novel heuristic for the parallelization of Bayesian optimization.
+The parallelization is realized via multi-objective ensemble of multiple
+acquisition functions. When we have multiple acquisition functions built from
+the same GP model, they may not disagree with each other about which point is
+most promising, for example, the value of LCB function always decreases as the
+$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma{\bm{x}}$
+increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and
+increase when $\mu(\bm{x}) > \tau$.
+
+% TODO: discuss the difference of acquisition functions: LCB: do not avoid repeated sampling, EI: always positive
+
+With multi-objective optimization, the disagreement between different
+acquisition function can be used for the parallelization of Bayesian
+optimization. In the standard Bayesian optimization, one acquisition function
+is specified, and in each iteration, the single-objective optimization is
+performed to optimize the acquisition function; in our proposed MACE algorithm,
+multiple acquisition function is pre-specified by the user, in each iteration,
+the DEMO multi-objective optimization algorithm is applied to find the Pareto
+front of the acquisition functions. Once the Pareto front is obtained, we can
+then sample from the Pareto front, and then evaluate these sampled points in
+parallel.
+
+% TODO: We illustrate the proposed MACE algorithm using the Branin-Hoo function~\cite{dixon1978global}
+% TODO: plot contour of Branin/Ei/LCB/PI, plot the PS and the PF
+
+We select the LCB, EI and PI acquisition function in our implementation of the MACE algorithm, but other acquisition functions like KG and PES can also be incorporated into the MACE framework.
+The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
+
+\begin{algorithm}
+\caption{Multi-objective Acquisition Ensemble Algorithm}
+\label{alg:MACE}
+\begin{algorithmic}[1]
+\STATE Initial Sampling
+\STATE Construct initial GP model
+\FOR{t = 1, 2, \dots}
+    \STATE Construct the LCB, EI and PI function according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
+    \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
+    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front
+    \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
+    \STATE Update the GP model
+\ENDFOR
+\STATE Return best $f(\bm{x})$ recorded during iterations
+\end{algorithmic}
+\end{algorithm}

### 2018-01-30 paper/main.tex
Paper update

@@
 \usepackage{booktabs} % for professional tables
+
+% Added by wenlong lyu
+\usepackage{amsmath}
+\usepackage[plain]{fancyref}
+\usepackage{bookmark}
+\usepackage{bm}
+\usepackage{todonotes}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Submission and Formatting Instructions for ICML 2018}
+\icmltitlerunning{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
 
@@
 \twocolumn[
-\icmltitle{Batched Bayesian Optimization via Multi-objective Acquisition Function Ensemble for Automated Analog Circuit Design}
+\icmltitle{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
 

### 2018-01-31 paper/intro.tex
Paper update

@@
 applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
-firstly introduced for the automated design of general analog circuits and has
+firstly introduced for the single- and multi-objective optimization of general analog circuits and has
 shown to be more sample-efficient compared to other simulation-based

### 2018-01-31 paper/experiments.tex
Update
Paper update

@@
 \section{Experimental Results}
+
+% TODO: more details about the setup of experiments
+
+We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{We implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloade from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}.
+The MACE algorithm and the BLCB algorithm are implemented using c++ language.
 
@@
 
+We tested the MACE algorithm and other parallel BO method using seven benchmark
+functions, including the branin function, the alpine1 function, the 6D hartmann
+function, the 2D and 10D ackley function and the 2D and 10D Rosenbrock
+function. The dimensions and design space are summarized in Table~ref{tab:summaryanalygical}.
+
+% \begin{table}[htbp]
+%     \small
+%     \centering
+%     \caption{Summary of the analytical benchmark functions}
+%     \label{tab:summaryanalygical}
+%     \begin{tabular}
+%         \toprule
+%         Function     & Dimension    & SearchDomain         \\ 
+%         \midrule
+%         Branin       & 2            & $[-5, 10]\times[0, 15]$ \\
+%         Alpine1      & 5            & $[-10, 10]^5$           \\
+%         Hartmann6    & 6            & $[0, 1]^6$              \\
+%         Ackley2      & 2            & $[-32, 32]^2$           \\
+%         Ackley10     & 10           & $[-32, 32]^10$          \\
+%         Rosenbrock2  & 2            & $[-5, 10]^2$            \\
+%         Rosenbrock10 & 10           & $[-20, 20]^10$          \\
+%         \bottomrule
+%     \end{tabular}
+% \end{table}
+
+\begin{table}[htbp]
+    \centering
+    \caption{Summary of the analytical benchmark functions}
+    \label{tab:summaryanalygical}
+    \begin{tabular}{llllllll}
+        \toprule
+        Function            & Dimension        & Search domain    \\ \midrule
+         Branin             & 2                & $[-5, 10]\times[0, 15]$ \\
+         Alpine1            & 5                & $[-10, 10]^5$           \\
+         Hartmann6          & 6                & $[0, 1]^6$              \\
+         Ackley2            & 2                & $[-32, 32]^2$           \\
+         Ackley10           & 10               & $[-32, 32]^{10}$          \\
+         Rosenbrock2        & 2                & $[-5, 10]^2$            \\
+         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
 \begin{enumerate}
+        \item Branin
+        \item Alpine1
         \item Hart6
-        \item Alpine1
-        \item Branin
         \item Rosenbrock-2
@@
 
-\begin{figure}[]
+\begin{figure}[htbp]
 \vskip 0.2in
@@
 \end{figure}
+
+\subsection{ClassE Power Amplifier}
+
+\textcolor{red}{TODO: qKG and qEI}
+
+\begin{figure}[htbp]
+\vskip 0.2in
+\begin{center}
+\centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
+\caption{Optimization results of the class-E power amplifier}
+\label{resDAC2014}
+\end{center}
+\vskip -0.2in
+\end{figure}

### 2018-01-31 paper/mace.tex
Paper update

@@
 the same GP model, they may not disagree with each other about which point is
-most promising, for example, the value of LCB function always decreases as the
-$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma{\bm{x}}$
+most promising. For example, the value of LCB function always decreases as the
+$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$
 increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and
@@
 acquisition function can be used for the parallelization of Bayesian
-optimization. In the standard Bayesian optimization, one acquisition function
-is specified, and in each iteration, the single-objective optimization is
-performed to optimize the acquisition function; in our proposed MACE algorithm,
-multiple acquisition function is pre-specified by the user, in each iteration,
-the DEMO multi-objective optimization algorithm is applied to find the Pareto
-front of the acquisition functions. Once the Pareto front is obtained, we can
-then sample from the Pareto front, and then evaluate these sampled points in
-parallel.
+optimization, as best trade-off between these acquisition functions can be
+captured by the Pareto front.
+
+In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected, but other acquisition functions like KG and PES can also be incorporated into the MACE framework.
+In each iteration, the following MO problem is constructed:
+\begin{equation}
+    \label{eq:MO_LCB_EI_PI}
+    \begin{aligned}
+        & \text{minimize} & & \mathrm{LCB}(\bm{x}),~-\mathrm{EI}(\bm{x}),~-\mathrm{PI}(\bm{x}).
+    \end{aligned}
+\end{equation}
+Then the DEMO multi-objective optimization algorithm is applied to solve \eqref{eq:MO_LCB_EI_PI}.
+Once the Pareto front of LCB, EI and PI is obtained, the candidate evalution points are then randomly sampled from the Pareto front.
 
@@
 
-We select the LCB, EI and PI acquisition function in our implementation of the MACE algorithm, but other acquisition functions like KG and PES can also be incorporated into the MACE framework.
 The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
@@
 \FOR{t = 1, 2, \dots}
-    \STATE Construct the LCB, EI and PI function according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
+    \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
     \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
-    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front
+    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front where B is the batch size
     \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$

### 2018-01-31 paper/experiments.tex
Paper update

@@
 
-We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{We implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloade from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}.
+We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{Although there are availble open source implementation of BLCB, we implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloaded from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}.
 The MACE algorithm and the BLCB algorithm are implemented using c++ language.
@@
 function, the 2D and 10D ackley function and the 2D and 10D Rosenbrock
-function. The dimensions and design space are summarized in Table~ref{tab:summaryanalygical}.
-
-% \begin{table}[htbp]
-%     \small
-%     \centering
-%     \caption{Summary of the analytical benchmark functions}
-%     \label{tab:summaryanalygical}
-%     \begin{tabular}
-%         \toprule
-%         Function     & Dimension    & SearchDomain         \\ 
-%         \midrule
-%         Branin       & 2            & $[-5, 10]\times[0, 15]$ \\
-%         Alpine1      & 5            & $[-10, 10]^5$           \\
-%         Hartmann6    & 6            & $[0, 1]^6$              \\
-%         Ackley2      & 2            & $[-32, 32]^2$           \\
-%         Ackley10     & 10           & $[-32, 32]^10$          \\
-%         Rosenbrock2  & 2            & $[-5, 10]^2$            \\
-%         Rosenbrock10 & 10           & $[-20, 20]^10$          \\
-%         \bottomrule
-%     \end{tabular}
-% \end{table}
+function. The dimensions and design space are summarized in
+Table~ref{tab:summaryanalygical}.
 
@@
 
-\begin{enumerate}
-        \item Branin
-        \item Alpine1
-        \item Hart6
-        \item Rosenbrock-2
-        \item Rosenbrock-10
-        \item Ackley-2
-        \item Ackley-10
-\end{enumerate}
+For all functions except the two 10D functions, we set the number of initial random sampling to $N_{init} = 20$ and the number of iterations to 45, and set to batch size $B$ to $B = 1$ and $B=4$ respectively,  the total number of function evaluations is $N_{init} + B \times iter$.
+For the 10D ackley and 10D rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$ and the number of iterations is fixed to 175.
+The experiments were repeated for ten times to average the random fluctuations.
+The convergence plot are shown in Figure~\ref{fig:CovPlotBenchmark}.
+
+\begin{table}[htbp]
+    \centering
+    \caption{Summary of the analytical benchmark functions}
+    \label{tab:summaryanalygical}
+    \begin{tabular}{llllllll}
+        \toprule
+        Function            & Dimension        & Search domain    \\ \midrule
+         Branin             & 2                & $[-5,  10]\times[0, 15]$ \\
+         Alpine1            & 5                & $[-10, 10]^5$           \\
+         Hartmann6          & 6                & $[0,   1]^6$              \\
+         Ackley2            & 2                & $[-32, 32]^2$           \\
+         Rosenbrock2        & 2                & $[-5,  10]^2$            \\
+         Ackley10           & 10               & $[-32, 32]^{10}$          \\
+         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\begin{table*}[htbp]
+    \centering
+    \caption{Optimization results of the benchmark functions}
+    \label{tab:summaryanalygical}
+    \begin{tabular}{lllllllllll}
+        \toprule
+        Function           & MACE-1             & LCB-1             & EI-1            & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
+         Branin            & 0.3979$\pm$1.31e-5 & 0.3980$\pm$1.1e-4 & 0.414$\pm$0.016 &         &         &         &       &        \\
+         Alpine1           & 2.66$\pm$1.06      & 5.67$\pm$1.77     & 2.46$\pm$1.56   &         &         &         &       &        \\
+         Hartmann6         & -3.26$\pm$0.06     & -3.20$\pm$0.12    & -3.21$\pm$0.15  &         &         &         &       &        \\
+         Ackley2           & 1.72$\pm$1.12      & 1.62$\pm$0.926    & 1.01$\pm$0.98   &         &         &         &       &        \\
+         Rosenbrock2       & 0.03$\pm$0.05      & 0.03$\pm$0.02     & 13.55$\pm$9.527 &         &         &         &       &        \\
+         Ackley10          &                    &                   &                 &         &         &         &       &        \\
+         Rosenbrock10      &                    &                   &                 &         &         &         &       &        \\
+        \bottomrule
+    \end{tabular}
+\end{table*}
 
@@
 \end{figure}
+
+\FloatBarrier

### 2018-01-31 paper/experiments.tex
Paper update

--- 2018-01-31 paper/experiments.tex
@@
 
-We compared the proposed MACE algorithm with several state-of-the-art parallel Bayesian optimization methods, including the BLCB algorithm\footnote{We implemented this algorithm, as the available open source implementation only takes discrete input}, the local penalization method with EI acquisition function\footnote{Code downloade from https://github.com/SheffieldML/GPyOpt}, the qKG and qEI method\footnote{The code for qKG and qEI is available at https://github.com/wujian16/Cornell-MOE}.
-The MACE algorithm and the BLCB algorithm are implemented using c++ language.
+The proposed MACE algorithm was compared with several state-of-the-art parallel
+Bayesian optimization methods, including the BLCB algorithm, the local
+penalization method with EI acquisition function (EI-LP), the qEI and the qKG
+strategy. We implemented the BLCB algorithm while for other compared
+algorithms, we used open source implementations\footnote{We implemented the
+BLCB algorithm as the availble open source implementations only allow discrete
+input; for the EI-LP method, the code is downloaded from
+https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
+downloaded from https://github.com/wujian16/Cornell-MOE}.
 
@@
 
-\begin{enumerate}
-        \item Branin
-        \item Alpine1
-        \item Hart6
-        \item Rosenbrock-2
-        \item Rosenbrock-10
-        \item Ackley-2
-        \item Ackley-10
-\end{enumerate}
+For all functions except the two 10D functions, we set the number of initial
+random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
+size are set to $B = 1 $ and $B = 4$ respectively, the total number of function
+evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D
+rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$
+and the number of iterations is fixed to 175. The experiments were repeated for
+ten times to average the random fluctuations.
+
+The mean convergence plot are shown in Figure~\ref{fig:CovPlotBenchmark}.
+
+\begin{figure*}[htbp]
+    \vskip 0.2in
+    \begin{center}
+        \centerline{\includegraphics[width=\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions\textcolor{red}{data still incomplete}}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+    \vskip -0.2in
+\end{figure*}
+
+As can be seen in Figure~\ref{fig:CovPlotBenchmark}, the MACE strategy is
+competitive in both sequential and batch setting. The qKG method performed not
+good for these benchmark functions, in some functions, it was even outperformed
+by the sequential EI and LCB.
+
+Other algorithms gave acceptable solutions, while the MACE algorithm are
+usually the best or second best algorithms for these benchmark functions.
+
+% \begin{table*}[htbp]
+%     \centering
+%     \caption{Optimization results of the benchmark functions\textcolor{red}{Alert: data still incomplete}}
+%     \label{tab:result_analytical}
+%     \begin{tabular}{lllllllllll}
+%         \toprule
+%         Function           & MACE-1             & LCB-1             & EI-1            & MACE-4             & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
+%          Branin            & 0.3979$\pm$1.31e-5 & 0.3980$\pm$1.1e-4 & 0.414$\pm$0.016 & 0.3979$\pm$6.64e-6 &         &         &       &        \\
+%          Alpine1           & 2.66$\pm$1.06      & 5.67$\pm$1.77     & 2.46$\pm$1.56   &                    &         &         &       &        \\
+%          Hartmann6         & -3.26$\pm$0.06     & -3.20$\pm$0.12    & -3.21$\pm$0.15  &                    &         &         &       &        \\
+%          Ackley2           & 1.72$\pm$1.12      & 1.62$\pm$0.926    & 1.01$\pm$0.98   &                    &         &         &       &        \\
+%          Rosenbrock2       & 0.03$\pm$0.05      & 0.03$\pm$0.02     & 13.55$\pm$9.527 &                    &         &         &       &        \\
+%          Ackley10          &                    &                   &                 &                    &         &         &       &        \\
+%          Rosenbrock10      &                    &                   &                 &                    &         &         &       &        \\
+%         \bottomrule
+%     \end{tabular}
+% \end{table*}
 

### 2018-01-31 paper/experiments.tex
Paper update

@@
 random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
-size are set to $B = 1 $ and $B = 4$ respectively, the total number of function
-evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D
-rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$
-and the number of iterations is fixed to 175. The experiments were repeated for
-ten times to average the random fluctuations.
+size are set to $B = 4$, the total number of function evaluations is $N_{init}
++ B \times iter$. For the 10D ackley and 10D rosenbrock functions, we set the
+number of initial sampling to $N_{init} = 100$ and the number of iterations is
+fixed to 175. The experiments were repeated for ten times to average the random
+fluctuations. The MACE, EI and LCB acquisition functions are also tested with
+$B = 1$.
 
@@
 
-As can be seen in Figure~\ref{fig:CovPlotBenchmark}, the MACE strategy is
-competitive in both sequential and batch setting. The qKG method performed not
-good for these benchmark functions, in some functions, it was even outperformed
-by the sequential EI and LCB.
-
-Other algorithms gave acceptable solutions, while the MACE algorithm are
-usually the best or second best algorithms for these benchmark functions.
+As can be seen in Figure~\ref{fig:CovPlotBenchmark}, for lower dimensional
+functions, the MACE algorithm, BLCB algorithm and the EI-LP algorithm are among
+the best algorithm, the have quite similar convergence rate, while the qEI and
+qKG were outperformed by the above three algorithms. For the 10D ackley and 10D
+rosenbrock functions, the MACE have the fastest convergence rate.
 

### 2018-02-01 paper/experiments.tex
Paper update

--- 2018-01-31 paper/experiments.tex
@@
 
-% TODO: more details about the setup of experiments
-
-The proposed MACE algorithm was compared with several state-of-the-art parallel
-Bayesian optimization methods, including the BLCB algorithm, the local
-penalization method with EI acquisition function (EI-LP), the qEI and the qKG
-strategy. We implemented the BLCB algorithm while for other compared
-algorithms, we used open source implementations\footnote{We implemented the
-BLCB algorithm as the availble open source implementations only allow discrete
-input; for the EI-LP method, the code is downloaded from
+The proposed MACE algorithm was tested using eight benchmark functions and two
+real-world circuits. Four state-of-the-art parallel Bayesian optimization
+methods were compared, including the BLCB algorithm, the local penalization
+method with EI acquisition function, the qEI and qKG methods\footnote{We
+implemented the BLCB algorithm as the availble open source implementations only
+allow discrete input; for the EI-LP method, the code is downloaded from
 https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
@@
 
-We tested the MACE algorithm and other parallel BO method using seven benchmark
-functions, including the branin function, the alpine1 function, the 6D hartmann
-function, the 2D and 10D ackley function and the 2D and 10D Rosenbrock
-function. The dimensions and design space are summarized in
-Table~ref{tab:summaryanalygical}.
+We tested the MACE algorithm and other parallel BO method using eight commonly used benchmark
+functions, as summarized in Table~ref{tab:summaryanalygical}.
 
@@
          Hartmann6          & 6                & $[0,   1]^6$              \\
+         Eggholder          & 2                & $[-512, 512]^2$           \\
          Ackley2            & 2                & $[-32, 32]^2$             \\
@@
 For all functions except the two 10D functions, we set the number of initial
-random sampling to $N_{init} = 20$ and the number of iterations to 45. Batch
-size are set to $B = 1 $ and $B = 4$ respectively, the total number of function
-evaluations is $N_{init} + B \times iter$. For the 10D ackley and 10D
-rosenbrock functions, we set the number of initial sampling to $N_{init} = 100$
-and the number of iterations is fixed to 175. The experiments were repeated for
-ten times to average the random fluctuations.
+random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
+45$. Batch size are set to $B = 4$, the total number of function evaluations is
+$N_{init} + B \times N_{iter}$. For the 10D ackley and 10D rosenbrock functions, we
+$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
+times to average the random fluctuations.
+
+We also compared MACE algorithm with the EI and LCB acquisition functions in
+sequential mode, the sequential EI and LCB are implemented by setting the batch
+size $B = 1$ for EI-LP and BLCB algorithms.
 
@@
     \begin{center}
-        \centerline{\includegraphics[width=\linewidth]{./img/convplot.eps}}
-        \caption{Optimization results of the benchmark functions\textcolor{red}{data still incomplete}}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
         \label{fig:CovPlotBenchmark}
@@
 
-As can be seen in Figure~\ref{fig:CovPlotBenchmark}, the MACE strategy is
-competitive in both sequential and batch setting. The qKG method performed not
-good for these benchmark functions, in some functions, it was even outperformed
-by the sequential EI and LCB.
-
-Other algorithms gave acceptable solutions, while the MACE algorithm are
-usually the best or second best algorithms for these benchmark functions.
+As can be seen in Figure~\ref{fig:CovPlotBenchmark}, when running with batch
+size $B = 4$, the MACE algorithm gives the best performance for six out of the
+eight benchmarks. For the 2D Ackley function, EI-LP is the best algorithm,
+while for the Eggholder function, the MACE, BLCB and EI-LP have quite similar
+performance. Compare the batched MACE and the sequential MACE, the speedup is
+also dramatic.
 
@@
 \end{figure}
-
-\FloatBarrier

### 2018-02-01 paper/conclusion.tex
First draft

\section{Conclusion}

In this paper, a batched Bayesian optimization algorithm is proposed for the
automation of analog circuit design. the parallelization is achieved via
multi-objective ensemble of acquisition function. In each iteration, the
candidate points are sampled from the Pareto front of multiple acquisition
functions. We compared the proposed MACE algorithm using analytical benchmark
functions and real-world circuits, it is shown that the MACE algorithm is
competitive compared with state-of-the-art method listed in the paper.

### 2018-02-01 paper/experiments.tex
First draft

@@
 
-\begin{figure*}[htbp]
-    \vskip 0.2in
-    \begin{center}
-        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
-        \caption{Optimization results of the benchmark functions}
-        \label{fig:CovPlotBenchmark}
-    \end{center}
-    \vskip -0.2in
-\end{figure*}
-
 As can be seen in Figure~\ref{fig:CovPlotBenchmark}, when running with batch
@@
 
-\textcolor{red}{TODO: qKG and qEI}
+%TODO: Introduce the importance of OpAmp and PA
+
+\begin{figure}[htbp]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
+        \caption{Schematic of the operational amplifier}
+        \label{fig:schDAC2014}
+    \end{center}
+\end{figure}
+
+The operational amplifier~\cite{wang2014enabling} shown in Figure~\ref{fig:schDAC2014} is used for
+comparison, the circuit is designed using the 180nm process. It has ten design
+parameters, including the lengths and widths of transistors, the resistance of
+resistors and the capacitance of capacitors. The circuit is simulated using the
+HSPICE circuit simulator.
+
+We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the $FOM$ is constructed as:
+$$
+\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
+$$
+
+For this circuit, we compared the MACE algorithm with the BLCB and EI-LP
+algorithms, the qKG and qEI are not compared as the calculation of qEI and qKG
+acquisition functions become very slow for the ten dimensionl functions.
+
+We run the algorithms in sequential mode and batched mode, for the batched
+mode, batch size is set to $B = 4$. The number initial random sampling is set
+to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
 
@@
 \caption{Optimization results of the operational amplifier}
-\label{resDAC2014}
+\label{fig:resDAC2014}
 \end{center}
@@
 
+The mean convergence plot for the sequential and batched runs are plotted in
+Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
+solution compared to other algorithms, the sequential MACE algorithm found
+better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
+the multi-objective acquisition ensemble is more robust than relying on single
+acquisition function; compared to the sequential MACE algorithm, the MACE
+algorithm with batch size $B = 4$ showed considerable speedup.
+
 \subsection{ClassE Power Amplifier}
 
-\textcolor{red}{TODO: qKG and qEI}
+\begin{figure}[htbp]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/classE.png}}
+        \caption{Schematic of the power amplifier\textcolor{red}{TODO: replace this schematic with eps file} }
+        \label{fig:schPA}
+    \end{center}
+\end{figure}
+
+The power amplifier shown in Figure~\ref{fig:schPA} is used for comparison, the
+circuit is designed using the 180nm process with twelve design parameters, the
+circuit is simulated by HSPICE to get its performances.
+
+For this power amplifier, we aim to maximize the power added effiency (PAE) and the output power (Pout), the $FOM$ is constructed as
+$$
+\mathit{FOM} = -3 * \mathit{PAE} - \mathit{Pout}
+$$
+
+The MACE, BLCB and EI-LP algorithms were tested in both, sequential and batched
+mode, the number of initial sampling is $N_{init} = 100$, the number of
+iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
+number of HSPICE simulations is 500 for each batched run and 200 for each
+sequential run.
 
@@
 \caption{Optimization results of the class-E power amplifier}
-\label{resDAC2014}
+\label{fig:resClassE}
 \end{center}
@@
 \end{figure}
+
+\begin{figure*}[]
+    \begin{center}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+\end{figure*}
+
+The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
+that the MACE outperformed the BLCB and EI-LP in both sequential and batched
+mode. For the batched runs, the MACE convergences fastest among the three
+algorithms, while the sequential MACE has similar performance as the batched
+EI-LP method.

### 2018-02-01 paper/abstract.tex
First draft

@@
     acquisition functions, candidate points are then sampled from the Pareto
-    fronts. The proposed method is compared with several state-of-the-art
+    front. The proposed method is compared with several state-of-the-art
     batched Bayesian optimization algorithms using analytical benchmark

### 2018-02-01 paper/background.tex
Paper update
First draft

@@
 
-\subsection{Formulation}
+\subsection{Problem Formulation}
 
@@
 or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
-design objective. Given the design parameters $\bf{x}$, the FOM value can be
+design objective. Given the design parameters $\bm{x}$, the FOM value can be
 obtained via circuit simulation using softwares like HSPICE or spectre.
@@
 \subsection{Gaussian Process Regression}
-
-\textcolor{red}{ALERT: COPIED FROM MY PAPER SUMBITTED TO DAC}
 

### 2018-02-01 paper/mace.tex
Paper update
First draft

@@
 \textcolor{red}{See how other MOBO paper formulate multi-objective optimization}
-
-\textcolor{red}{ALERT: COPIED FROM MY TCAS-I paper}
 
@@
 
-\subsection{MACE}
+\subsection{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble}
 
@@
 With multi-objective optimization, the disagreement between different
-acquisition function can be used for the parallelization of Bayesian
+acquisition functions can be used for the parallelization of Bayesian
 optimization, as best trade-off between these acquisition functions can be

### 2018-02-03 paper/abstract.tex
Paper update

@@
 \begin{abstract} 
-    The Bayesian optimization has recently shown promising performance for
-    automated analog circuit design. However, the sequential property of
-    Bayesian optimization limits its further application. In this paper, a
-    batched bayesian optimization method is proposed, the parallelization is
-    realized via a multi-objective ensemble of acquisition functions. In each
-    iteration, multiple acquisition functions are selected, the multi-objective
-    optimization is then performed to search for the Pareto front of the
-    acquisition functions, candidate points are then sampled from the Pareto
-    front. The proposed method is compared with several state-of-the-art
-    batched Bayesian optimization algorithms using analytical benchmark
-    functions and real-world analog circuits; the experimental results show
-    that the proposed method is competitive compared to the state-of-the-art
-    methods.
+    The Bayesian optimization algorithm has recently shown promising
+    performance for the automated design analog integrated circuits. However,
+    the sequential property of Bayesian optimization limits its further
+    application. In this paper, a batched bayesian optimization algorithm is
+    proposed, the parallelization is realized via a multi-objective ensemble of
+    acquisition functions. In each iteration, multiple acquisition functions
+    are selected, the multi-objective optimization is performed to search for
+    the Pareto front of the acquisition functions, candidate points are then
+    sampled from the Pareto front. The proposed method is compared with several
+    state-of-the-art batched Bayesian optimization algorithms using analytical
+    benchmark functions and real-world analog circuits; the experimental
+    results show that the proposed method is competitive compared to the
+    state-of-the-art algorithms.
 \end{abstract}

### 2018-02-03 paper/intro.tex
Paper update

@@
 % % TODO: more introduction to the importance of anlog IC sizing, as the reviewers may not have much knowledge of circuit design
-Automated analog circuit design has been a challenging problem for the
-community of electronic design automation (EDA). Unlike digital circuits, where
-the design flow is highly automated, analog circuit design still
-heavily relies on designer's experience. The design parameters of analog circuits like
-transistor widths and lengths need to be manually calculated based on the
-specifications and the designers' understanding of the circuit. However, due to
-the ever-scaling IC manufacture technology and the increasing demands for
-high-performance, low-power circuits, it is getting much more difficult to meet
-the performance and time-to-market requirement with manual circuit design.
+%
+The advancement of modern society is driven by the development of integrated
+circuits (IC), unlike the digital circuits where the design flow is already
+highly automated, the automation of analog circuit design is still a
+challenging problem.
+
+For analog circuits, the design parameters like widths and lengths of
+transistors are manually calculated by designers with their experience and the
+understanding of the design specifications. However, due to the progress of IC
+manufacture technology forecasted by Moore's law, the circuit devices become
+more and more complicated, and the parasitic effect of the circuit can no
+longer be ignored; on the other hand, the demands for high-performance,
+low-power analog circuits is increasing. It is getting much more difficult to
+meet the performance and time-to-market requirement with manual designing.
 Automated analog circuit design has thus attracted more research interests in
@@
 simulation-based approaches. The offline model-based methods try to build
-accurate global models and then apply global optimization algorithms to the
-cheap-to-evaluate models. The model either comes from designers' manual
-derivation or regression models like SVM and ANN. The problem of this approach
-is that the accurate models are usually hard to get, for example,
-in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
-a sparse polynomial model for a circuit with ten design parameters.
-Simulation-based methods, instead, treat the circuits as black-box functions
-that get the FOM value from circuit simulations, global optimization algorithms
-are then directly applied to the black-box functions. For simulation-based
-circuit optimization methods, meta-heuristic
-algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used, although
-these algorithms can explore the whole design space, they have relatively low
-convergence rate and consume many circuit simulations. When the circuit
-simulation takes a long time, both model-based and simulation-based approaches
-can be very time-consuming.
+accurate global models and then optimize the cheap-to-evaluate models. The
+model either comes from designers' manual derivation or regression models like
+SVM and ANN. The problem of this approach is that the accurate models are
+usually hard to get; for example, in~\cite{wang2014enabling}, 100,000 randomly
+simulated points are used to train a sparse polynomial model for an amplifier
+circuit with ten design parameters. Simulation-based methods, instead, treat
+the circuits as black-box functions that get the FOM values from circuit
+simulations, global optimization algorithms are then directly applied to the
+black-box functions.  For simulation-based circuit optimization methods,
+meta-heuristic algorithms~\cite{phelps2000anaconda, liu2009analog} are widely
+used, although these algorithms can explore the whole design space, they have
+relatively low convergence rate. When the circuit simulation takes a long time,
+both model-based and simulation-based approaches can be very time-consuming.
 

### 2018-02-03 paper/intro.tex
Paper update

@@
 meet the performance and time-to-market requirement with manual designing.
-Automated analog circuit design has thus attracted more research interests in
+Automated analog circuit design has thus attracted much research interests in
 the past decade~\cite{rutenbar2007hierarchical}.
@@
 simulated points are used to train a sparse polynomial model for an amplifier
-circuit with ten design parameters. Simulation-based methods, instead, treat
-the circuits as black-box functions that get the FOM values from circuit
-simulations, global optimization algorithms are then directly applied to the
-black-box functions.  For simulation-based circuit optimization methods,
-meta-heuristic algorithms~\cite{phelps2000anaconda, liu2009analog} are widely
-used, although these algorithms can explore the whole design space, they have
-relatively low convergence rate. When the circuit simulation takes a long time,
-both model-based and simulation-based approaches can be very time-consuming.
+circuit with ten design parameters.
+
+Simulation-based methods, instead, treat the circuits as black-box functions
+that get the FOM values from circuit simulations, global optimization
+algorithms are then directly applied to the black-box functions. For
+simulation-based circuit optimization methods, meta-heuristic
+algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used, although
+these algorithms can explore the whole design space, they have relatively low
+convergence rate. When the circuit simulation takes a long time, both
+model-based and simulation-based approaches can be very time-consuming.
 
@@
 assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
-differential evolution algorithm, Recently, the
+differential evolution algorithm; recently, the
 Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
@@
 % TODO: See how other papers review existing batched BO methods
-Batched Bayesian optimization has been a \textcolor{red}{hot} topic in the BO
-literature. Related works include the \emph{simulation matching}
-method~\cite{azimi2010batch}, the \emph{BUCB} (BLCB for minimization)
-method~\cite{desautels2014parallelizing}, the \emph{GP-UCB-PE}
-method~\cite{contal2013parallel}, the \emph{local penalization}
-method~\cite{gonzalez2016batch}, the \emph{parallel predictive entropy
-search}~\cite{shah2015parallel} and the \emph{qKG}
-method~\cite{wu2016parallel}.
+Batched Bayesian optimization has been a hot topic in the BO literature.
+Related works include the simulation matching (SM)
+method~\cite{azimi2010batch}, the BUCB (BLCB for minimization)
+method~\cite{desautels2014parallelizing}, the GP-UCB-PE
+method~\cite{contal2013parallel}, the local penalization (LP)
+method~\cite{gonzalez2016batch}, the parallel predictive entropy (PPES)
+search~\cite{shah2015parallel} and the qKG method~\cite{wu2016parallel}.
+
+\textcolor{red}{TODO}{Discuss more details about these algorithms}
 
@@
 % TODO: Beiefly introduce my algorithm
-All the algorithms mentioned above choose to use one acquisition function, and
-except for the simulation matching method and local penalization method which
-can select arbitrary acquisition function, other parallelization methods rely
-on specific acquisition function, the UCB acquisition function must be used for
-BUCB and GP-UCB-PE, and the knowledge gradient method must be used for the qKG
-algorithm. As has been stated in~\cite{hoffman2011portfolio}, no one
-acquisition function can always outperform other acquisition functions, so
-relying on one acquisition function may resulting in poor performance.
+All the algorithms mentioned above choose to use single acquisition function,
+and except for the simulation matching method and local penalization method
+which can select arbitrary acquisition function, other parallelization methods
+rely on a specific acquisition function. The UCB acquisition function must be
+used for BUCB and GP-UCB-PE, and the knowledge gradient method must be used for
+the qKG algorithm. As is stated in~\cite{hoffman2011portfolio}, no single
+acquisition function can always outperform other acquisition functions, relying
+on one acquisition function may result in poor performance.
 
-In contrast to existing batched bayesian optimization methods, we propose a
-different perspective to the parallelization of Bayesian optimization. In this
-paper, we propose to parallelize the Bayesian optimization algorithm via a
-multi-objective ensemble of acquisition functions. Firstly, in each iteration,
-after the GP model is updated, multiple acquisition functions are selected, we
-then perform multi-objective optimization to find the \emph{Pareto front} (PF)
-of the acquisition functions. The PF represents the best trade-off between
-these acquisition functions. When used in sequential mode, the proposed
-multi-objective acquisition ensemble (MACE) strategy can be seen as a portfolio
-strategy, when batched evaluation is possible, we can sample multiple points on
-the PF as there are usually much more points on the PF than the batch size.
+In this paper, we propose to parallelize the Bayesian optimization algorithm
+via the multi-objective acquisition ensemble (MACE). Firstly, in each
+iteration, after the GP model is updated, multiple acquisition functions are
+selected, we then perform multi-objective optimization to find the \emph{Pareto
+front} (PF) of the acquisition functions. The PF represents the best trade-off
+between these acquisition functions. When batched evaluations are possible, we
+can sample multiple points on the optimized PF to accelerate the optimization.
 
 The MACE algorithm is tested using several analytical benchmark functions and
-two real-world analog circuits, including an operational amplifier with
-\textcolor{red}{14} design parameters and a class-E power amplifier with
-\textcolor{red}{ten} design parameters. The BLCB method, local penalization
-method with expected improvement acquisition function (EI-LP), the qEI methods
-and qEI methods are compared with MACE. The proposed MACE method achieved
-competitive performance when compared with the listed state-of-the-art
-algorithms.
+two real-world analog circuits, including an operational amplifier with ten
+design parameters and a class-E power amplifier with twelve design parameters.
+The BLCB method, local penalization method with expected improvement
+acquisition function (EI-LP), qEI methods and qKG methods are compared with
+MACE. The proposed MACE method achieved competitive performance when compared
+to the listed state-of-the-art algorithms.

### 2018-02-05 paper/background.tex
Paper update

@@
 
-We handle the scenarios where topology of the analog circuit is fixed, this is
-practical as thare are usually a lot of classical topologies for given design
-task. Once the circuit topology is fixed, the designer has to choose the
+We handle the scenarios where the topology of the analog circuit is fixed, this
+is practical as there are usually a lot of classical topologies for given
+design task. Once the circuit topology is fixed, the designer has to choose the
 appropriate design parameters according to the specifications and the circuit
-device model. What we want to do is to automatically search for the optimal
+device model. What we want to do is automatically searching for the optimal
 design parameters, the problem can then be formulated as a bound-constrained
@@
 
-where $\bm{x} \in \textrm{D} \subset \textrm{R}^d$ is the design variables
-and $f_i(\bm{x})$ represents the $i$-th cared circuit performance like gain
-or phase margin of an amplifier. and the $\mathrm{FOM}(\bm{x})$ is the
-design objective. Given the design parameters $\bm{x}$, the FOM value can be
-obtained via circuit simulation using softwares like HSPICE or spectre.
+where $\bm{x} \in \textrm{D}$ is the vector of design variables,
+$\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
+specifications. Given the design parameters $\bm{x}$, the FOM value can be
+obtained by commercial circuit simulators like HSPICE or spectre.
 
-% TODO: Explain the noise
+\textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}
+
+\begin{figure}[]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
+        \caption{Phase margin of an amplifier as function of the width of a transistor}
+        \label{fig:PMOpAmp}
+    \end{center}
+\end{figure}
 
 \subsection{Gaussian Process Regression}
+
+\textcolor{red}{
+    TODO:
+    \begin{enumerate}
+            \item Noise
+            \item MLE learning
+    \end{enumerate}
+}
 
@@
 function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
-paper, we use squared-exponential ARD kernel, and a constant mean function
+work, we use squared-exponential ARD kernel, and a constant mean function
 $m(\bm{x}) = \mu_0$ for all our experiments.
@@
 Bayesian optimization~\cite{shahriari2016taking} was proposed for the
-optimization of expensive black-box functions. It consists of two essential
-ingredients, i.e., the probabilistic surrogate models and an acquisition
-function. The probabilistic surrogate models provide the prediction with
-uncertainties. They are refined incrementally with newly observed data.
-Acquisition function is used to explore the state space based on the surrogate
-model optimally. The procedure of Bayesian optimization is described in
-Algorithm~\ref{alg:BayesianOptAlgo}.
+optimization of expensive black-box functions, it has two essential
+ingredients, i.e., the probabilistic surrogate models and acquisition
+functions. The probabilistic surrogate models provide predictions with
+uncertainties. The acquisition functions make use of the predictive
+distribution to explore the state space, the procedure of Bayesian optimization
+is summarized in Algorithm~\ref{alg:BayesianOptAlgo}.
 
+\textcolor{red}{TODO: Add Input, Output parameters}
 \begin{algorithm}
@@
 \begin{equation}
-    \label{eq:LCB}
+    \label{eq:LCBKappa}
     \begin{array}{lll}
@@
 \end{equation}
-Where $t$ is the number of current iteration.
-$\nu$ and $\delta$ are two user defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.
+where $t$ is the number of current iteration.
+$\nu$ and $\delta$ are two user-defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.
 
@@
 
-There are also other acquisition function, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}.
-A portforlio of several acquisition function is also possible~\cite{hoffman2011portfolio}.
+There are also other acquisition functions, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}.
+A portfolio of several acquisition functions is also possible~\cite{hoffman2011portfolio}.

### 2018-02-05 paper/experiments.tex
Paper update

@@
+\begin{figure*}[htbp]
+    \begin{center}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+\end{figure*}
+
 \section{Experimental Results}
@@
 We tested the MACE algorithm and other parallel BO method using eight commonly used benchmark
-functions, as summarized in Table~ref{tab:summaryanalygical}.
+functions, as summarized in Table~\ref{tab:summaryanalygical}.
 
@@
 random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
-45$. Batch size are set to $B = 4$, the total number of function evaluations is
-$N_{init} + B \times N_{iter}$. For the 10D ackley and 10D rosenbrock functions, we
+45$. Batch size is set to $B = 4$, the total number of function evaluations is
+$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we
 $N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
@@
 
-We also compared MACE algorithm with the EI and LCB acquisition functions in
-sequential mode, the sequential EI and LCB are implemented by setting the batch
-size $B = 1$ for EI-LP and BLCB algorithms.
+We also ran the MACE algorithm in sequential mode and compared the EI and LCB
+acquisition functions, the sequential EI and LCB based Bayesian optimization
+are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
+respectively.
 
-The mean convergence plot are shown in Figure~\ref{fig:CovPlotBenchmark}.
-
-As can be seen in Figure~\ref{fig:CovPlotBenchmark}, when running with batch
-size $B = 4$, the MACE algorithm gives the best performance for six out of the
-eight benchmarks. For the 2D Ackley function, EI-LP is the best algorithm,
-while for the Eggholder function, the MACE, BLCB and EI-LP have quite similar
+The mean convergence plot is shown in Figure~\ref{fig:CovPlotBenchmark}. The
+statistics of the final optimization results are listed in
+Table~\ref{tab:result_analytical}. As can be seen, when running with batch size
+$B = 4$, the MACE algorithm gives the best performance for six out of the eight
+benchmarks.  For the 2D Ackley function, EI-LP is the best algorithm, while for
+the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
 performance.  Compare the batched MACE and the sequential MACE, the speedup is
@@
 
-% \begin{table*}[htbp]
-%     \centering
-%     \caption{Optimization results of the benchmark functions\textcolor{red}{Alert: data still incomplete}}
-%     \label{tab:result_analytical}
-%     \begin{tabular}{lllllllllll}
-%         \toprule
-%         Function           & MACE-1             & LCB-1             & EI-1            & MACE-4             & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
-%          Branin            & 0.3979$\pm$1.31e-5 & 0.3980$\pm$1.1e-4 & 0.414$\pm$0.016 & 0.3979$\pm$6.64e-6 &         &         &       &        \\
-%          Alpine1           & 2.66$\pm$1.06      & 5.67$\pm$1.77     & 2.46$\pm$1.56   &                    &         &         &       &        \\
-%          Hartmann6         & -3.26$\pm$0.06     & -3.20$\pm$0.12    & -3.21$\pm$0.15  &                    &         &         &       &        \\
-%          Ackley2           & 1.72$\pm$1.12      & 1.62$\pm$0.926    & 1.01$\pm$0.98   &                    &         &         &       &        \\
-%          Rosenbrock2       & 0.03$\pm$0.05      & 0.03$\pm$0.02     & 13.55$\pm$9.527 &                    &         &         &       &        \\
-%          Ackley10          &                    &                   &                 &                    &         &         &       &        \\
-%          Rosenbrock10      &                    &                   &                 &                    &         &         &       &        \\
-%         \bottomrule
-%     \end{tabular}
-% \end{table*}
+\begin{table*}[tp]
+    \centering
+    \caption{Optimization results of the benchmark functions}
+    \label{tab:result_analytical}
+    \begin{tabular}{lllllllllll}
+        \toprule
+        Function           & MACE-1 & LCB-1  & EI-1  & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
+         Branin            &        &        &       &         &         &         &       &        \\
+         Alpine1           &        &        &       &         &         &         &       &        \\
+         Hartmann6         &        &        &       &         &         &         &       &        \\
+         Eggholder         &        &        &       &         &         &         &       &        \\
+         Ackley2           &        &        &       &         &         &         &       &        \\
+         Rosenbrock2       &        &        &       &         &         &         &       &        \\
+         Ackley10          &        &        &       &         &         &         &       &        \\
+         Rosenbrock10      &        &        &       &         &         &         &       &        \\
+        \bottomrule
+    \end{tabular}
+\end{table*}
 
@@
 
-\begin{figure}[htbp]
-    \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
-        \caption{Schematic of the operational amplifier}
-        \label{fig:schDAC2014}
-    \end{center}
-\end{figure}
+\textcolor{red}{TODO: if possible, run qKG and qEI for this circuit}
 
-The operational amplifier~\cite{wang2014enabling} shown in Figure~\ref{fig:schDAC2014} is used for
-comparison, the circuit is designed using the 180nm process. It has ten design
-parameters, including the lengths and widths of transistors, the resistance of
-resistors and the capacitance of capacitors. The circuit is simulated using the
-HSPICE circuit simulator.
+The operational amplifier~\cite{wang2014enabling} shown in
+Figure~\ref{fig:schDAC2014} is used for comparison, the circuit is designed
+using the 180nm process. It has ten design parameters, including the lengths
+and widths of transistors, the resistance of resistors and the capacitance of
+capacitors. The circuit is simulated using the HSPICE circuit simulator.
 
@@
 algorithms, the qKG and qEI are not compared as the calculation of qEI and qKG
-acquisition functions become very slow for the ten dimensionl functions.
+acquisition functions become very slow for the ten-dimensional functions.
 
-We run the algorithms in sequential mode and batched mode, for the batched
-mode, batch size is set to $B = 4$. The number initial random sampling is set
-to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
+\begin{figure}[h]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
+        \caption{Schematic of the operational amplifier}
+        \label{fig:schDAC2014}
+    \end{center}
+\end{figure}
 
-\begin{figure}[htbp]
+\begin{figure}[]
 \vskip 0.2in
@@
 \end{figure}
+
+We run the algorithms in sequential mode and batched mode, for the batched
+mode, batch size is set to $B = 4$. The number initial random sampling is set
+to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
+
+\begin{table}[]
+    \centering
+    \caption{Optimization results of the operational amplifier}
+    \label{tab:result_opamp}
+    \begin{tabular}{llll}
+        \toprule
+        Algorithm & Results     \\ \midrule
+        MACE-1    & 0.0$\pm$0.0 \\
+        LCB-1     & 0.0$\pm$0.0 \\
+        EI-1      & 0.0$\pm$0.0 \\
+        MACE-4    & 0.0$\pm$0.0 \\
+        BLCB-1    & 0.0$\pm$0.0 \\
+        EI-LP-4   & 0.0$\pm$0.0 \\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 
-For this power amplifier, we aim to maximize the power added effiency (PAE) and the output power (Pout), the $FOM$ is constructed as
+For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the $FOM$ is constructed as
 $$
-\mathit{FOM} = -3 * \mathit{PAE} - \mathit{Pout}
+\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
 $$
 
-The MACE, BLCB and EI-LP algorithms were tested in both, sequential and batched
-mode, the number of initial sampling is $N_{init} = 100$, the number of
+\begin{table}[htbp]
+    \centering
+    \caption{Optimization results of the power amplifier}
+    \label{tab:result_PA}
+    \begin{tabular}{llll}
+        \toprule
+        Algorithm & Results     \\ \midrule
+        MACE-1    & 0.0$\pm$0.0 \\
+        LCB-1     & 0.0$\pm$0.0 \\
+        EI-1      & 0.0$\pm$0.0 \\
+        MACE-4    & 0.0$\pm$0.0 \\
+        BLCB-1    & 0.0$\pm$0.0 \\
+        EI-LP-4   & 0.0$\pm$0.0 \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batched
+mode. The number of initial sampling is $N_{init} = 100$, the number of
 iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
@@
 
-\begin{figure*}[]
-    \begin{center}
-        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
-        \caption{Optimization results of the benchmark functions}
-        \label{fig:CovPlotBenchmark}
-    \end{center}
-\end{figure*}
-
 The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see

### 2018-02-05 paper/mace.tex
Paper update

@@
 
-Multi-objective optimization~\cite{MO_overview} can be formulated as:
+Unlike single-objective optimization, multi-objective optimization problems
+simultaneously optimize multiple objectives~\cite{MO_overview}, the
+multi-objective optimization problem is formulated as
 \begin{equation}
@@
 \end{equation}
-
-For multi-objective optimization, there are more than one objecive to optimize, and usually there does not exist a single solution that simultaneously optimize all these objectives.
-A design $\bm{x}_1$ is said to be \emph{dominate} by $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
-A design is \emph{Pareto-optimal} if it is not dominated by any other point and dominate at least one point.
-The whole set of the non-dominated points in the design space is called the \emph{Pareto set}, and the set of non-dominated points in the objective space is called the \emph{Pareto front}.
+When we have multiple objectives to optimizes, the objectives can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to appropriate the \emph{Pareto front} of the objectives.
+A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
+A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominate at least one point.
+The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}.
 It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
 
-There exist many mature multi-objective optimization algorithms, like the non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the multi-objective evolutionary algorithm based on decomposition (MOEA/D)~\cite{moead}.
-In this paper, the multi-objective optimization based on differential evolution (DEMO)~\cite{demo} is used to solve multi-objective optimization problems.
+There exist many mature multi-objective optimization algorithms, like the
+non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the
+multi-objective evolutionary algorithm based on decomposition
+(MOEA/D)~\cite{moead}. In this paper, the multi-objective optimization based on
+differential evolution (DEMO)~\cite{demo} is used to solve multi-objective
+optimization problems.
 
@@
 We propose a novel heuristic for the parallelization of Bayesian optimization.
-The parallelization is realized via multi-objective ensemble of multiple
-acquisition functions. When we have multiple acquisition functions built from
-the same GP model, they may not disagree with each other about which point is
-most promising. For example, the value of LCB function always decreases as the
-$\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$
-increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and
-increase when $\mu(\bm{x}) > \tau$.
+The parallelization is realized via the multi-objective ensemble of multiple
+acquisition functions. As each acquisition function represents a unique
+interpretation to the optimization problem, different acquisition functions may
+not agree with each other about where to sample the next point. For example,
+the value of LCB function always decreases as the $\sigma(\bm{x})$ increases,
+however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI
+would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) >
+\tau$. For a noise-free problem, the EI values at already sampled points are
+always zero, so that any unsampled point would have a better EI value than the
+sampled points, while this property does not hold for the LCB function.
 
-% TODO: discuss the difference of acquisition functions: LCB: do not avoid repeated sampling, EI: always positive
+\textcolor{red}{TODO: Illustrate PF}
+\begin{figure}[ht]
+    \vskip 0.2in
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/pf.jpg}}
+        \caption{Illustration of Pareto front}
+        \label{fig:PF_example}
+    \end{center}
+    \vskip -0.2in
+\end{figure}
 
-With multi-objective optimization, the disagreement between different
-acquisition functions can be used for the parallelization of Bayesian
-optimization, as best trade-off between these acquisition functions can be
-captured by the Pareto front.
+With multi-objective optimization, the best trade-off between acquisition functions can be captured by the Pareto front of these acquisition functions.
+We can then sample on the Pareto front to obtain multiple candidate points for the objective function evaluations.
 
@@
 \end{equation}
-Then the DEMO multi-objective optimization algorithm is applied to solve \eqref{eq:MO_LCB_EI_PI}.
+Then the DEMO multi-objective optimization algorithm is applied to solve the multi-objective problem in \eqref{eq:MO_LCB_EI_PI}.
 Once the Pareto front of LCB, EI and PI is obtained, the candidate evalution points are then randomly sampled from the Pareto front.
@@
 
+\textcolor{red}{TODO: Input, Output parameters, see how other papers format the algorithm description}
 \begin{algorithm}
@@
 \end{algorithm}
+
+\textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}

### 2018-02-06 paper/abstract.tex
Batched => Batch

@@
     the sequential property of Bayesian optimization limits its further
-    application. In this paper, a batched bayesian optimization algorithm is
+    application. In this paper, a batch bayesian optimization algorithm is
     proposed, the parallelization is realized via a multi-objective ensemble of
@@
     sampled from the Pareto front. The proposed method is compared with several
-    state-of-the-art batched Bayesian optimization algorithms using analytical
+    state-of-the-art batch Bayesian optimization algorithms using analytical
     benchmark functions and real-world analog circuits; the experimental

### 2018-02-06 paper/conclusion.tex
Paper update
Batched => Batch

@@
 
-In this paper, a batched Bayesian optimization algorithm is proposed for the
-automation of analog circuit design. the parallelization is achieved via
-multi-objective ensemble of acquisition function. In each iteration, the
+In this paper, a batch Bayesian optimization algorithm is proposed for the
+automation of analog circuit design. The parallelization is achieved via
+the multi-objective ensemble of acquisition function. In each iteration, the
 candidate points are sampled from the Pareto front of multiple acquisition

### 2018-02-06 paper/experiments.tex
Batched => Batch

@@
 the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
-performance.  Compare the batched MACE and the sequential MACE, the speedup is
+performance.  Compare the batch MACE and the sequential MACE, the speedup is
 also dramatic.
@@
 
-We run the algorithms in sequential mode and batched mode, for the batched
+We run the algorithms in sequential mode and batch mode, for the batch
 mode, batch size is set to $B = 4$. The number initial random sampling is set
@@
 
-The mean convergence plot for the sequential and batched runs are plotted in
+The mean convergence plot for the sequential and batch runs are plotted in
 Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
@@
 
-The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batched
+The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
 mode. The number of initial sampling is $N_{init} = 100$, the number of
 iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
-number of HSPICE simulations is 500 for each batched run and 200 for each
+number of HSPICE simulations is 500 for each batch run and 200 for each
 sequential run.
@@
 The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
-that the MACE outperformed the BLCB and EI-LP in both sequential and batched
-mode. For the batched runs, the MACE convergences fastest among the three
-algorithms, while the sequential MACE has similar performance as the batched
+that the MACE outperformed the BLCB and EI-LP in both sequential and batch
+mode. For the batch runs, the MACE convergences fastest among the three
+algorithms, while the sequential MACE has similar performance as the batch
 EI-LP method.

### 2018-02-06 paper/intro.tex
Batched => Batch

@@
 % TODO: Review current methods
-% TODO: See how other papers review existing batched BO methods
-Batched Bayesian optimization has been a hot topic in the BO literature.
+% TODO: See how other papers review existing batch BO methods
+Batch Bayesian optimization has been a hot topic in the BO literature.
 Related works include the simulation matching (SM)
@@
 front} (PF) of the acquisition functions. The PF represents the best trade-off
-between these acquisition functions. When batched evaluations are possible, we
+between these acquisition functions. When batch evaluations are possible, we
 can sample multiple points on the optimized PF to accelerate the optimization.

### 2018-02-06 paper/abstract.tex
"compared to" => "compared with"

@@
     benchmark functions and real-world analog circuits; the experimental
-    results show that the proposed method is competitive compared to the
+    results show that the proposed method is competitive compared with the
     state-of-the-art algorithms.

### 2018-02-06 paper/experiments.tex
"compared to" => "compared with"

@@
 
-We also ran the MACE algorithm in sequential mode and compared the EI and LCB
+We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
 acquisition functions, the sequential EI and LCB based Bayesian optimization
@@
 Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
-solution compared to other algorithms, the sequential MACE algorithm found
+solution compared with other algorithms, the sequential MACE algorithm found
 better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
 the multi-objective acquisition ensemble is more robust than relying on single
-acquisition function; compared to the sequential MACE algorithm, the MACE
+acquisition function; compared with the sequential MACE algorithm, the MACE
 algorithm with batch size $B = 4$ showed considerable speedup.

### 2018-02-06 paper/intro.tex
"compared to" => "compared with"
Paper update

@@
 low-power analog circuits is increasing. It is getting much more difficult to
-meet the performance and time-to-market requirement with manual designing.
-Automated analog circuit design has thus attracted much research interests in
+meet the performance and time-to-market requirement with manual circuit analysis.
+Automated analog circuit design has thus attracted much research interest in
 the past decade~\cite{rutenbar2007hierarchical}.
@@
 The analog circuit design automation problems can be formulated as optimization
-problems, the aim is to find the optimal vector of design parameters that give
-the best figure of merit (FOM). Prior works about analog circuit optimization
-include offline model-based approaches
+problems, the aim is to find the optimal vector of design parameters that gives
+the best circuti performance, which is represented by a figure of merit (FOM)
+function. Prior works about analog circuit optimization include offline
+model-based approaches
 ~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
@@
 accurate global models and then optimize the cheap-to-evaluate models. The
-model either comes from designers' manual derivation or regression models like
-SVM and ANN. The problem of this approach is that the accurate models are
-usually hard to get; for example, in~\cite{wang2014enabling}, 100,000 randomly
-simulated points are used to train a sparse polynomial model for an amplifier
-circuit with ten design parameters.
+problem of this approach is that the accurate models are usually hard to get;
+for example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
+used to train a sparse polynomial model for an amplifier circuit with ten
+design parameters.
 
@@
 The Bayesian optimization algorithm is a well-studied algorithm and has
-demonstrated to be a promising algorithm for automated analog circuit design.
-However, the standard Bayesian optimization algorithm is sequential; it chooses
-the next evaluation point by optimizing the specified acquisition function,
-which makes the parallelization of Bayesian optimization non-trivial. The
-sequential property of BO limits its further application in multi-core computer
-systems.
+demonstrated to be promising for the automated design of analog circuits.
+However, the standard Bayesian optimization algorithm is sequential, it chooses
+only one point at each iteration by optimizing the acquisition function. It is
+often desirable to select a batch of points at each iteration, the sequential
+property of BO limits its further application in multi-core computer systems.
 
-% TODO: Review current methods
-% TODO: See how other papers review existing batch BO methods
-Batch Bayesian optimization has been a hot topic in the BO literature.
-Related works include the simulation matching (SM)
-method~\cite{azimi2010batch}, the BUCB (BLCB for minimization)
-method~\cite{desautels2014parallelizing}, the GP-UCB-PE
-method~\cite{contal2013parallel}, the local penalization (LP)
-method~\cite{gonzalez2016batch}, the parallel predictive entropy (PPES)
-search~\cite{shah2015parallel} and the qKG method~\cite{wu2016parallel}.
-
-\textcolor{red}{TODO}{Discuss more details about these algorithms}
-
-% BUCB, UCB-PE: regret bound
-% PPES: entropy search
-% qKG, qEI: optimal decision if multiple points are selected
-% LP: very good heuristic
+The Bayesian optimization algorithm has been extended to enable batch
+selection. Some prior works, like the qEI\cite{qEI}, qKG\cite{wu2016parallel}
+and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
+approaches, consider to search for the optimal batch selection for a given
+acquisition function. These methods usually involve some approximations or
+Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
+works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
+batch-UCB(BUCB, BLCB for minimization
+problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
+exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
+penalization~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
+strategies that select individual points until the batch is filled.
 
@@
 MACE. The proposed MACE method achieved competitive performance when compared
-to the listed state-of-the-art algorithms.
+with the listed state-of-the-art algorithms.

### 2018-02-06 paper/intro.tex
Paper update

@@
 exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
-penalization~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
+penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
 strategies that select individual points until the batch is filled.
@@
 All the algorithms mentioned above choose to use single acquisition function,
-and except for the simulation matching method and local penalization method
-which can select arbitrary acquisition function, other parallelization methods
-rely on a specific acquisition function. The UCB acquisition function must be
-used for BUCB and GP-UCB-PE, and the knowledge gradient method must be used for
-the qKG algorithm. As is stated in~\cite{hoffman2011portfolio}, no single
-acquisition function can always outperform other acquisition functions, relying
-on one acquisition function may result in poor performance.
+and except for the SM method and LP method which can use arbitrary acquisition
+function, other parallelization methods rely on a specific acquisition
+function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
+the knowledge gradient method must be used for the qKG algorithm. As is stated
+in~\cite{hoffman2011portfolio}, no single acquisition function can always
+outperform other acquisition functions, relying on one acquisition function may
+result in poor performance.
 
 In this paper, we propose to parallelize the Bayesian optimization algorithm
-via the multi-objective acquisition ensemble (MACE). Firstly, in each
-iteration, after the GP model is updated, multiple acquisition functions are
-selected, we then perform multi-objective optimization to find the \emph{Pareto
-front} (PF) of the acquisition functions. The PF represents the best trade-off
-between these acquisition functions. When batch evaluations are possible, we
-can sample multiple points on the optimized PF to accelerate the optimization.
+via the multi-objective acquisition ensemble (MACE). The proposed MACE method
+exploits the disagreement between different acquisition functions to enable
+parallel selection. At each iteration, after the GP model is updated, multiple
+acquisition functions are selected, we then perform multi-objective
+optimization to find the \emph{Pareto front} (PF) of the acquisition functions.
+The PF represents the best trade-off between these acquisition functions. When
+batch evaluations are possible, we can sample multiple points on the optimized
+PF to accelerate the optimization.
 
@@
 MACE. The proposed MACE method achieved competitive performance when compared
-with the listed state-of-the-art algorithms.
+with the state-of-the-art algorithms listed in the paper.

### 2018-02-06 paper/background.tex
Paper update
Add figure

@@
 
-\textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}
+% \textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}
 
-\begin{figure}[]
-    \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
-        \caption{Phase margin of an amplifier as function of the width of a transistor}
-        \label{fig:PMOpAmp}
-    \end{center}
-\end{figure}
+% \begin{figure}[]
+%     \begin{center}
+%         \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
+%         \caption{Phase margin of an amplifier as function of the width of a transistor}
+%         \label{fig:PMOpAmp}
+%     \end{center}
+% \end{figure}
 
@@
 
+\textcolor{red}{$\sigma_f$ ???}
+
 \subsection{Bayesian Optimization}
@@
 \end{equation}
-Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP. $\kappa$ is a parameter that balances the exploitation and exploration.
+Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.
 
@@
         \kappa &=& \sqrt{\nu \tau_t} \\
-        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta)
+        \tau_t &=& 2 \log(t^{d/2+2} \pi^2 / 3 \delta),
     \end{array}
 \end{equation}
-where $t$ is the number of current iteration.
-$\nu$ and $\delta$ are two user-defined parameters, we fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.
+where $t$ is the number of current iteration, $\nu$ and $\delta$ are two user-defined parameters.
+We fix $\nu = 0.5$ and $\delta = 0.05$ in this paper for the proposed MACE algorithm and our implementation of the BLCB algorithm.
 
@@
 The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution.
+We fix $\xi = 1e-3$ in our implementation of the MACE algorithm.
 
@@
 
-There are also other acquisition functions, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}.
+There are also other acquisition functions, like the knowledge gradient~\cite{scott2011correlated} function, predictive entropy search~\cite{hernandez2014predictive}, and the max-value entropy search\cite{wang2017max}.
 A portfolio of several acquisition functions is also possible~\cite{hoffman2011portfolio}.

### 2018-02-06 paper/mace.tex
Add figure

@@
 \section{Proposed Batched Bayesian Optimization Algorithm}
+
+\begin{figure*}[tp!]
+    \centering
+    \subfigure[True phase margin curve, GP predictions, and Pareto set]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pm_gp_ps.eps}}
+    ~
+    \subfigure[The LCB, EI, and PI functions and the Pareto front]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pf.eps}}
+    \caption{Illustration of the multi-objective optimization of acquisition functions}
+    \label{fig:PF_example}
+        % \begin{subfigure}[]{width=0.5\textwidth}
+        %     \includegraphics[width=0.5\textwidth]{./img/pf.eps}
+        %     \caption{LCB, EI, PI and PF}
+        %     \label{fig:PF_example_1}
+        % \end{subfigure}
+        % \begin{subfigure}[]{0.5\textwidth}
+        %     \includegraphics[width=0.5\textwidth]{./img/pm_gp_ps.eps}
+        %     \caption{True curve, GP predictions and PS}
+        %     \label{fig:PF_example_1}
+        % \end{subfigure}
+\end{figure*}
 
@@
 
-Unlike single-objective optimization, multi-objective optimization problems
-simultaneously optimize multiple objectives~\cite{MO_overview}, the
-multi-objective optimization problem is formulated as
+Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}, the multi-objective optimization problem is formulated as
 \begin{equation}
@@
     \begin{aligned}
-        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x})
+        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
     \end{aligned}
 \end{equation}
-When we have multiple objectives to optimizes, the objectives can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to appropriate the \emph{Pareto front} of the objectives.
+The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives.
 A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
@@
 
-There exist many mature multi-objective optimization algorithms, like the
-non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the
-multi-objective evolutionary algorithm based on decomposition
-(MOEA/D)~\cite{moead}. In this paper, the multi-objective optimization based on
-differential evolution (DEMO)~\cite{demo} is used to solve multi-objective
-optimization problems.
-
-% When we have more than one objective to optimize, the problem is formulated as:
+There exist many mature multi-objective optimization algorithms, like the non-dominated sorting based genetic algorithm (NSGA-II)~\cite{nsgaii}, and the multi-objective evolutionary algorithm based on decomposition (MOEA/D)~\cite{moead}.
+In this paper, the multi-objective optimization based on differential evolution (DEMO)~\cite{demo} is used to solve multi-objective optimization problems, but other multi-objective optimization algorithms can also be applied.
 
@@
 
-We propose a novel heuristic for the parallelization of Bayesian optimization.
-The parallelization is realized via the multi-objective ensemble of multiple
-acquisition functions. As each acquisition function represents a unique
-interpretation to the optimization problem, different acquisition functions may
-not agree with each other about where to sample the next point. For example,
-the value of LCB function always decreases as the $\sigma(\bm{x})$ increases,
-however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI
-would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) >
-\tau$. For a noise-free problem, the EI values at already sampled points are
-always zero, so that any unsampled point would have a better EI value than the
-sampled points, while this property does not hold for the LCB function.
-
-\textcolor{red}{TODO: Illustrate PF}
-\begin{figure}[ht]
-    \vskip 0.2in
-    \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/pf.jpg}}
-        \caption{Illustration of Pareto front}
-        \label{fig:PF_example}
-    \end{center}
-    \vskip -0.2in
-\end{figure}
+Each acquisition function represents a unique selection strategy, different acquisition functions may not agree with each other about where to sample the next point.
+For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$.
+For a noise-free problem, the EI values at already sampled points would always be lower than any unsampled location, while this property does not hold for the LCB function.
 

### 2018-02-06 paper/main.tex
Paper update
First draft
Batched => Batch

@@
 \usepackage[plain]{fancyref}
-\usepackage{bookmark}
 \usepackage{bm}
 \usepackage{todonotes}
+\usepackage{placeins}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\icmltitlerunning{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
+\icmltitlerunning{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
 
@@
 \twocolumn[
-\icmltitle{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
+\icmltitle{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
 
@@
 \input{experiments}
+\input{conclusion}
+
+\FloatBarrier
 

### 2018-02-07 paper/mace.tex
Batched => Batch
Paper update

@@
-\section{Proposed Batched Bayesian Optimization Algorithm}
+\section{Proposed Batch Bayesian Optimization Algorithm}
 
@@
     ~
-    \subfigure[The LCB, EI, and PI functions and the Pareto front]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pf.eps}}
+    \subfigure[The LCB, EI, and PI functions and the Pareto front]{\label{fig:PF_example_2}\includegraphics[width=0.49\textwidth]{./img/pf.eps}}
     \caption{Illustration of the multi-objective optimization of acquisition functions}
@@
 
-\subsection{Batched Bayesian Optimization via Multi-objective Acquisition Ensemble}
+\subsection{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble}
 
@@
 % TODO: plot contour of Branin/Ei/LCB/PI, plot the PS and the PF
+We illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.
+The optimization objective is to maximize the phase margin (PF) of the amplifier, so the FOM is defined as $\mathrm{FOM}(\bm{x}) = - \mathrm{PF}(\bm{x})$.
+The width of one of its transistor is the design variable, we sweep the width of the transistor and perform HSPICE simulations to get the FOM values.
+The curve of FOM values is plotted in Figure~\ref{fig:PF_example_1} (the blue line); several points are randomly sampled from the FOM curve to train the GP model, the LCB, EI, PI functions and the Pareto front of the acquisition functions are plotted in Figure~\ref{fig:PF_example_2}.
+We can see from Figure~\ref{fig:PF_example_2} that the optimal locations of the three acquisition functions are different, while their best trade-off is captured by the Pareto front.
+The Pareto set that represents the best trade-off between the three acquisition functions is the interval $[43, 50.4]$, as plotted in Figure~\ref{fig:PF_example_1}.
+The candidate points for the next batch of evaluations are randomly sampled from the Pareto set.
 

### 2018-02-07 paper/background.tex
Paper update

@@
 black-box optimization problem:
-
 \begin{equation}
     \label{eq:Formulation}
-    \text{minimize}~\mathrm{FOM}(\bm{x})
+    \text{minimize}~\mathrm{FOM}(\bm{x}), 
 \end{equation}
-
 where $\bm{x} \in \textrm{D}$ is the vector of design variables,
@@
             \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
-            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x})
+            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x}), 
         \end{array}
@@
     \label{eq:LCB}
-    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x})
+    \mathrm{LCB}(\bm{x}) = \mu(\bm{x}) - \kappa \sigma(\bm{x}), 
 \end{equation}
-Where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.
+where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.
 

### 2018-02-07 paper/abstract.tex
revise abstract

--- 2018-02-06 paper/abstract.tex
@@
 \begin{abstract}
-    The Bayesian optimization algorithm has recently shown promising
-    performance for the automated design analog integrated circuits. However,
-    the sequential property of Bayesian optimization limits its further
-    application. In this paper, a batch bayesian optimization algorithm is
-    proposed, the parallelization is realized via a multi-objective ensemble of
-    acquisition functions. In each iteration, multiple acquisition functions
-    are selected, the multi-objective optimization is performed to search for
-    the Pareto front of the acquisition functions, candidate points are then
-    sampled from the Pareto front. The proposed method is compared with several
+    Bayesian optimization methods are promising for the optimizations of black-box functions that are expensive to evaluate.
+In this paper, a novel batch Bayesian optimization approach is proposed.
+The parallelization is realized via a multi-objective ensemble of multipe
+    acquisition functions. In each iteration, the multi-objective optimization of the multiple acquisition functions is performed to search for
+    the Pareto front of the acquisition functions.
+The batches of inputs are then selected from the Pareto front.
+The Pareto front represents the best trade-off between the multiple acquisition functions.
+Such a policy for batched Bayesian optimization can significantly improve the efficiency of optimization.
+The proposed method is compared with several
     state-of-the-art batch Bayesian optimization algorithms using analytical
-    benchmark functions and real-world analog circuits; the experimental
-    results show that the proposed method is competitive compared to the
+    benchmark functions and real-world analog circuits. The experimental
+    results show that the proposed method is competitive compared with the
     state-of-the-art algorithms.

### 2018-02-07 paper/intro.tex
minor revision of introduction.

@@
 %
-The advancement of modern society is driven by the development of integrated
-circuits (IC), unlike the digital circuits where the design flow is already
+The advancement of modern society is driven by the development of Integrated
+Circuits (IC). Unlike the digital circuits where the design flow is already
 highly automated, the automation of analog circuit design is still a
@@
 
-For analog circuits, the design parameters like widths and lengths of
+Traditionally, the design parameters of analog circuits like widths and lengths of
 transistors are manually calculated by designers with their experience and the
@@
 manufacture technology forecasted by Moore's law, the circuit devices become
-more and more complicated, and the parasitic effect of the circuit can no
-longer be ignored; on the other hand, the demands for high-performance,
-low-power analog circuits is increasing. It is getting much more difficult to
-meet the performance and time-to-market requirement with manual circuit analysis.
+more and more complicated, and the parasitic effect of the circuits can no
+longer be ignored. On the other hand, the demands for high-performance,
+low-power analog circuits are increasing. It is much more difficult to
+meet the performance and time-to-market requirements with manual circuit design.
 Automated analog circuit design has thus attracted much research interest in
@@
 The analog circuit design automation problems can be formulated as optimization
-problems, the aim is to find the optimal vector of design parameters that gives
-the best circuti performance, which is represented by a figure of merit (FOM)
+problems. The aim is to find the optimal design parameters that provide
+the best circuit performance, which can be represented by a figure of merit (FOM)
 function. Prior works about analog circuit optimization include offline
@@
 accurate global models and then optimize the cheap-to-evaluate models. The
-problem of this approach is that the accurate models are usually hard to get;
-for example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
+problem of this approach is that the accurate models are usually hard to get.
+For example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
 used to train a sparse polynomial model for an amplifier circuit with ten
@@
 
-Simulation-based methods, instead, treat the circuits as black-box functions
-that get the FOM values from circuit simulations, global optimization
+Simulation-based methods, instead, treat the performances of the circuits as black-box functions. The performances are obtained from circuit simulations. Global optimization
 algorithms are then directly applied to the black-box functions. For
 simulation-based circuit optimization methods, meta-heuristic
-algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used, although
+algorithms~\cite{phelps2000anaconda, liu2009analog} are widely used. Although
 these algorithms can explore the whole design space, they have relatively low
@@
 assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
-differential evolution algorithm; recently, the
+differential evolution algorithm. Recently, the
 Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
@@
 firstly introduced for the single- and multi-objective optimization of general analog circuits and has
-shown to be more sample-efficient compared to other simulation-based
+shown to be more efficient compared to other simulation-based
 approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
@@
 often desirable to select a batch of points at each iteration, the sequential
-property of BO limits its further application in multi-core computer systems.
+property of Bayesian optimization limits its further applications in multi-core computer systems.
 
 The Bayesian optimization algorithm has been extended to enable batch
-selection. Some prior works, like the qEI\cite{qEI}, qKG\cite{wu2016parallel}
+selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
 and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
@@
 works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
-batch-UCB(BUCB, BLCB for minimization
+batch-UCB (BUCB, BLCB for minimization
 problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
@@
 All the algorithms mentioned above choose to use single acquisition function,
-and except for the SM method and LP method which can use arbitrary acquisition
-function, other parallelization methods rely on a specific acquisition
+except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
+function. The other parallelization methods rely on a specific acquisition
 function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
@@
 in~\cite{hoffman2011portfolio}, no single acquisition function can always
-outperform other acquisition functions, relying on one acquisition function may
+outperform other acquisition functions. Relying on one acquisition function may
 result in poor performance.
@@
 In this paper, we propose to parallelize the Bayesian optimization algorithm
-via the multi-objective acquisition ensemble (MACE). The proposed MACE method
+via the Multi-objective ACquisition Ensemble (MACE). The proposed MACE method
 exploits the disagreement between different acquisition functions to enable
-parallel selection. At each iteration, after the GP model is updated, multiple
-acquisition functions are selected, we then perform multi-objective
+batch selection. At each iteration, after the GP model is updated, multiple
+acquisition functions are selected. We then perform multi-objective
 optimization to find the \emph{Pareto front} (PF) of the acquisition functions.
 The PF represents the best trade-off between these acquisition functions. When
-batch evaluations are possible, we can sample multiple points on the optimized
-PF to accelerate the optimization.
+batch evaluations are possible, we can sample multiple points on the PF to accelerate the optimization.
 
@@
 design parameters and a class-E power amplifier with twelve design parameters.
-The BLCB method, local penalization method with expected improvement
-acquisition function (EI-LP), qEI methods and qKG methods are compared with
+The BLCB method~\cite{desautels2014parallelizing}, local penalization method with expected improvement
+acquisition function (EI-LP)~\cite{gonzalez2016batch}, qEI \cite{qEI} methods and qKG \cite{wu2016parallel} are compared with
 MACE. The proposed MACE method achieved competitive performance when compared

### 2018-02-07 paper/background.tex

@@
 % TODO: See how other people describe GP and BO}
+In this section, we will present the problem formulation of analog circuit optimization, and review the background of Gaussian process regression and Bayesian optimization.
 
@@
 
-We handle the scenarios where the topology of the analog circuit is fixed, this
+We handle the scenarios where the topology of the analog circuit is fixed. This
 is practical as there are usually a lot of classical topologies for given
@@
 device model. What we want to do is automatically searching for the optimal
-design parameters, the problem can then be formulated as a bound-constrained
+design parameters. This problem can then be formulated as a bound-constrained
 black-box optimization problem:
@@
 specifications. Given the design parameters $\bm{x}$, the FOM value can be
-obtained by commercial circuit simulators like HSPICE or spectre.
+obtained by commercial circuit simulators like HSPICE or Spectre.
 
@@
 
-We model the $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} with Gaussian
+The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be approximated by Gaussian
 process (GP) model~\cite{GPML}. The GP model is the most commonly used model
-for Bayesian optimization, the advantage of GP is that it can give a
+for Bayesian optimization. The advantage of GP is that it provides a
 well-calibrated uncertainty of prediction. GP is characterized by a mean
@@
 f(\bm{x}) \sim N(\mu(\bm{x}),
-\sigma^2(\bm{x}))
+\sigma^2(\bm{x})),
 \label{eq:GPRPred}
@@
             \mu(\bm{x}) &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
-            \sigma^2(\bm{x}) &=& \sigma_f^2 - k(\bm{x}, X)K^{-1}k(X, \bm{x}), 
+            \sigma^2(\bm{x}) &=&  - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
         \end{array}
@@
 $\mu(\bm{x})$ can be viewed as the prediction of the function value, while
-the $\sigma^2(\bm{x})$ is a measure of uncertainty.
+the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction.
+The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.
 
-\textcolor{red}{$\sigma_f$ ???}
+\textcolor{red}{$\sigma_f$ ???, it is not necessary to mention it here.}
 
@@
 Bayesian optimization~\cite{shahriari2016taking} was proposed for the
-optimization of expensive black-box functions, it has two essential
-ingredients, i.e., the probabilistic surrogate models and acquisition
+optimization of expensive black-box functions. It consists of two essential
+ingredients, i.e., the probabilistic surrogate models and the acquisition
 functions. The probabilistic surrogate models provide predictions with
 uncertainties. The acquisition functions make use of the predictive
-distribution to explore the state space, the procedure of Bayesian optimization
+distribution to explore the state space. The procedure of Bayesian optimization
 is summarized in Algorithm~\ref{alg:BayesianOptAlgo}.
@@
 The acquisition function considers both the predictive value and the uncertainty.
-There are a lot of existing acquisition functions, examples include the lower confidence bound (LCB), the probability of improvement (PI), and the expected improvement (EI).
+There are a lot of existing acquisition functions.
+Examples include the lower confidence bound (LCB), the probability of improvement (PI), and the expected improvement (EI).
 
@@
 
-The PI and EI function are defined as
+The PI and EI functions are defined as
 \begin{equation}

### 2018-02-07 paper/mace.tex
Paper update
Add input parameters in the algorithm blocks

@@
 \subsection{Multi-objective Optimization of Acquisition Functions}\label{sec:MOForumlation}
-
-\textcolor{red}{See how other MOBO paper formulate multi-objective optimization}
 
@@
 
-% TODO: We illustrate the proposed MACE algorithm using the Branin-Hoo function~\cite{dixon1978global}
-% TODO: plot contour of Branin/Ei/LCB/PI, plot the PS and the PF
+The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
+
+\begin{algorithm}
+    \caption{Multi-objective Acquisition Ensemble Algorithm}
+    \label{alg:MACE}
+    \begin{algorithmic}[1]
+        \REQUIRE Number of initial sampling points $N_{init}$, number of iterations $N_{iter}$, batch size $B$.
+        \STATE Randomly sample $N_{init}$ points in the design space
+        \STATE Construct initial GP model
+        \FOR{t = 1, 2, \dots, $N_{iter}$}
+        \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
+        \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
+        \STATE Randomly sample $B$ points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front
+        \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
+        \STATE Update the GP model
+        \ENDFOR
+        \STATE \textbf{Return} best $f(\bm{x})$ recorded during iterations
+    \end{algorithmic}
+\end{algorithm}
+
 We illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.
@@
 
-The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
-
-\textcolor{red}{TODO: Input, Output parameters, see how other papers format the algorithm description}
-\begin{algorithm}
-\caption{Multi-objective Acquisition Ensemble Algorithm}
-\label{alg:MACE}
-\begin{algorithmic}[1]
-\STATE Initial Sampling
-\STATE Construct initial GP model
-\FOR{t = 1, 2, \dots}
-    \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
-    \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
-    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front where B is the batch size
-    \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
-    \STATE Update the GP model
-\ENDFOR
-\STATE Return best $f(\bm{x})$ recorded during iterations
-\end{algorithmic}
-\end{algorithm}
-
-\textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}
+% \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}

### 2018-02-07 paper/mace.tex
Paper update
minor revision of mace.tex

--- 2018-02-07 paper/mace.tex
@@
 \section{Proposed Batch Bayesian Optimization Algorithm}
+We will present the proposed batch Bayesian optimization algorithm in this section.
 
@@
 
-\subsection{Multi-objective Optimization of Acquisition Functions}\label{sec:MOForumlation}
+\subsection{Multi-objective Optimization}\label{sec:MOForumlation}
 
@@
 
-\subsection{Batch Bayesian Optimization via Multi-objective Acquisition Ensemble}
+\subsection{Batch Bayesian Optimization via Multi-objective Acquisition Function Ensemble}
 
 Each acquisition function represents a unique selection strategy, different acquisition functions may not agree with each other about where to sample the next point.
-For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases, however, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$.
-For a noise-free problem, the EI values at already sampled points would always be lower than any unsampled location, while this property does not hold for the LCB function.
+For example, the value of LCB function always decreases as the $\sigma(\bm{x})$ increases.
+However, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$.
+For the EI function, the values of EI function at already sampled points would always be lower than any unsampled locations, while this property does not hold for the LCB function.
 
@@
 
-In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected, but other acquisition functions like KG and PES can also be incorporated into the MACE framework.
-In each iteration, the following MO problem is constructed:
+In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected.
+Other acquisition functions like KG and PES can also be incorporated into the MACE framework.
+In each iteration, the following multi-objective optimization problem is constructed:
 \begin{equation}
@@
 \end{equation}
-Then the DEMO multi-objective optimization algorithm is applied to solve the multi-objective problem in \eqref{eq:MO_LCB_EI_PI}.
-Once the Pareto front of LCB, EI and PI is obtained, the candidate evalution points are then randomly sampled from the Pareto front.
+Then the DEMO multi-objective optimization algorithm~\cite{demo} is applied to solve the multi-objective problem in \eqref{eq:MO_LCB_EI_PI}.
+Once the Pareto front of LCB, EI and PI is obtained, the candidate points are then randomly sampled from the Pareto front.
 
@@
 The optimization objective is to maximize the phase margin (PF) of the amplifier, so the FOM is defined as $\mathrm{FOM}(\bm{x}) = - \mathrm{PF}(\bm{x})$.
-The width of one of its transistor is the design variable, we sweep the width of the transistor and perform HSPICE simulations to get the FOM values.
-The curve of FOM values is plotted in Figure~\ref{fig:PF_example_1} (the blue line); several points are randomly sampled from the FOM curve to train the GP model, the LCB, EI, PI functions and the Pareto front of the acquisition functions are plotted in Figure~\ref{fig:PF_example_2}.
+The width of one of its transistor is the design variable.
+We sweep the width of the transistor and perform circuit simulations to get the FOM values.
+The curve of FOM values is plotted in Figure~\ref{fig:PF_example_1} (the blue line).
+Several points are randomly sampled from the FOM curve to train the GP model.
+The LCB, EI, PI functions and the Pareto front of the acquisition functions are plotted in Figure~\ref{fig:PF_example_2}.
 We can see from Figure~\ref{fig:PF_example_2} that the optimal locations of the three acquisition functions are different, while their best trade-off is captured by the Pareto front.
@@
 
-\textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}
+% \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}

### 2018-02-07 paper/mace.tex

@@
     \label{fig:PF_example}
-        % \begin{subfigure}[]{width=0.5\textwidth}
-        %     \includegraphics[width=0.5\textwidth]{./img/pf.eps}
-        %     \caption{LCB, EI, PI and PF}
-        %     \label{fig:PF_example_1}
-        % \end{subfigure}
-        % \begin{subfigure}[]{0.5\textwidth}
-        %     \includegraphics[width=0.5\textwidth]{./img/pm_gp_ps.eps}
-        %     \caption{True curve, GP predictions and PS}
-        %     \label{fig:PF_example_1}
-        % \end{subfigure}
 \end{figure*}
@@
 \subsection{Multi-objective Optimization}\label{sec:MOForumlation}
-
-\textcolor{red}{See how other MOBO paper formulate multi-objective optimization}
 
@@
 The width of one of its transistor is the design variable.
-We sweep the width of the transistor and perform circuit simulations to get the FOM values.
+We sweep the width of the transistor and perform HSPICE simulations to get the FOM values.
 The curve of FOM values is plotted in Figure~\ref{fig:PF_example_1} (the blue line).
@@
 
-The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
-
-\textcolor{red}{TODO: Input, Output parameters, see how other papers format the algorithm description}
-\begin{algorithm}
-\caption{Multi-objective Acquisition Ensemble Algorithm}
-\label{alg:MACE}
-\begin{algorithmic}[1]
-\STATE Initial Sampling
-\STATE Construct initial GP model
-\FOR{t = 1, 2, \dots}
-    \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
-    \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
-    \STATE Randomly sample B points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front where B is the batch size
-    \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$
-    \STATE Update the GP model
-\ENDFOR
-\STATE Return best $f(\bm{x})$ recorded during iterations
-\end{algorithmic}
-\end{algorithm}
-
 % \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}

### 2018-02-07 paper/experiments.tex
New schematic of classE PA
Data for benchmark functions

@@
 
-\begin{table*}[tp]
+% \begin{table*}[tp]
+%     \tiny
+%     \centering
+%     \caption{Optimization results of the benchmark functions}
+%     \label{tab:result_analytical}
+%     \begin{tabular}{lllllllllll}
+%         \toprule
+%         Function    & MACE-1             & LCB-1                 &  EI-1                 &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4                   & qEI-4                     \\ \midrule
+%         Eggholder   & 88$\pm$76          &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            & \\
+%         Branin      & 1e-5$\pm$1.3e-5    &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    & \\
+%         Alpine1     & 2.7$\pm$1.1        &  5.7$\pm$1.8          &  2.5$\pm$1.6          &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          & \\
+%         Hart6       & 0.065$\pm$0.062    &  0.13$\pm$0.12        &  0.11$\pm$0.15        &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        & \\
+%         Ackley      & 1.7$\pm$1.1        &  1.6$\pm$0.93         &  1$\pm$0.99           &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            & \\
+%         Rosenbrock  & 0.026$\pm$0.051    &  0.02$\pm$0.021       &  14$\pm$9.5           &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            & \\
+%         G05         & 3.1$\pm$0.45       &  3.1$\pm$0.52         &  19$\pm$0.65          &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           & \\
+%         G07         & 500$\pm$300        &  520$\pm$290          &  1400$\pm$640         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          & \\
+%         \bottomrule
+%     \end{tabular}
+% \end{table*}
+
+\begin{table*}[t]
     \centering
@@
         \toprule
-        Function           & MACE-1 & LCB-1  & EI-1  & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
-         Branin            &        &        &       &         &         &         &       &        \\
-         Alpine1           &        &        &       &         &         &         &       &        \\
-         Hartmann6         &        &        &       &         &         &         &       &        \\
-         Eggholder         &        &        &       &         &         &         &       &        \\
-         Ackley2           &        &        &       &         &         &         &       &        \\
-         Rosenbrock2       &        &        &       &         &         &         &       &        \\
-         Ackley10          &        &        &       &         &         &         &       &        \\
-         Rosenbrock10      &        &        &       &         &         &         &       &        \\
+                    & MACE-1                & LCB-1                 &  EI-1                 &                & \\ \midrule
+        Eggholder   & 88$\pm$76             &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &                & \\
+        Branin      & 1e-5$\pm$1.3e-5       &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &                & \\
+        Alpine1     & 2.7$\pm$1.1           &  5.7$\pm$1.8          &  2.5$\pm$1.6          &                & \\
+        Hart6       & 0.065$\pm$0.062       &  0.13$\pm$0.12        &  0.11$\pm$0.15        &                & \\
+        Ackley      & 1.7$\pm$1.1           &  1.6$\pm$0.93         &  1$\pm$0.99           &                & \\
+        Rosenbrock  & 0.026$\pm$0.051       &  0.02$\pm$0.021       &  14$\pm$9.5           &                & \\
+        G05         & 3.1$\pm$0.45          &  3.1$\pm$0.52         &  19$\pm$0.65          &                & \\
+        G07         & 500$\pm$300           &  520$\pm$290          &  1400$\pm$640         &                & \\
+        \hline
+                    &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4          & qEI-4                 \\ \midrule
+        Eggholder   &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            \\
+        Branin      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    \\
+        Alpine1     &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          \\
+        Hart6       &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        \\
+        Ackley      &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            \\
+        Rosenbrock  &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            \\
+        G05         &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           \\
+        G07         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          \\
         \bottomrule
@@
 
-\begin{table}[]
+\begin{table}[h]
     \centering
@@
 
-\subsection{ClassE Power Amplifier}
+\subsection{Class-E Power Amplifier}
 
@@
     \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/classE.png}}
-        \caption{Schematic of the power amplifier\textcolor{red}{TODO: replace this schematic with eps file} }
+        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
+        \caption{Schematic of the power amplifier}
         \label{fig:schPA}

### 2018-02-07 paper/experiments.tex
Paper update

@@
-\begin{figure*}[htbp]
-    \begin{center}
-        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+\section{Experimental Results}
+
+\begin{table*}[t]
+    \centering
     \caption{Optimization results of the benchmark functions}
-        \label{fig:CovPlotBenchmark}
-    \end{center}
-\end{figure*}
-
-\section{Experimental Results}
+    \label{tab:result_analytical}
+    \begin{tabular}{lllllllllll}
+        \toprule
+                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
+        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
+        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
+        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
+        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
+        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
+        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
+        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
+        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
+        \hline
+                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
+        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
+        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
+        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
+        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
+        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
+        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
+        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
+        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
+        \bottomrule
+    \end{tabular}
+\end{table*}
 
@@
 
-\begin{table*}[t]
-    \centering
-    \caption{Optimization results of the benchmark functions}
-    \label{tab:result_analytical}
-    \begin{tabular}{lllllllllll}
-        \toprule
-                    & MACE-1                & LCB-1                 &  EI-1                 &                & \\ \midrule
-        Eggholder   & 88$\pm$76             &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &                & \\
-        Branin      & 1e-5$\pm$1.3e-5       &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &                & \\
-        Alpine1     & 2.7$\pm$1.1           &  5.7$\pm$1.8          &  2.5$\pm$1.6          &                & \\
-        Hart6       & 0.065$\pm$0.062       &  0.13$\pm$0.12        &  0.11$\pm$0.15        &                & \\
-        Ackley      & 1.7$\pm$1.1           &  1.6$\pm$0.93         &  1$\pm$0.99           &                & \\
-        Rosenbrock  & 0.026$\pm$0.051       &  0.02$\pm$0.021       &  14$\pm$9.5           &                & \\
-        G05         & 3.1$\pm$0.45          &  3.1$\pm$0.52         &  19$\pm$0.65          &                & \\
-        G07         & 500$\pm$300           &  520$\pm$290          &  1400$\pm$640         &                & \\
-        \hline
-                    &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4          & qEI-4                 \\ \midrule
-        Eggholder   &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            \\
-        Branin      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    \\
-        Alpine1     &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          \\
-        Hart6       &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        \\
-        Ackley      &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            \\
-        Rosenbrock  &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            \\
-        G05         &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           \\
-        G07         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          \\
-        \bottomrule
-    \end{tabular}
-\end{table*}
-
 \subsection{Operational Amplifier}
@@
 %TODO: Introduce the importance of OpAmp and PA
-
-\textcolor{red}{TODO: if possible, run qKG and qEI for this circuit}
 

### 2018-02-07 paper/experiments.tex
Paper update

@@
     \end{tabular}
+    \vskip -0.2in
 \end{table}
@@
 
-The mean convergence plot is shown in Figure~\ref{fig:CovPlotBenchmark}. The
-statistics of the final optimization results are listed in
-Table~\ref{tab:result_analytical}. As can be seen, when running with batch size
-$B = 4$, the MACE algorithm gives the best performance for six out of the eight
-benchmarks.  For the 2D Ackley function, EI-LP is the best algorithm, while for
-the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
-performance.  Compare the batch MACE and the sequential MACE, the speedup is
-also dramatic.
+The mean performances of the tested algorithms on the benchmark functions are
+plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
+optimization results are listed in Table~\ref{tab:result_analytical}. As can be
+seen in Figure~\ref{fig:CovPlotBenchmark} and
+Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
+algorithm is competitive with the LCB and EI acquisition functions, the MACE-1
+algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
+Branin, Hartmann6, Ackley10, and Rosenbrock10 functions; also, the parallel
+MACE (MACE-4) gave the best performances among all the tested algorithms for
+six out of the eight benchmark functions, and has shown dramatic speedup
+compared to the sequential MACE (MACE-1).
 
-% \begin{table*}[tp]
-%     \tiny
-%     \centering
-%     \caption{Optimization results of the benchmark functions}
-%     \label{tab:result_analytical}
-%     \begin{tabular}{lllllllllll}
-%         \toprule
-%         Function    & MACE-1             & LCB-1                 &  EI-1                 &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4                   & qEI-4                     \\ \midrule
-%         Eggholder   & 88$\pm$76          &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            & \\
-%         Branin      & 1e-5$\pm$1.3e-5    &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    & \\
-%         Alpine1     & 2.7$\pm$1.1        &  5.7$\pm$1.8          &  2.5$\pm$1.6          &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          & \\
-%         Hart6       & 0.065$\pm$0.062    &  0.13$\pm$0.12        &  0.11$\pm$0.15        &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        & \\
-%         Ackley      & 1.7$\pm$1.1        &  1.6$\pm$0.93         &  1$\pm$0.99           &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            & \\
-%         Rosenbrock  & 0.026$\pm$0.051    &  0.02$\pm$0.021       &  14$\pm$9.5           &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            & \\
-%         G05         & 3.1$\pm$0.45       &  3.1$\pm$0.52         &  19$\pm$0.65          &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           & \\
-%         G07         & 500$\pm$300        &  520$\pm$290          &  1400$\pm$640         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          & \\
-%         \bottomrule
-%     \end{tabular}
-% \end{table*}
+% when running with batch size $B = 4$, the
+% MACE algorithm gives the best performance for six out of the eight benchmarks.
+% For the 2D Ackley function, EI-LP is the best algorithm, while for the
+% Eggholder function, the MACE, BLCB, and EI-LP have quite similar performance.
+% Compare the batch MACE and the sequential MACE, the speedup is also dramatic.
 
@@
     \end{center}
+    \vskip -0.2in
 \end{figure}
@@
 
-We run the algorithms in sequential mode and batch mode, for the batch
-mode, batch size is set to $B = 4$. The number initial random sampling is set
-to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
+We run the algorithms in sequential mode and batch mode, for the batch mode,
+batch size is set to $B = 4$. The number initial random sampling is set to
+$N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
 
@@
         Algorithm & Results     \\ \midrule
-        MACE-1    & 0.0$\pm$0.0 \\
-        LCB-1     & 0.0$\pm$0.0 \\
-        EI-1      & 0.0$\pm$0.0 \\
-        MACE-4    & 0.0$\pm$0.0 \\
-        BLCB-1    & 0.0$\pm$0.0 \\
-        EI-LP-4   & 0.0$\pm$0.0 \\
+        MACE-1    & -678.174$\pm$21.7445 \\
+        LCB-1     & -607.583$\pm$51.9786 \\
+        EI-1      & -532.555$\pm$66.942  \\
+        MACE-4    & \textbf{-690.3$\pm$0.104963}  \\
+        BLCB-4    & -665.442$\pm$23.066  \\
+        EI-LP-4   & -636.675$\pm$35.7359 \\
         \bottomrule
@@
 
-The mean convergence plot for the sequential and batch runs are plotted in
-Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
-solution compared with other algorithms, the sequential MACE algorithm found
-better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
-the multi-objective acquisition ensemble is more robust than relying on single
-acquisition function; compared with the sequential MACE algorithm, the MACE
-algorithm with batch size $B = 4$ showed considerable speedup.
+The mean convergence plot for the sequential and batch runs are given in
+Figure~\ref{fig:resDAC2014}, the mean and standard deviation of the final
+optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
+seen, on average, the batch MACE algorithm had the fastest convergence rate
+compared with the sequential MACE algorithm and other parallel algorithms. It
+should also be noted that the final optimized FOM values given by MACE-4 have
+very small deviation (0.105) compared with other algorithms.
+
+% The mean convergence plot for the sequential and batch runs are shown in
+% Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
+% solution compared with other algorithms, the sequential MACE algorithm found
+% better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
+% the multi-objective acquisition ensemble is more robust than relying on single
+% acquisition function; compared with the sequential MACE algorithm, the MACE
+% algorithm with batch size $B = 4$ showed considerable speedup.
 
@@
 
-\begin{figure}[htbp]
+\begin{table}[]
+    \centering
+    \caption{Optimization results of the power amplifier}
+    \label{tab:result_PA}
+    \begin{tabular}{llll}
+        \toprule
+        Algorithm & Results               \\ \midrule
+        MACE-1    & -4.08608$\pm$0.296647 \\
+        LCB-1     & -3.78533$\pm$0.335532 \\
+        EI-1      & -3.36407$\pm$0.307489 \\
+        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
+        BLCB-4    & -4.20266$\pm$0.211102 \\
+        EI-LP-4   & -4.07233$\pm$0.244436 \\
+        \bottomrule
+    \end{tabular}
+    \vskip -0.2in
+\end{table}
+
+\begin{figure}[]
     \begin{center}
@@
 
-\begin{table}[htbp]
-    \centering
-    \caption{Optimization results of the power amplifier}
-    \label{tab:result_PA}
-    \begin{tabular}{llll}
-        \toprule
-        Algorithm & Results     \\ \midrule
-        MACE-1    & 0.0$\pm$0.0 \\
-        LCB-1     & 0.0$\pm$0.0 \\
-        EI-1      & 0.0$\pm$0.0 \\
-        MACE-4    & 0.0$\pm$0.0 \\
-        BLCB-1    & 0.0$\pm$0.0 \\
-        EI-LP-4   & 0.0$\pm$0.0 \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
 The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
@@
 
-\begin{figure}[htbp]
-\vskip 0.2in
+\begin{figure}[]
     \begin{center}

### 2018-02-08 paper/experiments.tex
Paper update

@@
 
-The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
-that the MACE outperformed the BLCB and EI-LP in both sequential and batch
-mode. For the batch runs, the MACE convergences fastest among the three
-algorithms, while the sequential MACE has similar performance as the batch
-EI-LP method.
+The mean convergence plot is given in Figure~\ref{fig:resClassE}, the mean and
+standard deviation of the final FOM values are listed in
+Table~\ref{tab:result_PA}. We can see that the MACE outperformed the BLCB and
+EI-LP in both sequential and batch mode.  For the batch runs, the MACE
+convergences fastest among the three algorithms, while the sequential MACE
+algorithm while the sequential MACE has similar performance as the batch EI-LP
+method.

### 2018-02-08 paper/conclusion.tex
minor revision of experimental results and conclusion

@@
 automation of analog circuit design. The parallelization is achieved via
-the multi-objective ensemble of acquisition function. In each iteration, the
+the multi-objective ensemble of acquisition functions. In each iteration, the
 candidate points are sampled from the Pareto front of multiple acquisition
@@
 functions and real-world circuits, it is shown that the MACE algorithm is
-competitive compared with state-of-the-art method listed in the paper.
+competitive compared with the state-of-the-art methods listed in the paper.

### 2018-02-08 paper/experiments.tex
minor revision of experimental results and conclusion

--- 2018-02-07 paper/experiments.tex
@@
+\begin{figure*}[htbp]
+    \begin{center}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+\end{figure*}
+
 \section{Experimental Results}
-
-\begin{table*}[t]
-    \centering
-    \caption{Optimization results of the benchmark functions}
-    \label{tab:result_analytical}
-    \begin{tabular}{lllllllllll}
-        \toprule
-                & Eggholder                &  Branin              &  Alpine1              & Hartmann6                   \\ \midrule
-        MACE-1  & 87.65$\pm$75.83          &  1.05e-5$\pm$1.31e-5          & 2.66305$\pm$1.05844            & 0.0646869$\pm$0.0621189 \\
-        LCB-1   & 153.9$\pm$112.8          &  6.86e-5$\pm$1.13e-4          & 5.66812$\pm$1.76973            & 0.125565$\pm$0.122684   \\
-        EI-1    & 172.8$\pm$132.2          &  1.62e-2$\pm$1.63e-2          & 2.46061$\pm$1.56079            & 0.110561$\pm$0.146809   \\
-        MACE-4  & 46.38$\pm$40.89          &  \textbf{4.62e-6$\pm$6.64e-6} & \textbf{0.903805$\pm$0.835209} & \textbf{0.0275738$\pm$0.052254}  \\
-        BLCB-4  & 56.86$\pm$35.91          &  4.32e-5$\pm$6.33e-5          & 1.8843$\pm$0.938873            & 0.06447$\pm$0.0621176   \\
-        EI-LP-4 & \textbf{44.68$\pm$56.45} &  2.11e-2$\pm$1.84e-2          & 1.0059$\pm$0.456865            & 0.0540446$\pm$0.0558557 \\
-        qKG-4   & 106.4$\pm$67.64          &  2.65e-1$\pm$2.70e-1          & 3.01513$\pm$1.13414            & 0.47134$\pm$0.18939     \\
-        qEI-4   & 72.13$\pm$52.08          &  3.29e-4$\pm$1.14e-3          & 2.7074$\pm$1.05145             & 0.186088$\pm$0.116323   \\
-        \hline
-                & Ackley2                       &  Rosenbrock2               & Ackley10              & Rosenbrock10        \\ \midrule
-        MACE-1  & 1.71474$\pm$1.12154           &  0.026173$\pm$0.051189              & 3.1348$\pm$0.447874           & 499.697$\pm$300.899 \\
-        LCB-1   & 1.624$\pm$0.926437            &  0.0201124$\pm$0.0205367            & 3.14797$\pm$0.519164          & 517.944$\pm$288.955 \\
-        EI-1    & 1.0136$\pm$0.985858           &  13.5508$\pm$9.52734                & 18.8006$\pm$0.652136          & 1367.08$\pm$637.507 \\
-        MACE-4  & 1.07906$\pm$0.886466          &  \textbf{0.00095416$\pm$0.00093729} & \textbf{2.56439$\pm$0.535488} & \textbf{158.116$\pm$50.0024} \\
-        BLCB-4  & 1.40051$\pm$1.02849           &  0.00191986$\pm$0.00180895          & 3.27543$\pm$0.735501          & 406.819$\pm$127.351 \\
-        EI-LP-4 & \textbf{0.284265$\pm$0.24634} &  2.73645$\pm$2.05923                & 18.2682$\pm$0.608564          & 721.351$\pm$327.365 \\
-        qKG-4   & 5.59394$\pm$1.80595           &  5.03976$\pm$3.72014                & 18.197$\pm$0.764103           & 705.112$\pm$412.762 \\
-        qEI-4   & 2.87373$\pm$1.02405           &  10.1881$\pm$15.0432                & 18.3686$\pm$0.501869          & 655.208$\pm$340.954 \\
-        \bottomrule
-    \end{tabular}
-\end{table*}
 
@@
 method with EI acquisition function, the qEI and qKG methods\footnote{We
-implemented the BLCB algorithm as the availble open source implementations only
-allow discrete input; for the EI-LP method, the code is downloaded from
-https://github.com/SheffieldML/GPyOpt is used; the code for qEI and qKG is
+implemented the BLCB algorithm as the available open source implementations only
+allow discrete input. For the EI-LP method, the code is downloaded from
+https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is
 downloaded from https://github.com/wujian16/Cornell-MOE}.
@@
 the Eggholder function, the MACE, BLCB, and EI-LP have quite similar
-performance.  Compare the batch MACE and the sequential MACE, the speedup is
+performance.  Compared with the sequential MACE, the speedup of the batch MACE is
 also dramatic.
 
-% \begin{table*}[tp]
-%     \tiny
-%     \centering
-%     \caption{Optimization results of the benchmark functions}
-%     \label{tab:result_analytical}
-%     \begin{tabular}{lllllllllll}
-%         \toprule
-%         Function    & MACE-1             & LCB-1                 &  EI-1                 &  MACE-4               & BLCB-4                &  EI-LP-4              & qKG-4                   & qEI-4                     \\ \midrule
-%         Eggholder   & 88$\pm$76          &  1.5e+2$\pm$1.1e2     &  1.7e2$\pm$1.3e2      &  46$\pm$41            &  57$\pm$36            &  45$\pm$56            &  1.1e2$\pm$68  &  72$\pm$52            & \\
-%         Branin      & 1e-5$\pm$1.3e-5    &  6.9e-5$\pm$1.1e-4    &  0.016$\pm$0.016      &  4.6e-6$\pm$6.6e-6    &  4.3e-5$\pm$6.3e-5    &  0.021$\pm$0.018      &  0.27$\pm$0.27 &  3.3e-4$\pm$1.1e-3    & \\
-%         Alpine1     & 2.7$\pm$1.1        &  5.7$\pm$1.8          &  2.5$\pm$1.6          &  0.9$\pm$0.84         &  1.9$\pm$0.94         &  1$\pm$0.46           &  3$\pm$1.1     &  2.7$\pm$1.1          & \\
-%         Hart6       & 0.065$\pm$0.062    &  0.13$\pm$0.12        &  0.11$\pm$0.15        &  0.028$\pm$0.052      &  0.064$\pm$0.062      &  0.054$\pm$0.056      &  0.47$\pm$0.19 &  0.19$\pm$0.12        & \\
-%         Ackley      & 1.7$\pm$1.1        &  1.6$\pm$0.93         &  1$\pm$0.99           &  1.1$\pm$0.89         &  1.4$\pm$1            &  0.28$\pm$0.25        &  5.6$\pm$1.8   &  2.9$\pm$1            & \\
-%         Rosenbrock  & 0.026$\pm$0.051    &  0.02$\pm$0.021       &  14$\pm$9.5           &  9.5e-4$\pm$9.4e-4    &  1.9e-3$\pm$1.8e-3    &  2.7$\pm$2.1          &  5$\pm$3.7     &  10$\pm$15            & \\
-%         G05         & 3.1$\pm$0.45       &  3.1$\pm$0.52         &  19$\pm$0.65          &  2.6$\pm$0.54         &  3.3$\pm$0.74         &  18$\pm$0.61          &  18$\pm$0.76   &  18$\pm$0.5           & \\
-%         G07         & 500$\pm$300        &  520$\pm$290          &  1400$\pm$640         &  160$\pm$50           &  410$\pm$130          &  720$\pm$330          &  710$\pm$410   &  660$\pm$340          & \\
-%         \bottomrule
-%     \end{tabular}
-% \end{table*}
+\begin{table*}[tp]
+    \centering
+    \caption{Optimization results of the benchmark functions}
+    \label{tab:result_analytical}
+    \begin{tabular}{lllllllllll}
+        \toprule
+        Function           & MACE-1 & LCB-1  & EI-1  & MACE-4  & BLCB-4  & EI-LP-4 & qKG-4 & qEI-4  \\ \midrule
+         Branin            &        &        &       &         &         &         &       &        \\
+         Alpine1           &        &        &       &         &         &         &       &        \\
+         Hartmann6         &        &        &       &         &         &         &       &        \\
+         Eggholder         &        &        &       &         &         &         &       &        \\
+         Ackley2           &        &        &       &         &         &         &       &        \\
+         Rosenbrock2       &        &        &       &         &         &         &       &        \\
+         Ackley10          &        &        &       &         &         &         &       &        \\
+         Rosenbrock10      &        &        &       &         &         &         &       &        \\
+        \bottomrule
+    \end{tabular}
+\end{table*}
 
@@
 
+\textcolor{red}{TODO: if possible, run qKG and qEI for this circuit}
+
 The operational amplifier~\cite{wang2014enabling} shown in
-Figure~\ref{fig:schDAC2014} is used for comparison, the circuit is designed
-using the 180nm process. It has ten design parameters, including the lengths
-and widths of transistors, the resistance of resistors and the capacitance of
-capacitors. The circuit is simulated using the HSPICE circuit simulator.
+Figure~\ref{fig:schDAC2014} is used to test the Bayesian optimization algorithms. The circuit is designed
+using the 180nm process. It has 10 design parameters, including the lengths
+and widths of transistors, the resistance of the resistors and the capacitance of the
+capacitors. The circuit is simulated using the commercial HSPICE circuit simulator.
 
-We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the $FOM$ is constructed as:
+We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the Figure of Merit $FOM$ is constructed as:
 $$
@@
 For this circuit, we compared the MACE algorithm with the BLCB and EI-LP
-algorithms, the qKG and qEI are not compared as the calculation of qEI and qKG
+algorithms. The qKG and qEI are not compared as the computation of qEI and qKG
 acquisition functions become very slow for the ten-dimensional functions.
@@
 
-We run the algorithms in sequential mode and batch mode, for the batch
-mode, batch size is set to $B = 4$. The number initial random sampling is set
+We run the algorithms in sequential mode and batch mode. For the batch
+mode, the batch size is set to $B = 4$. The number of initial random sampling is set
 to $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.
 
-\begin{table}[h]
+\begin{table}[]
     \centering
@@
 
-The mean convergence plot for the sequential and batch runs are plotted in
+The mean convergence plot for the sequential and the batch runs are plotted in
 Figure~\ref{fig:resDAC2014}. As can be seen, the MACE algorithm gave better
-solution compared with other algorithms, the sequential MACE algorithm found
+solution compared with other algorithms. The sequential MACE algorithm found
 better solution than BLCB and EI-LP with batch size $B = 4$, which showed that
 the multi-objective acquisition ensemble is more robust than relying on single
-acquisition function; compared with the sequential MACE algorithm, the MACE
+acquisition function. Compared with the sequential MACE algorithm, the MACE
 algorithm with batch size $B = 4$ showed considerable speedup.
@@
         \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
-        \caption{Schematic of the power amplifier}
+        \caption{Schematic of the power amplifier\textcolor{red}{TODO: replace this schematic with eps file} }
         \label{fig:schPA}
@@
 
-The power amplifier shown in Figure~\ref{fig:schPA} is used for comparison, the
-circuit is designed using the 180nm process with twelve design parameters, the
-circuit is simulated by HSPICE to get its performances.
+The power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
+circuit is designed using the 180nm process with 12 design parameters, the
+circuit is simulated by the commercial HSPICE circuit simulator to get its performances.
 
-For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the $FOM$ is constructed as
+For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
 $$
@@
 The MACE, BLCB, and EI-LP algorithms were tested in both sequential and batch
-mode. The number of initial sampling is $N_{init} = 100$, the number of
-iterations is $N_{iter} = 100$, the batch size is set to $B = 4$, so the total
+modes. The number of initial sampling is $N_{init} = 100$. The number of
+iterations is $N_{iter} = 100$. The batch size is set to $B = 4$. The total
 number of HSPICE simulations is 500 for each batch run and 200 for each
@@
 \centerline{\includegraphics[width=\columnwidth]{./img/ClassE_mean.eps}}
-\caption{Optimization results of the class-E power amplifier}
+\caption{Optimization results of the class-E power amplifier.}
 \label{fig:resClassE}
@@
 that the MACE outperformed the BLCB and EI-LP in both sequential and batch
-mode. For the batch runs, the MACE convergences fastest among the three
+mode. For the batch runs, the MACE converges fastest among the three
 algorithms, while the sequential MACE has similar performance as the batch

### 2018-02-08 paper/experiments.tex

--- 2018-02-07 paper/experiments.tex
@@
 Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
-algorithm is competitive with the LCB and EI acquisition functions, the MACE-1
+algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
 algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
-Branin, Hartmann6, Ackley10, and Rosenbrock10 functions; also, the parallel
+Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
 MACE (MACE-4) gave the best performances among all the tested algorithms for
@@
 The operational amplifier~\cite{wang2014enabling} shown in
-Figure~\ref{fig:schDAC2014} is used for comparison, the circuit is designed
-using the 180nm process. It has ten design parameters, including the lengths
-and widths of transistors, the resistance of resistors and the capacitance of
-capacitors. The circuit is simulated using the HSPICE circuit simulator.
+Figure~\ref{fig:schDAC2014} is used to test the Bayesian optimization algorithms. The circuit is designed
+using the 180nm process. It has 10 design parameters, including the lengths
+and widths of transistors, the resistance of the resistors and the capacitance of the
+capacitors. The circuit is simulated using the commercial HSPICE circuit simulator.
 
-We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the $FOM$ is constructed as:
+We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the Figure of Merit $FOM$ is constructed as:
 $$
@@
 
-We run the algorithms in sequential mode and batch mode, for the batch mode,
-batch size is set to $B = 4$. The number initial random sampling is set to
+We run the algorithms in sequential mode and batch mode. For the batch mode,
+the batch size is set to $B = 4$. The number of initial random sampling is set to
 $N_{init} = 100$, and the number of iterations is set to $N_{iter} = 100$.

### 2018-02-08 paper/mace.tex
Paper update

@@
 A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
-A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominate at least one point.
+A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominates at least one point.
 The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}.
@@
 
+\begin{figure*}[htbp]
+    \begin{center}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+\end{figure*}
+
 We illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.

### 2018-02-08 paper/background.tex
Paper update

@@
 
-% TODO: See how other people describe GP and BO}
 In this section, we will present the problem formulation of analog circuit optimization, and review the background of Gaussian process regression and Bayesian optimization.
@@
 \subsection{Problem Formulation}
-
-% TODO: The circuit performance comes from \bf{circuit} simulation}
-% TODO: format, citation of HSPICE/spectre}
-% TODO: See how other analog circuit optimization paper formulate the problem}
 
@@
 $\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
-specifications. Given the design parameters $\bm{x}$, the FOM value can be
-obtained by commercial circuit simulators like HSPICE or Spectre.
-
-% \textcolor{red}{TODO: If there is still space, illustrate the objecive with the PM-width figure}
-
-% \begin{figure}[]
-%     \begin{center}
-%         \centerline{\includegraphics[width=\columnwidth]{./img/PM.eps}}
-%         \caption{Phase margin of an amplifier as function of the width of a transistor}
-%         \label{fig:PMOpAmp}
-%     \end{center}
-% \end{figure}
+specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric of noisy
+depending on the design specifications. Given the design parameters $\bm{x}$,
+the FOM value can be obtained by commercial circuit simulators like HSPICE or
+Spectre.
 
@@
 
-\textcolor{red}{
-    TODO:
-    \begin{enumerate}
-            \item Noise
-            \item MLE learning
-    \end{enumerate}
-}
+% \textcolor{red}{
+%     TODO:
+%     \begin{enumerate}
+%             \item Noise
+%             \item MLE learning
+%     \end{enumerate}
+% }
 
@@
             \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
-            \sigma^2(\bm{x}) &=&  - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
+            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
         \end{array}
@@
 The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.
-
-\textcolor{red}{$\sigma_f$ ???, it is not necessary to mention it here.}
 
@@
 
-\textcolor{red}{TODO: Add Input, Output parameters}
 \begin{algorithm}
@@
     \begin{algorithmic}[1]
-\STATE Initial Sampling
+        \REQUIRE Number of initial sampling points $N_{init}$, number of iterations $N_{iter}$
+        \STATE Randomly sample $N_{init}$ points in the design space
         \STATE Construct initial GP model
-\FOR{t = 1, 2, \dots}
+        \FOR{t = 1, 2, \dots, $N_{iter}$}
         \STATE Construct the acquisition function
@@
         \ENDFOR
-\STATE Return best $f(\bm{x})$ recorded during iterations
+        \STATE \textbf{Return} best $f(\bm{x})$ recorded during iterations
     \end{algorithmic}

### 2018-02-08 paper/background.tex
Paper update

@@
 
-The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be approximated by Gaussian
-process (GP) model~\cite{GPML}. The GP model is the most commonly used model
-for Bayesian optimization. The advantage of GP is that it provides a
-well-calibrated uncertainty of prediction. GP is characterized by a mean
-function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In this
-work, we use squared-exponential ARD kernel, and a constant mean function
-$m(\bm{x}) = \mu_0$ for all our experiments.
+The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
+approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
+most commonly used model for Bayesian optimization. The advantage of GP is that
+it provides a well-calibrated uncertainty of prediction. GP is characterized by
+a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
+this work, we use squared-exponential ARD kernel, and a constant mean function
+$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
+objective function evaluations are noisy and let GP to infer the noise level
+$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
+numerical stability.
 
@@
         \begin{array}{lll}
-            \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)K^{-1}(\bm{y} - \mu_0) \\
-            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)K^{-1}k(X, \bm{x}),
+            \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)[K+\sigma_n^2I]^{-1}(\bm{y} - \mu_0) \\
+            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)[K+\sigma_n^2]^{-1}k(X, \bm{x}),
         \end{array}
@@
 the $\sigma^2(\bm{x})$ is a measure of uncertainty of the prediction.
-The hyperparameters including the parameters of the kernel function, and $\mu_0$ can be obtained by Maximum Likelihood Estimation (MLE) based on the training data set.
 

### 2018-02-08 paper/experiments.tex
Paper update

@@
 The proposed MACE algorithm was tested using eight benchmark functions and two
-real-world circuits. Four state-of-the-art parallel Bayesian optimization
-methods were compared, including the BLCB algorithm, the local penalization
-method with EI acquisition function, the qEI and qKG methods\footnote{We
-implemented the BLCB algorithm as the available open source implementations only
-allow discrete input. For the EI-LP method, the code is downloaded from
-https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is
-downloaded from https://github.com/wujian16/Cornell-MOE}.
+real-world circuits. For the two test circuits, we used HSPICE 2012.06 to as
+the simulator to get circuit performances.
+
+Four state-of-the-art parallel Bayesian optimization methods were compared,
+including the BLCB algorithm, the local penalization method with EI acquisition
+function, the qEI and qKG methods\footnote{We implemented the BLCB algorithm as
+the available open source implementations only allow discrete input. For the
+EI-LP method, the code is downloaded from
+https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
+from https://github.com/wujian16/Cornell-MOE}. For the MACE, BLCB, and EI-LP
+method, the ARD squared-exponential kernel is used and the GP models are fitted
+by maximum likelihood estimations(MLE); for the qKG and qEI methods, the
+Matern52 kernel is used, and the GP hyperparameters are integrated via MCMC
+sampling. The Matern52 kernel and MCMC integration are the default strategies
+of the qKG and qEI implementations and it is unclear in the documentation about
+how to change the GP settings.
 
@@
 45$. Batch size is set to $B = 4$, the total number of function evaluations is
-$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we
+$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we set
 $N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten

### 2018-02-08 paper/abstract.tex
Fix typo
Paper update

@@
 In this paper, a novel batch Bayesian optimization approach is proposed.
-The parallelization is realized via a multi-objective ensemble of multipe
+The parallelization is realized via a multi-objective ensemble of multiple
     acquisition functions. In each iteration, the multi-objective optimization of the multiple acquisition functions is performed to search for
@@
 The Pareto front represents the best trade-off between the multiple acquisition functions.
-Such a policy for batched Bayesian optimization can significantly improve the efficiency of optimization.
+Such a policy for batch Bayesian optimization can significantly improve the efficiency of optimization.
 The proposed method is compared with several

### 2018-02-08 paper/intro.tex
Paper update

@@
 the best circuit performance, which can be represented by a figure of merit (FOM)
-function. Prior works about analog circuit optimization include offline
+scalar real-valued function. Prior works about analog circuit optimization include offline
 model-based approaches
@@
 simulation-based approaches. The offline model-based methods try to build
-accurate global models and then optimize the cheap-to-evaluate models. The
+accurate global models of the FOM and then optimize the cheap-to-evaluate models. The
 problem of this approach is that the accurate models are usually hard to get.
@@
 Simulation-based methods, instead, treat the performances of the circuits as black-box functions. The performances are obtained from circuit simulations. Global optimization
-algorithms are then directly applied to the black-box functions. For
+algorithms are directly applied to the black-box functions. For
 simulation-based circuit optimization methods, meta-heuristic
@@
 firstly introduced for the single- and multi-objective optimization of general analog circuits and has
-shown to be more efficient compared to other simulation-based
+shown to be more efficient compared with other simulation-based
 approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
@@
 % TODO: Beiefly introduce my algorithm
-All the algorithms mentioned above choose to use single acquisition function,
-except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
-function. The other parallelization methods rely on a specific acquisition
+All the algorithms mentioned above choose to use single acquisition function.
+And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition
+function, other parallelization methods rely on a specific acquisition
 function. The UCB acquisition function must be used for BUCB and GP-UCB-PE, and
-the knowledge gradient method must be used for the qKG algorithm. As is stated
+the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
 in~\cite{hoffman2011portfolio}, no single acquisition function can always

### 2018-02-08 paper/background.tex
Paper update

@@
 We handle the scenarios where the topology of the analog circuit is fixed. This
-is practical as there are usually a lot of classical topologies for given
+is practical as there are usually a lot of classical topologies for a given
 design task. Once the circuit topology is fixed, the designer has to choose the
@@
 $\mathrm{FOM}(\bm{x})$ is the objective constructed from the design
-specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric of noisy
+specifications, the $\mathrm{FOM}(\bm{x})$ can be deterministric or noisy
 depending on the design specifications. Given the design parameters $\bm{x}$,
@@
 a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
-this work, we use squared-exponential ARD kernel, and a constant mean function
-$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
-objective function evaluations are noisy and let GP to infer the noise level
-$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
+this work, we use squared-exponential ARD kernel~\cite{GPML}, and a constant
+mean function $m(\bm{x}) = \mu_0$ for all our experiments. By default, we
+assume the objective function evaluations are influenced by i.i.d. noise
+$\epsilon_t \sim N(0, \sigma_n^2)$ and set the noise level $\sigma_n^2$ as a
+hyperparameter.  The introduction of the i.i.d noise also helps to improve the
 numerical stability.
@@
 The $\Phi(.)$ and $\phi(.)$ functions are the CDF and PDF functions of normal distribution.
-We fix $\xi = 1e-3$ in our implementation of the MACE algorithm.
+In our implementation of the MACE algorithm, we fix $\xi$ = 1e-3.
 

### 2018-02-08 paper/experiments.tex
Paper update

--- 2018-02-08 paper/experiments.tex
@@
 \section{Experimental Results}
+
+\begin{table}[htbp]
+    \centering
+    \caption{Summary of the analytical benchmark functions}
+    \label{tab:summaryanalygical}
+    \begin{tabular}{llllllll}
+        \toprule
+         Function           & Dimension        & Search domain             \\ \midrule
+         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
+         Alpine1            & 5                & $[-10, 10]^5$             \\
+         Hartmann6          & 6                & $[0,   1]^6$              \\
+         Eggholder          & 2                & $[-512, 512]^2$           \\
+         Ackley2            & 2                & $[-32, 32]^2$             \\
+         Ackley10           & 10               & $[-32, 32]^{10}$          \\
+         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
+         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 methods were compared, including the BLCB algorithm, the local penalization
-method with EI acquisition function, the qEI and qKG methods\footnote{We
-implemented the BLCB algorithm as the available open source implementations only
-allow discrete input. For the EI-LP method, the code is downloaded from
-https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is
-downloaded from https://github.com/wujian16/Cornell-MOE}.
+method with EI acquisition function (EI-LP), the qEI and qKG
+methods\footnote{We implemented the BLCB algorithm as the available open source
+implementations only allow discrete input. For the EI-LP method, the code is
+downloaded from https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG
+is downloaded from https://github.com/wujian16/Cornell-MOE}. 
+% For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
+% used and the GP models are fitted by maximum likelihood estimations(MLE); for
+% the qKG and qEI methods, the Matern52 kernel is used, and the GP
+% hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
+% integration are the default strategies of the qKG and qEI implementations and
+% it is unclear in the documentation about how to change the GP settings.
 
@@
 
-We tested the MACE algorithm and other parallel BO method using eight commonly used benchmark
+We tested the MACE algorithm and other parallel BO methods using eight commonly used benchmark
 functions, as summarized in Table~\ref{tab:summaryanalygical}.
-
-\begin{table}[htbp]
-    \centering
-    \caption{Summary of the analytical benchmark functions}
-    \label{tab:summaryanalygical}
-    \begin{tabular}{llllllll}
-        \toprule
-         Function           & Dimension        & Search domain             \\ \midrule
-         Branin             & 2                & $[-5,  10]\times[0, 15]$  \\
-         Alpine1            & 5                & $[-10, 10]^5$             \\
-         Hartmann6          & 6                & $[0,   1]^6$              \\
-         Eggholder          & 2                & $[-512, 512]^2$           \\
-         Ackley2            & 2                & $[-32, 32]^2$             \\
-         Ackley10           & 10               & $[-32, 32]^{10}$          \\
-         Rosenbrock2        & 2                & $[-5,  10]^2$             \\
-         Rosenbrock10       & 10               & $[-20, 20]^{10}$          \\
-        \bottomrule
-    \end{tabular}
-    \vskip -0.2in
-\end{table}
 
@@
 
-The mean performances of the tested algorithms on the benchmark functions are
-plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
+The mean convergence plots of the tested algorithms on the benchmark functions are
+given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
 optimization results are listed in Table~\ref{tab:result_analytical}. As can be
 seen in Figure~\ref{fig:CovPlotBenchmark} and
-Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
+Table~\ref{tab:result_analytical}, when running in sequential mode (MACE-1 in Table~\ref{tab:result_analytical} and Figure~\ref{fig:CovPlotBenchmark}), the MACE
 algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
@@
 six out of the eight benchmark functions, and has shown dramatic speedup
-compared to the sequential MACE (MACE-1).
+compared to the sequential MACE.
 
@@
 
-The power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
+The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
 circuit is designed using the 180nm process with 12 design parameters, the
@@
 mode. For the batch runs, the MACE converges fastest among the three
-algorithms, while the sequential MACE has similar performance as the batch
-EI-LP method.
+algorithms, while the sequential MACE (MACE-1) has comparable performance as
+the batch EI-LP (EI-LP-4) method.

### 2018-02-08 paper/mace.tex
Paper update

@@
 \end{equation}
-The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives.
+The multiple objectives to be optimized can be conflicting so that it is usually impossible to find a single solution that is the optimum of all objectives.
+The goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives.
 A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
@@
 The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}.
-It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
+It is often unlikely to get the whole Pareto front as there might be infinite points on the Paret front, multi-objective optimization algorithms try to find a set of evenly distributed solutions that approximate the true Pareto front.
 
@@
         \STATE Construct the LCB, EI and PI functions according to \eqref{eq:LCB} and \eqref{eq:PI_EI}
-        \STATE Find the Pareto front of LCB, EI, PI function using the DEMO algorithm
-        \STATE Randomly sample $B$ points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto front
+        \STATE Find the Pareto front of LCB, EI, PI functions using the DEMO algorithm
+        \STATE Randomly sample $B$ points $\bm{x}_1, \dots, \bm{x}_B$ from the Pareto-optimal points
         \STATE Evaluate $\bm{x}_1, \dots, \bm{x}_B$ to get $y_1 = f(\bm{x}_1),~\dots~,y_B = f(\bm{x}_B)$

### 2018-02-09 paper/background.tex
minor revisions

--- 2018-02-08 paper/background.tex
@@
 this work, we use squared-exponential ARD kernel, and a constant mean function
-$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
+$m(\bm{x}) = \mu_0$ for all our experiments. By default, we assume the
 objective function evaluations are noisy and let GP to infer the noise level
-$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
+$\sigma_n$. The introduction of the $\sigma_n$ level also helps to improve the
 numerical stability.

### 2018-02-09 paper/experiments.tex
minor revisions

--- 2018-02-08 paper/experiments.tex
@@
 real-world circuits. For the two test circuits, we used HSPICE 2012.06 to as
-the simulator to get circuit performances.
+the simulator to get the circuit performances.
 
@@
 We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
-acquisition functions, the sequential EI and LCB based Bayesian optimization
+acquisition functions. The sequential EI and LCB based Bayesian optimization
 are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
@@
 Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
-algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
-algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
+algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
+algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
 Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
@@
 
-We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the Figure of Merit $FOM$ is constructed as:
+We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier. The Figure of Merit $FOM$ is constructed as
 $$
-\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
+\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}.
 $$
@@
 The mean convergence plot for the sequential and batch runs are given in
-Figure~\ref{fig:resDAC2014}, the mean and standard deviation of the final
+Figure~\ref{fig:resDAC2014}. The mean and standard deviation of the final
 optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
@@
 
-For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
+For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout). The Figure of Merit $FOM$ is constructed as
 $$
-\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
+\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}.
 $$

### 2018-02-09 paper/intro.tex
minor revisions

--- 2018-02-07 paper/intro.tex
@@
 demonstrated to be promising for the automated design of analog circuits.
-However, the standard Bayesian optimization algorithm is sequential, it chooses
+However, the standard Bayesian optimization algorithm is sequential. It chooses
 only one point at each iteration by optimizing the acquisition function. It is
-often desirable to select a batch of points at each iteration, the sequential
+often desirable to select a batch of points at each iteration. The sequential
 property of Bayesian optimization limits its further applications in multi-core computer systems.

### 2018-02-09 paper/mace.tex
minor revisions

--- 2018-02-08 paper/mace.tex
@@
 
-Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}, the multi-objective optimization problem is formulated as
+Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}. The multi-objective optimization problem is formulated as
 \begin{equation}
@@
 \end{equation}
-The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives.
+The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives.
+The goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives.
 A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$.
@@
 The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}.
-It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
+It is often unlikely to get the whole Pareto front as there might be infinite points on the front.
+The goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
 

### 2018-02-09 paper/intro.tex
Paper update

--- 2018-02-08 paper/intro.tex
@@
 The analog circuit design automation problems can be formulated as optimization
-problems. The aim is to find the optimal design parameters that provide
-the best circuit performance, which can be represented by a figure of merit (FOM)
-scalar real-valued function. Prior works about analog circuit optimization include offline
-model-based approaches
+problems. The aim is to find the optimal design parameters that provide the
+best circuit performance, which can be represented by a figure of merit (FOM)
+scalar real-valued function. Prior works about analog circuit optimization
+include offline model-based approaches
 ~\cite{colleran2003optimization,daems2003simulation,wang2014enabling} and
 simulation-based approaches. The offline model-based methods try to build
-accurate global models of the FOM and then optimize the cheap-to-evaluate models. The
-problem of this approach is that the accurate models are usually hard to get.
-For example, in~\cite{wang2014enabling}, 100,000 randomly simulated points are
-used to train a sparse polynomial model for an amplifier circuit with ten
-design parameters.
+global models of the FOM via manual calculation or regression with simulated
+data and then optimize the cheap-to-evaluate models. The problem with this
+approach is that the accurate models are usually hard to get. For example,
+in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
+a sparse polynomial model for an amplifier circuit with ten design parameters.
 
@@
 % parallelize it
-%
-% TODO: cite the two 3D-IC papers of TVLSI
-To reduce the number of circuit simulations, the Gaussian process
-(GP)~\cite{GPML} model has been introduced as an online surrogate model to
-assist the optimization. In~\cite{liu2014gaspad}, GP is combined with
-differential evolution algorithm. Recently, the
-Bayesian optimization (BO)~\cite{shahriari2016taking} algorithm has been
-applied for analog circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization algorithm is
-firstly introduced for the single- and multi-objective optimization of general analog circuits and has
-shown to be more efficient compared with other simulation-based
-approaches. In~\cite{wang2017efficient}, the Bayesian optimization algorithm
-is combined with adaptive Monte-Carlo sampling to optimize the yield of analog
-circuits and static random-access memory (SRAM).
+
+In recent years, the Gaussian process (GP)~\cite{GPML} model has been
+introduced for the automated design of analog circuits to reduce the
+required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
+with differential evolution algorithm. Recently, the Bayesian optimization
+(BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
+circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
+algorithm is firstly introduced for the single- and multi-objective
+optimization of general analog circuits and has shown to be more efficient
+compared with other simulation-based approaches. In~\cite{wang2017efficient},
+the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
+sampling to optimize the yield of analog circuits and static random-access
+memory (SRAM).
 
@@
 problems)~\cite{desautels2014parallelizing} method, the parallel UCB with pure
-exploration (GP-UCB-PE)~\cite{contal2013parallel} method and the local
+exploration (GP-UCB-PE)~\cite{contal2013parallel} method, and the local
 penalization (LP)~\cite{gonzalez2016batch} method, adopted the \emph{greedy}
@@
 % TODO: Beiefly introduce my algorithm
-All the algorithms mentioned above choose to use single acquisition function.
+All the batch Bayesian optimization algorithms mentioned above choose to use single acquisition function.
 And except for the SM method~\cite{azimi2010batch} and LP method~\cite{gonzalez2016batch} which can use arbitrary acquisition

### 2018-02-09 paper/experiments.tex
Paper update

--- 2018-02-08 paper/experiments.tex
@@
 
-\begin{table}[htbp]
+The proposed MACE algorithm was tested using eight benchmark functions and two
+real-world circuits. Four state-of-the-art parallel Bayesian optimization
+methods were compared, including the BLCB algorithm, the local penalization
+method with EI acquisition function (EI-LP), the qEI and qKG
+methods\footnote{We implemented the BLCB algorithm as the available open source
+implementations only allow discrete input. For the EI-LP method, the code is
+downloaded from https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG
+is downloaded from https://github.com/wujian16/Cornell-MOE}. 
+% For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
+% used and the GP models are fitted by maximum likelihood estimations(MLE); for
+% the qKG and qEI methods, the Matern52 kernel is used, and the GP
+% hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
+% integration are the default strategies of the qKG and qEI implementations and
+% it is unclear in the documentation about how to change the GP settings.
+
+\begin{table}[!htb]
     \centering
@@
 
-\begin{table*}[t]
+\begin{table*}[!htb]
     \centering
@@
 
-The proposed MACE algorithm was tested using eight benchmark functions and two
-real-world circuits. Four state-of-the-art parallel Bayesian optimization
-methods were compared, including the BLCB algorithm, the local penalization
-method with EI acquisition function (EI-LP), the qEI and qKG
-methods\footnote{We implemented the BLCB algorithm as the available open source
-implementations only allow discrete input. For the EI-LP method, the code is
-downloaded from https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG
-is downloaded from https://github.com/wujian16/Cornell-MOE}. 
-% For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
-% used and the GP models are fitted by maximum likelihood estimations(MLE); for
-% the qKG and qEI methods, the Matern52 kernel is used, and the GP
-% hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
-% integration are the default strategies of the qKG and qEI implementations and
-% it is unclear in the documentation about how to change the GP settings.
-
 \subsection{Benchmark Problems}
@@
 optimization results are listed in Table~\ref{tab:result_analytical}. As can be
-seen in Figure~\ref{fig:CovPlotBenchmark} and
-Table~\ref{tab:result_analytical}, when running in sequential mode (MACE-1 in Table~\ref{tab:result_analytical} and Figure~\ref{fig:CovPlotBenchmark}), the MACE
-algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
-algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
+seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
+algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
+algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
 Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
@@
 
-\begin{table}[h]
+\begin{table}[!htb]
     \centering
@@
 
+\begin{figure}[!htb]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
+        \caption{Schematic of the power amplifier}
+        \label{fig:schPA}
+    \end{center}
+\end{figure}
+
 \subsection{Class-E Power Amplifier}
 
-\begin{table}[]
+The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
+circuit is designed using the 180nm process with 12 design parameters, the
+circuit is simulated by the commercial HSPICE circuit simulator to get its performances.
+
+\begin{table}[!htb]
     \centering
     \caption{Optimization results of the power amplifier}
+    \vskip 0.15in
     \label{tab:result_PA}
@@
     \end{tabular}
-    \vskip -0.2in
+    \vskip -0.1in
 \end{table}
-
-\begin{figure}[]
-    \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/classE.eps}}
-        \caption{Schematic of the power amplifier}
-        \label{fig:schPA}
-    \end{center}
-\end{figure}
-
-The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
-circuit is designed using the 180nm process with 12 design parameters, the
-circuit is simulated by the commercial HSPICE circuit simulator to get its performances.
 
@@
 $$
-\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
+\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}.
 $$
@@
 
-\begin{figure}[]
+\begin{figure}[!htb]
     \begin{center}

### 2018-02-09 paper/mace.tex
Paper update

--- 2018-02-08 paper/mace.tex
@@
 
-\begin{figure*}[htbp]
+\begin{figure*}[!htb]
     \begin{center}
@@
     \end{center}
+    \vskip -0.15in
 \end{figure*}

### 2018-02-09 paper/experiments.tex
Paper update

@@
 The proposed MACE algorithm was tested using eight benchmark functions and two
-real-world circuits. Four state-of-the-art parallel Bayesian optimization
-methods were compared, including the BLCB algorithm, the local penalization
-method with EI acquisition function (EI-LP), the qEI and qKG
-methods\footnote{We implemented the BLCB algorithm as the available open source
-implementations only allow discrete input. For the EI-LP method, the code is
-downloaded from https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG
-is downloaded from https://github.com/wujian16/Cornell-MOE}. 
-% For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
-% used and the GP models are fitted by maximum likelihood estimations(MLE); for
-% the qKG and qEI methods, the Matern52 kernel is used, and the GP
-% hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
-% integration are the default strategies of the qKG and qEI implementations and
-% it is unclear in the documentation about how to change the GP settings.
+real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
+methods were compared, including the BLCB
+algorithm~\cite{desautels2014parallelizing}, the local penalization method with
+EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
+methods~\cite{qEI,wu2016parallel}\footnote{We implemented the BLCB algorithm as
+the available open source implementations only allow discrete input. For the
+EI-LP method, the code is downloaded from
+https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
+from https://github.com/wujian16/Cornell-MOE}.
+
+For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
+used and the GP models are fitted by maximum likelihood estimations(MLE); for
+the qKG and qEI methods, the ARD Matern52 kernels are used, and the GP
+hyperparameters are integrated via MCMC sampling. The Matern52 kernel and MCMC
+integration are the default strategies of the qKG and qEI implementations and
+it is unclear in the documentation about how to change the GP settings.
 
@@
 
+\begin{figure}[!htb]
+    \begin{center}
+        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
+        \caption{Schematic of the operational amplifier}
+        \label{fig:schDAC2014}
+    \end{center}
+    \vskip -0.2in
+\end{figure}
+
 We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier. The Figure of Merit $FOM$ is constructed as
@@
 
-\begin{figure}[h]
-    \begin{center}
-        \centerline{\includegraphics[width=\columnwidth]{./img/sopam.pdf}}
-        \caption{Schematic of the operational amplifier}
-        \label{fig:schDAC2014}
-    \end{center}
-    \vskip -0.2in
-\end{figure}
-
-\begin{figure}[]
+\begin{figure}[!htb]
 \vskip 0.2in
@@
     \end{center}
+    \vskip -0.15in
 \end{figure}
@@
 circuit is simulated by the commercial HSPICE circuit simulator to get its performances.
-
-\begin{table}[!htb]
-    \centering
-    \caption{Optimization results of the power amplifier}
-    \vskip 0.15in
-    \label{tab:result_PA}
-    \begin{tabular}{llll}
-        \toprule
-        Algorithm & Results               \\ \midrule
-        MACE-1    & -4.08608$\pm$0.296647 \\
-        LCB-1     & -3.78533$\pm$0.335532 \\
-        EI-1      & -3.36407$\pm$0.307489 \\
-        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
-        BLCB-4    & -4.20266$\pm$0.211102 \\
-        EI-LP-4   & -4.07233$\pm$0.244436 \\
-        \bottomrule
-    \end{tabular}
-    \vskip -0.1in
-\end{table}
 
@@
 
-The mean convergence plot is given in Figure~\ref{fig:resClassE}. We can see
-that the MACE outperformed the BLCB and EI-LP in both sequential and batch
-mode. For the batch runs, the MACE converges fastest among the three
-algorithms, while the sequential MACE (MACE-1) has comparable performance as
-the batch EI-LP (EI-LP-4) method.
+The optimization results of the class-E power amplifier are given in
+Figure~\ref{fig:resClassE} and Table~\ref{tab:result_PA}. We can see that the
+MACE outperformed the BLCB and EI-LP in both sequential and batch mode. For the
+batch runs, the MACE converges fastest among the three algorithms, while the
+sequential MACE (MACE-1) has comparable performance as the batch EI-LP
+(EI-LP-4) method.
+
+\begin{table}[!htb]
+    \centering
+    \caption{Optimization results of the power amplifier}
+    \vskip 0.15in
+    \label{tab:result_PA}
+    \begin{tabular}{llll}
+        \toprule
+        Algorithm & Results               \\ \midrule
+        MACE-1    & -4.08608$\pm$0.296647 \\
+        LCB-1     & -3.78533$\pm$0.335532 \\
+        EI-1      & -3.36407$\pm$0.307489 \\
+        MACE-4    & \textbf{-4.31762$\pm$0.347026} \\
+        BLCB-4    & -4.20266$\pm$0.211102 \\
+        EI-LP-4   & -4.07233$\pm$0.244436 \\
+        \bottomrule
+    \end{tabular}
+    \vskip -0.1in
+\end{table}

### 2018-02-09 paper/experiments.tex
minor revision

@@
 For the MACE, BLCB, and EI-LP method, the ARD squared-exponential kernel is
-used and the GP models are fitted by maximum likelihood estimations(MLE); for
+used and the GP models are fitted by maximum likelihood estimations (MLE); for
 the qKG and qEI methods, the ARD Matern52 kernels are used, and the GP

### 2018-02-09 paper/abstract.tex
Revise introduction

@@
 \begin{abstract}
-    Bayesian optimization methods are promising for the optimizations of black-box functions that are expensive to evaluate.
+    Bayesian optimization methods are promising for the optimization of black-box functions that are expensive to evaluate.
 In this paper, a novel batch Bayesian optimization approach is proposed.
@@
     state-of-the-art batch Bayesian optimization algorithms using analytical
-    benchmark functions and real-world analog circuits. The experimental
+    benchmark functions and real-world analog integrated circuits. The experimental
     results show that the proposed method is competitive compared with the

### 2018-02-09 paper/intro.tex
Revise introduction

@@
 best circuit performance, which can be represented by a figure of merit (FOM)
-scalar real-valued function. Prior works about analog circuit optimization
+real-valued function. Prior works about analog circuit optimization
 include offline model-based approaches
@@
 algorithm is firstly introduced for the single- and multi-objective
-optimization of general analog circuits and has shown to be more efficient
+optimization of general analog circuits and has shown to be much more efficient
 compared with other simulation-based approaches. In~\cite{wang2017efficient},
@@
 and parallel predictive entropy search (PPES)~\cite{shah2015parallel}
-approaches, consider to search for the optimal batch selection for a given
+approaches, consider to search for the optimal batch selection for a specific
 acquisition function. These methods usually involve some approximations or
-Monte-Carlo sampling, and thus scales poorly as the batch size increases. Other
+Monte-Carlo sampling, and thus scale poorly as the batch size increases. Other
 works, including the simulation matching (SM)~\cite{azimi2010batch} method, the
@@
 The BLCB method~\cite{desautels2014parallelizing}, local penalization method with expected improvement
-acquisition function (EI-LP)~\cite{gonzalez2016batch}, qEI \cite{qEI} methods and qKG \cite{wu2016parallel} are compared with
+acquisition function (EI-LP)~\cite{gonzalez2016batch}, qEI \cite{qEI} and qKG \cite{wu2016parallel} methods are compared with
 MACE. The proposed MACE method achieved competitive performance when compared

### 2018-02-09 paper/background.tex
Paper update

--- 2018-02-08 paper/background.tex
@@
 
-We handle the scenarios where the topology of the analog circuit is fixed. This
+When designing integrated circuits, the designers have to decide what circuit
+topology to use and then set the corrsponding design parameters. In this work,
+we handle the scenarios where the topology of the analog circuit is fixed. This
 is practical as there are usually a lot of classical topologies for a given
-design task. Once the circuit topology is fixed, the designer has to choose the
-appropriate design parameters according to the specifications and the circuit
-device model. What we want to do is automatically searching for the optimal
-design parameters. This problem can then be formulated as a bound-constrained
+design task, so unlike digital circuits, choosing appropriate topology is
+relatively easy.
+
+Once the circuit topology is fixed, the designer has to choose the appropriate
+design parameters according to the specifications and the circuit device model.
+What we want to do is automatically searching for the optimal design
+parameters. This problem can then be formulated as a bound-constrained
 black-box optimization problem:
@@
 hyperparameter.  The introduction of the i.i.d noise also helps to improve the
-numerical stability.
 
-Given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is
-not a scalar value, but a predictive distribution
+Denote the training set as $\{X, \bm{y}\}$ where $X = \{\bm{x}_1, \dots, \bm{x}_N\}$ and $\bm{y} = \{y_1, \dots, y_N\}$, given a new data point $\bm{x}$, the prediction of $f(\bm{x})$ is not a scalar value, but a predictive distribution
 \begin{equation}
@@
             \mu(\bm{x})      &=& \mu_0 + k(\bm{x},X)[K+\sigma_n^2I]^{-1}(\bm{y} - \mu_0) \\
-            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)[K+\sigma_n^2]^{-1}k(X, \bm{x}),
+            \sigma^2(\bm{x}) &=& k(\bm{x}, \bm{x}) - k(\bm{x}, X)[K+\sigma_n^2I]^{-1}k(X, \bm{x}),
         \end{array}
@@
 \end{equation}
-where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP, $\kappa$ is a parameter that balances the exploitation and exploration.
+where the $\mu(\bm{x})$ and the $\sigma(\bm{x})$ are the predictive value and uncertainty of GP defined in \eqref{eq:GPRPredEqNoisy}, $\kappa$ is a parameter that balances the exploitation and exploration.
 

### 2018-02-09 paper/mace.tex
Paper update

@@
 However, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$.
-For the EI function, the values of EI function at already sampled points would always be lower than any unsampled locations, while this property does not hold for the LCB function.
+For the EI function, the values of EI function at already sampled points would always be lower than the values at any unsampled locations, while this property does not hold for the LCB function.
 
@@
 
+\begin{figure*}[!htb]
+    \begin{center}
+        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
+        \caption{Optimization results of the benchmark functions}
+        \label{fig:CovPlotBenchmark}
+    \end{center}
+    \vskip -0.15in
+\end{figure*}
+
+% \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}
 The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
 
-\begin{algorithm}
+\begin{algorithm}[!htb]
     \caption{Multi-objective Acquisition Ensemble Algorithm}
@@
 
-\begin{figure*}[!htb]
-    \begin{center}
-        \centerline{\includegraphics[width=1.0\linewidth]{./img/convplot.eps}}
-        \caption{Optimization results of the benchmark functions}
-        \label{fig:CovPlotBenchmark}
-    \end{center}
-    \vskip -0.15in
-\end{figure*}
-
-We illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.
+In Figure~\ref{fig:PF_example}, we illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.
 The optimization objective is to maximize the phase margin (PF) of the amplifier, so the FOM is defined as $\mathrm{FOM}(\bm{x}) = - \mathrm{PF}(\bm{x})$.
@@
 The candidate points for the next batch of evaluations are randomly sampled from the Pareto set.
-
-% \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}

### 2018-02-09 paper/mace.tex
Paper update

@@
 
-With multi-objective optimization, the best trade-off between acquisition functions can be captured by the Pareto front of these acquisition functions.
-We can then sample on the Pareto front to obtain multiple candidate points for the objective function evaluations.
-
-In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected.
-Other acquisition functions like KG and PES can also be incorporated into the MACE framework.
-In each iteration, the following multi-objective optimization problem is constructed:
-\begin{equation}
-    \label{eq:MO_LCB_EI_PI}
-    \begin{aligned}
-        & \text{minimize} & & \mathrm{LCB}(\bm{x}),~-\mathrm{EI}(\bm{x}),~-\mathrm{PI}(\bm{x}).
-    \end{aligned}
-\end{equation}
-Then the DEMO multi-objective optimization algorithm~\cite{demo} is applied to solve the multi-objective problem in \eqref{eq:MO_LCB_EI_PI}.
-Once the Pareto front of LCB, EI and PI is obtained, the candidate points are then randomly sampled from the Pareto front.
-
 \begin{figure*}[!htb]
@@
 \end{figure*}
-
-% \textcolor{red}{TODO: If there is space, discuss the approximation of EI in a new subsection "Implementation details"}
-The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
 
@@
 
+With multi-objective optimization, the best trade-off between acquisition functions can be captured by the Pareto front of these acquisition functions.
+We can then sample on the Pareto front to obtain multiple candidate points for the objective function evaluations.
+
+The proposed MACE algorithm is described in Algorithm~\ref{alg:MACE}.
+In the proposed MACE algorithm, the LCB, EI, and PI acquisition functions are selected.
+Other acquisition functions like KG and PES can also be incorporated into the MACE framework.
+In each iteration, the following multi-objective optimization problem is constructed:
+\begin{equation}
+    \label{eq:MO_LCB_EI_PI}
+    \begin{aligned}
+        & \text{minimize} & & \mathrm{LCB}(\bm{x}),~-\mathrm{EI}(\bm{x}),~-\mathrm{PI}(\bm{x}).
+    \end{aligned}
+\end{equation}
+Then the DEMO multi-objective optimization algorithm~\cite{demo} is applied to solve the multi-objective problem in \eqref{eq:MO_LCB_EI_PI}.
+Once the Pareto front of LCB, EI and PI is obtained, the candidate points are then randomly sampled from the Pareto front.
+
 In Figure~\ref{fig:PF_example}, we illustrate the proposed MACE algorithm using an example of a real-world amplifier circuit.
-The optimization objective is to maximize the phase margin (PF) of the amplifier, so the FOM is defined as $\mathrm{FOM}(\bm{x}) = - \mathrm{PF}(\bm{x})$.
+The optimization objective is to maximize the phase margin (PM) of the amplifier, so the FOM is defined as $\mathrm{FOM}(\bm{x}) = - \mathrm{PM}(\bm{x})$.
 The width of one of its transistor is the design variable.

### 2018-06-04 paper/main.tex
Data for benchmark functions
Author and acknowledgements

@@
 \usepackage{placeins}
+\usepackage{multirow}
 
@@
 
-% Use the following line for the initial blind version submitted for review:
-\usepackage{icml2018}
+% % Use the following line for the initial blind version submitted for review:
+% \usepackage{icml2018}
 
 % If accepted, instead use the following line for the camera-ready submission:
-%\usepackage[accepted]{icml2018}
+\usepackage[accepted]{icml2018}
 
@@
 % in order of appearance and this is the preferred way.
-\icmlsetsymbol{equal}{*}
+% \icmlsetsymbol{equal}{*}
 
 \begin{icmlauthorlist}
-\icmlauthor{Aeiau Zzzz}{equal,to}
-\icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-\icmlauthor{Cieua Vvvvv}{goo}
-\icmlauthor{Iaesut Saoeu}{ed}
-\icmlauthor{Fiuea Rrrr}{to}
-\icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
-\icmlauthor{Aaoeu Iasoh}{goo}
-\icmlauthor{Buiui Eueu}{ed}
-\icmlauthor{Aeuia Zzzz}{ed}
-\icmlauthor{Bieea C.~Yyyy}{to,goo}
-\icmlauthor{Teoau Xxxx}{ed}
-\icmlauthor{Eee Pppp}{ed}
+    \icmlauthor{Wenlong Lyu}{fudan}
+    \icmlauthor{Fan Yang}{fudan}
+    \icmlauthor{Changhao Yan}{fudan}
+    \icmlauthor{Dian Zhou}{fudan,utd}
+    \icmlauthor{Xuan Zeng}{fudan}
+% \icmlauthor{Aeiau Zzzz}{equal,to}
+% \icmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
+% \icmlauthor{Cieua Vvvvv}{goo}
+% \icmlauthor{Iaesut Saoeu}{ed}
+% \icmlauthor{Fiuea Rrrr}{to}
+% \icmlauthor{Tateu H.~Yasehe}{ed,to,goo}
+% \icmlauthor{Aaoeu Iasoh}{goo}
+% \icmlauthor{Buiui Eueu}{ed}
+% \icmlauthor{Aeuia Zzzz}{ed}
+% \icmlauthor{Bieea C.~Yyyy}{to,goo}
+% \icmlauthor{Teoau Xxxx}{ed}
+% \icmlauthor{Eee Pppp}{ed}
 \end{icmlauthorlist}
 
-\icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-\icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-\icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
+% \icmlaffiliation{utd}{utdallas}
+\icmlaffiliation{fudan}{State Key Lab of ASIC and System, Microelectronics Department, Fudan University, China}
+\icmlaffiliation{utd}{Department of Electrical Engineering, University of Texas at Dallas, Richardson, TX, U.S.A}
+% \icmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
+% \icmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
+% \icmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
 
-\icmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-\icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+\icmlcorrespondingauthor{Xuan Zeng}{xzeng@fudan.edu.cn}
+% \icmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
 
@@
 
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
+\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+% \printAffiliationsAndNotice{\icmlEqualContribution} % otherwise use the standard text.
 
@@
 \input{conclusion}
+
+\section*{Acknowledgements}
+This research was supported  partly by the National Major Science and
+Technology Special Project of China (2017ZX01028101-003), partly by National
+Natural Science Foundation of China (NSFC) research projects 61774045,
+61574044, 61474026, 61574046, 61674042, and 61628402 and partly by the
+Recruitment Program of Global Experts (the Thousand Talents Plan).
+
+aaaa
 

### 2018-06-05 paper/experiments.tex
Paper update
Add github address in the paper

@@
 EI acquisition function (EI-LP)~\cite{gonzalez2016batch}, the qEI and qKG
-methods~\cite{qEI,wu2016parallel}\footnote{We implemented the BLCB algorithm as
+methods~\cite{qEI,wu2016parallel}. \footnote{We implemented the BLCB algorithm as
 the available open source implementations only allow discrete input. For the
@@
 https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
-from https://github.com/wujian16/Cornell-MOE}.
+from https://github.com/wujian16/Cornell-MOE}.The code of our MACE algorithm is available at \texttt{https://github.com/Alaya-in-Matrix/MACE}.
 
@@
 it is unclear in the documentation about how to change the GP settings.
+
+\subsection{Benchmark Problems}
+
+We tested the MACE algorithm and other parallel BO methods using eight commonly used benchmark
+functions, as summarized in Table~\ref{tab:summaryanalygical}.
 
@@
 \end{table}
+
+For all functions except the two 10D functions, we set the number of initial
+random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
+45$. Batch size is set to $B = 4$, the total number of function evaluations is
+$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we set
+$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
+times to average the random fluctuations.
+
+We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
+acquisition functions. The sequential EI and LCB based Bayesian optimization
+are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
+respectively.
+
+The mean convergence plots of the tested algorithms on the benchmark functions are
+given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
+optimization results are listed in Table~\ref{tab:result_analytical}. As can be
+seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
+algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
+algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
+Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
+MACE (MACE-4) gave the best performances among all the tested algorithms for
+six out of the eight benchmark functions, and has shown dramatic speedup
+compared to the sequential MACE.
 
@@
 \end{table*}
-
-\subsection{Benchmark Problems}
-
-We tested the MACE algorithm and other parallel BO methods using eight commonly used benchmark
-functions, as summarized in Table~\ref{tab:summaryanalygical}.
-
-For all functions except the two 10D functions, we set the number of initial
-random sampling to $N_{init} = 20$ and the number of iterations to $N_{iter} =
-45$. Batch size is set to $B = 4$, the total number of function evaluations is
-$N_{init} + B \times N_{iter}$. For the 10D Ackley and 10D Rosenbrock functions, we set
-$N_{init} = 100$ and $N_{iter} = 175$. The experiments were repeated ten
-times to average the random fluctuations.
-
-We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
-acquisition functions. The sequential EI and LCB based Bayesian optimization
-are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
-respectively.
-
-The mean convergence plots of the tested algorithms on the benchmark functions are
-given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
-optimization results are listed in Table~\ref{tab:result_analytical}. As can be
-seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
-algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
-algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
-Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
-MACE (MACE-4) gave the best performances among all the tested algorithms for
-six out of the eight benchmark functions, and has shown dramatic speedup
-compared to the sequential MACE.
 

### 2018-06-06 paper/experiments.tex
move github address to footnote

@@
 
-The proposed MACE algorithm was tested using eight benchmark functions and two
+The proposed MACE algorithm\footnote{Available at https://github.com/Alaya-in-Matrix/MACE} was tested using eight benchmark functions and two
 real-world analog circuits. Four state-of-the-art parallel Bayesian optimization
@@
 https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
-from https://github.com/wujian16/Cornell-MOE}.The code of our MACE algorithm is available at \texttt{https://github.com/Alaya-in-Matrix/MACE}.
+from https://github.com/wujian16/Cornell-MOE}
 

### 2018-06-06 paper/mo_description.tex
Supplementary

\section{Description and Demonstration of the DEMO Multi-objective Optimization Algorithm}

### 2018-06-06 paper/intro.tex
Revision about the citations

@@
 approach is that the accurate models are usually hard to get. For example,
-in~\cite{wang2014enabling}, 100,000 randomly simulated points are used to train
+in~\citet{wang2014enabling}, 100,000 randomly simulated points are used to train
 a sparse polynomial model for an amplifier circuit with ten design parameters.
@@
 introduced for the automated design of analog circuits to reduce the
-required number of circuit simulations. In~\cite{liu2014gaspad}, GP is combined
+required number of circuit simulations. In~\citet{liu2014gaspad}, GP is combined
 with differential evolution algorithm. Recently, the Bayesian optimization
 (BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
-circuit optimization. In~\cite{lyu2017efficient}, the Bayesian optimization
+circuit optimization. In~\citet{lyu2017efficient}, the Bayesian optimization
 algorithm is firstly introduced for the single- and multi-objective
 optimization of general analog circuits and has shown to be much more efficient
-compared with other simulation-based approaches. In~\cite{wang2017efficient},
+compared with other simulation-based approaches. In~\citet{wang2017efficient},
 the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
@@
 the knowledge gradient (KG) acquisition function must be used for the qKG algorithm. As is stated
-in~\cite{hoffman2011portfolio}, no single acquisition function can always
+in~\citet{hoffman2011portfolio}, no single acquisition function can always
 outperform other acquisition functions. Relying on one acquisition function may

### 2018-06-06 paper/experiments.tex
"the Bayesian optimization" => "Bayesian optimization"

@@
 The operational amplifier~\cite{wang2014enabling} shown in
-Figure~\ref{fig:schDAC2014} is used to test the Bayesian optimization algorithms. The circuit is designed
+Figure~\ref{fig:schDAC2014} is used to test Bayesian optimization algorithms. The circuit is designed
 using the 180nm process. It has 10 design parameters, including the lengths
@@
 
-The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test the Bayesian optimization algorithms. The
+The class-E power amplifier shown in Figure~\ref{fig:schPA} is used to test Bayesian optimization algorithms. The
 circuit is designed using the 180nm process with 12 design parameters, the

### 2018-06-06 paper/intro.tex
"the Bayesian optimization" => "Bayesian optimization"

@@
 required number of circuit simulations. In~\citet{liu2014gaspad}, GP is combined
-with differential evolution algorithm. Recently, the Bayesian optimization
+with differential evolution algorithm. Recently, Bayesian optimization
 (BO)~\cite{shahriari2016taking} algorithm has also been applied for analog
-circuit optimization. In~\citet{lyu2017efficient}, the Bayesian optimization
+circuit optimization. In~\citet{lyu2017efficient}, Bayesian optimization
 algorithm is firstly introduced for the single- and multi-objective
@@
 compared with other simulation-based approaches. In~\citet{wang2017efficient},
-the Bayesian optimization algorithm is combined with adaptive Monte-Carlo
+Bayesian optimization algorithm is combined with adaptive Monte-Carlo
 sampling to optimize the yield of analog circuits and static random-access
@@
 
-The Bayesian optimization algorithm is a well-studied algorithm and has
+Bayesian optimization algorithm is a well-studied algorithm and has
 demonstrated to be promising for the automated design of analog circuits.
@@
 
-The Bayesian optimization algorithm has been extended to enable batch
+Bayesian optimization algorithm has been extended to enable batch
 selection. Some prior works, like the qEI \cite{qEI}, qKG \cite{wu2016parallel}
@@
 
-In this paper, we propose to parallelize the Bayesian optimization algorithm
+In this paper, we propose to parallelize Bayesian optimization algorithm
 via the Multi-objective ACquisition Ensemble (MACE). The proposed MACE method

### 2018-06-06 paper/background.tex
Revision about the citations
Paper revision

@@
 $\epsilon_t \sim N(0, \sigma_n^2)$ and set the noise level $\sigma_n^2$ as a
-hyperparameter.  The introduction of the i.i.d noise also helps to improve the
+hyperparameter.  The introduction of the i.i.d noise also helps to improve the numerical stability.
 
@@
 
-Following the suggestion of~\cite{brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
+Following the suggestion of~\cite{srinivas2010gaussian, brochu2010tutorial}, the $\kappa$ in \eqref{eq:LCB} is defined as:
 \begin{equation}

### 2018-06-06 paper/experiments.tex
Paper revision

@@
 https://github.com/SheffieldML/GPyOpt. The code for qEI and qKG is downloaded
-from https://github.com/wujian16/Cornell-MOE}
+from https://github.com/wujian16/Cornell-MOE.}
 
@@
 
-The mean convergence plots of the tested algorithms on the benchmark functions are
-given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
-optimization results are listed in Table~\ref{tab:result_analytical}. As can be
-seen in Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
-algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
-algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
-Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
-MACE (MACE-4) gave the best performances among all the tested algorithms for
-six out of the eight benchmark functions, and has shown dramatic speedup
-compared to the sequential MACE.
+The mean convergence plots of the tested algorithms on the benchmark functions
+are given in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
+regrets are listed in Table~\ref{tab:result_analytical}. As can be seen in
+Figure~\ref{fig:CovPlotBenchmark} and Table~\ref{tab:result_analytical}, when
+running in sequential mode, the MACE algorithm is competitive with the LCB and
+EI acquisition functions. The sequential MACE (MACE-1) algorithm gave better
+performances than the sequential EI (EI-1) and sequential LCB (LCB-1)
+algorithms in the Eggholder, Branin, Hartmann6, Ackley10, and Rosenbrock10
+functions. Also, the parallel MACE (MACE-4) gave the best performances among
+all the tested algorithms for six out of the eight benchmark functions, and has
+shown dramatic speedup compared to the sequential MACE. We also performed
+additional experiments with varied batch sizes, the detail of those
+experimental results can be seen in the supplementary materials.
 
@@
     \centering
-    \caption{Optimization results of the benchmark functions}
+    \caption{Statistics of the regrets of the benchmark functions}
     \label{tab:result_analytical}

### 2018-06-06 paper/mace.tex
Paper revision

@@
 However, for the PI function, when $\sigma(\bm{x})$ increases, the value of PI would decrease when $\mu(\bm{x}) < \tau$, and increase when $\mu(\bm{x}) > \tau$.
-For the EI function, the values of EI function at already sampled points would always be lower than the values at any unsampled locations, while this property does not hold for the LCB function.
+For the EI function, if the function is noiseless, the values of EI function at already sampled points would always be worse than the EI values at any unsampled locations, while this property does not hold for the LCB function.
 

### 2018-06-07 paper/mo_description.tex
Revise the supplementary materials

@@
-\section{Description and Demonstration of the DEMO Multi-objective Optimization Algorithm}
+\section{DEMO: Differential Evolution for Multi-Objective Optimization}
+
+The DEMO (Differential Evolution for Multi-Objective, \citet{demo}) algorithm is used for the multi-objective optimization of acquisition functions, we briefly introduce the algorithm in this section.
+It should be noted that other multi-objective optimization algorithms can also be used for the proposed MACE algorithm.
+
+The DEMO algorithm follows the basic procedure of evolutionary algorithms.
+Firstly, a set of points are randomly sampled to form the initial population, at each iteration, random variations are added to parent population via mutation and crossover to generate the children population, the parent population and children population are compared to create the parent population for the next generation.
+During the evolution, the Pareto front is recorded.
+The DEMO algorithm is summarized in Algorithm~\ref{alg:DEMO}.
+
+\begin{algorithm}[h]
+    \caption{DEMO}
+    \label{alg:DEMO}
+    \begin{algorithmic}[1]
+        \STATE Randomly sample the $N$ points in the design space to form the initial population $P^1$
+        \FOR{t = 1, 2, \dots $G$~}
+            \STATE $M^t$     = \texttt{mutation}($P^t$)
+            \STATE $C^t$     = \texttt{crossover}($P^t$, $M^t$)
+            \STATE $P^{t+1}$ = \texttt{selection}($P^t$, $C^t$)
+        \ENDFOR
+        \STATE Return the recorded Pareto front
+    \end{algorithmic}
+\end{algorithm}
+
+% XXX: mutation
+At the $i$-th iteration, we denote the population as $P^i \in R^{N \times D}$, where $N$ is the number of population, and $D$ is the dimension of input variables.
+The mutated population $M^i \in R^{N \times D}$ is generated by
+\begin{equation}
+    \label{eq:DEMO_mutation}
+    M^i_j = P^i_{r1} + F \times (P^i_{r2} - P^i_{r3}),~j \in \{1 \dots NP\}
+\end{equation}
+where $M^i_j$ means the $j$-th row of $M^i$, while $P^i_{r1}$, $P^i_{r2}$ and $P^i_{r3}$ are the $\mathit{r1}$-th, $\mathit{r2}$-th and $\mathit{r3}$-th rows of $P^i$, the $r1$, $r2$ and $r3$ are three integers randomly chosen from $[1, N]$.
+The scaling factor $F \in (0, 1)$ is an algorithm parameter to control the mutation.
+
+After the mutation, crossover operations are performed to generated the children population $C^i \in R^{N \times D}$.
+For each element of $C^i$, two random numbers $r_r$ and $r_i$ are generated, $r_r$ is a real-valued number uniformly sampled from $(0, 1)$, $r_i$ is an integer number uniformly sampled from $[1, D]$, the element of $C^i$ is calculated by
+\begin{equation}
+    \label{eq:DEMO_crossover}
+    C^i_{jk} = \left\{
+        \begin{array}{lll}
+            P^i_{jk} & & r_r < \mathit{CR} \text{ and } r_i \neq k \\
+            C^i_{jk} & & \text{otherwise}.
+        \end{array}
+    \right.
+\end{equation}
+where the crossover rate $\mathit{CR}$ is an algorithm parameter to control the crossover.
+
+Now that we have the parent population $P^i$ and the children population $C^i$,
+we perform selection to generate the new population $P^{i+1}$. Firstly, an
+empty archive is created, we perform pair-wise compairsion between parents and
+children, if one parent solution dominates its child solution, the parent
+solution is added into the archive; if the child solution dominates its parent,
+the child is added into the archive; if the parent and its child don't dominate
+each other, both the parent and the child are added into the archive. After
+the pair-wise compairsion, non-dominated sorting\cite{nsgaii} is
+performed to select $G$ solutions as the parent population of the next
+generation. The non-dominated sorting method defines a complete order between a
+group of solutions, details of the non-dominated sorting can be seen in
+\cite{nsgaii}.
+
+As has been mentioned, four algorithm parameters are to be set for the DEMO algorithm: the population size $N$, the number of generations $G$, the scaling factor $F$ and the crossover rate $\mathit{CR}$.
+We set $N = 100$, $G = 250$, $F = 0.5$ and $\mathit{CR} = 0.3$ for all the experiments performed in the paper.

### 2018-06-07 paper/experiments.tex
Revision

@@
 additional experiments with varied batch sizes, the detail of those
-experimental results can be seen in the supplementary materials.
+experimental results can be seen in the supplementary materials. We report the
+time spent on the ten-dimensional Rosenbrock function optimization with $B = 4$ as a measure
+of the algorithm overhead, for the ten-dimensional Rosenbrock function, it took
+MACE about 11 hours to finish all the $N_{iter} = 175$ iterations, the BLCB algorithm took about
+five hours, for the EI-LP algorithm, it took only one hour to finish the optimization. The overheads for qEI and qKG are much larger, it took
+more than two days for qKG and qEI to finish the optimization of the ten-dimensional Rosenbrock function.
 

### 2018-07-09 paper/ICML_poster.tex
Poster finished

% \documentclass[landscape,a0paper,fontscale=0.292]{baposter}
\documentclass[landscape,paperwidth=200cm, paperheight=120cm,fontscale=0.19]{baposter}

\usepackage[vlined]{algorithm2e}
\usepackage{times}
\usepackage{calc}
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{subfigure}
\usepackage{bm}

\usepackage{graphicx}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{ae}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Begin of Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Here starts the poster
%%---------------------------------------------------------------------------
%% Format it to your taste with the options
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{poster}{
 % Show grid to help with alignment
 grid=false,
 % Column spacing
 colspacing=0.7em,
 % Color style
 headerColorOne=cyan!20!white!90!black,
 borderColor=cyan!30!white!90!black,
 % Format of textbox
 textborder=faded,
 % Format of text header
 headerborder=open,
 headershape=roundedright,
 headershade=plain,
 background=none,
 bgColorOne=cyan!10!white,
 headerheight=0.14\textheight}
 % Eye Catcher
 {
      % \includegraphics[width=0.08\linewidth]{track_frame_00010_06}
      % \includegraphics[width=0.08\linewidth]{track_frame_00450_06}
      % \includegraphics[width=0.08\linewidth]{track_frame_04999_06}
 }
 % Title
 {Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design}
 % Authors
    {
        Wenlong Lyu$^1$, Fan Yang$^1$, Changhao Yan$^1$, Dian Zhou$^{1, 2}$ and Xuan Zeng$^1$ \\
        $^1$ \small State Key Lab of ASIC and System, School of Microelectronics, Fudan University, Shanghai, China \\
        $^2$ \small Department of Electrical Engineering, University of Texas at Dallas, Richardson, TX, U.S.A
    }
 % University logo
 {
  % \begin{tabular}{r}
  %   \includegraphics[height=0.12\textheight]{logo}\\
  %   \raisebox{0em}[0em][0em]{\includegraphics[height=0.03\textheight]{msrlogo}}
  % \end{tabular}
 }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Now define the boxes that make up the poster
%%%---------------------------------------------------------------------------
%%% Each box has a name and can be placed absolutely or relatively.
%%% The only inconvenience is that you can only specify a relative position 
%%% towards an already declared box. So if you have a box attached to the 
%%% bottom, one to the top and a third one which should be inbetween, you 
%%% have to specify the top and bottom boxes before you specify the middle 
%%% box.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Motivation}{name=motivation,column=0,row=0,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
            \item The design of analog integrated circuits heavily relys on designers' manual calculation, which can be difficult as the progress of Moore's law
            \item Circuit simulation can be viewed as black-box function that maps the design variables to the circuit performance, global optimization algorithms can be applied to optimize the circuits
            \item In our previous work, we applied Bayesian optimization for the efficient optimization of analog circuits
            \item Bayesian optimization needs to be paralleled to use available multi-core systems
      \end{itemize}
  }
  \headerbox{Bayesian Optimization}{name=BO,column=0,span=1, below=motivation}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
            \item Gaussian process used as probabilistic model of the black-box function
            \item Acquisition functions are constructed and optimized to find promising design
            \item Many existing acquisition functions: EI, PI, LCB and so on, these acquisition fucntions may not agree with each other
      \end{itemize}
  }

  \headerbox{Multi-objective optimization}{name=MO,column=0,span=1, above=bottom, below=BO}{
        Suppose we have $m$ objectives, the formulation of the problem is 
        $$
        \text{minimize} f_1(\bm{x}),\dots,f_m(\bm{x})
        $$

        For two designs \(\bm{x}_1\) and \(\bm{x}_2\), \(\bm{x}_1\) \textbf{domininates} \(\bm{x}_2\) if

        \begin{itemize}
        \item
          $\forall i \in 1 \dots m, f_i(\bm{x}_1) \le f_i(\bm{x}_2)$
        \item
          $\exists i \in 1 \dots m, f_i(\bm{x}_1) < f_i(\bm{x}_2)$
        \end{itemize}

        If a design is not domininated by any other design, it is said to be \textbf{Pareto-optimal}. All the Pareto-optimal points in the design space are the \textbf{Pareto set}. All the Pareto-optimal points in the objective space are the \textbf{Pareto front}. The goal of multi-objective is to find a set of evenly distributed points on the Pareto front
  }

  \headerbox{Multi-objective Acquisition Function Ensemble (MACE)}{name=proposed,column=1,span=2, row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \begin{itemize}
            \item At each iteration, train GP model and construct EI, PI and LCB acquisition functions
            \item Perform \textbf{multi-objective} optimization to find the Pareto front of the three acquisition functions
            \item Sample $B$ points from the Pareto front and evaluate them, $B$ is the batch size
      \end{itemize}
  }

  \headerbox{Multi-objective optimization of multiple acquisition functions}{name=MACE,column=1,below=proposed, span=2}{
      \center{
    \includegraphics[width=0.36\textwidth]{./img/pm_gp_ps.eps}
    ~
    \includegraphics[width=0.36\textwidth]{./img/pf.eps}

    New points are selected from the Pareto set (the yellow points) of the acquisition functions
    }

}

  \headerbox{Results of Benchmark Functions}{name=Benchmark,column=1,span=2, below=MACE, above=bottom}{
      \center{
  \includegraphics[width=0.82\linewidth]{./img/convplot.eps}
  }

  Dotted lines: optimization result with batch size $B$=1. Solid lines: optimization results with batch size $B$=4

    % \subfigure[]{\label{fig:PF_example_1}\includegraphics[width=0.49\textwidth]{./img/pm_gp_ps.eps}}
    % ~
    % \subfigure[]{\label{fig:PF_example_2}\includegraphics[width=0.49\textwidth]{./img/pf.eps}}
    % \label{fig:PF_example}
% \end{figure}

    % \caption{Optimization results of the benchmark functions}
    % \label{fig:CovPlotBenchmark}
}

  \headerbox{Schematic of the OpAmp Circuit}{name=schopamp,column=3,span=1, row=0}{
      \centerline{\includegraphics[width=0.60\linewidth]{./img/sopam.pdf}}
  }
  \headerbox{Results of the OpAmp circuit}{name=opamp,column=3,span=1, below=schopamp}{
      \centerline{\includegraphics[width=0.60\linewidth]{./img/mean_DAC2014.eps}}
  }
  \headerbox{Schematic of the Power Amplifier}{name=schpa,column=3,span=1, below=opamp}{
      \centerline{\includegraphics[width=0.60\linewidth]{./img/classE.eps}}
  }
  \headerbox{Results of the power amplifier}{name=PA,column=3,span=1, below=schpa}{
      \centerline{\includegraphics[width=0.60\linewidth]{./img/ClassE_mean.eps}}
}

\end{poster}
%
\end{document}
